\sidequest[Town]{the Trouble with Ale}

\label{troubleAle}

\noindent
What dwarves call ale, humans call `hard spirits'.
If you water it down, it makes for a cheap beer substitute.
\Gls{beardedalemaster} has decided to capitalize on this by smuggling barrels of dwarven spirit into \gls{town}, via \gls{pigowner}.

She has made a killing in profits, and almost pushed out the regular \gls{wheatGuild}.
\Gls{alemaster} isn't happy with her profits being cut into, so the two sides sabotage each other and shenanigans ensue.

\begin{boxtext}

  A rank wind blows through \gls{town}.
  From the street ahead a drunken man in full plate armour falls against a wall, before getting back up and shouting at passers by that they're pathetic for drinking elvish nonsense, and need a proper dwarvish drink.

\end{boxtext}

\subsubsection*{Resolutions}

The troupe may resolve this in a number of ways.

\paragraph{Prosecuting the \gls{wheatGuild} members}
in the \gls{court} may work, but \gls{townmaster} does not always make predictable rulings, and the \glspl{pc} may end up in trouble for raising the matter.%
\exRef{judgement}{Judgement}{god:Justice}

\paragraph{Coercing both \glspl{server} to the \gls{armourHall}}
will require a clear incentive, but once done, the \glspl{armourer} will ensure they resolve their dispute amicably.
They will demand lower taxes for imports from \gls{warden}, while \gls{alemaster} receives a cut of the profits.
\label{aleResolution}

\paragraph{Failure to resolve}
means the two fight until the fights have destroyed the ale supply on both sides.
People will riot, and the troupe will not be able to drink ale.

And even worse, the townsfolk will begin drinking the water around \gls{town}, and soon contract diseases, such as Spychoke and Guardbane.%
\iftoggle{judgement}{\footnote{See the book of \textit{Judgement}, \autopageref{Spychoke}.}}


\sqpart{Town}% AREA
{\squash The Drunken Outlander}% NAME
{A cook of the local \gls{wheatGuild} starts fights while pretending to be from the \gls{wheatGuild} of \glsentrytext{southDale}}% SUMMARY
\label{drunkenOutlander}

Reputation is paramount among the guilds, so \gls{alemaster} wants to discredit \gls{southDale}'s \gls{wheatGuild}.
She pays a few of the \gls{wheatGuild}'s cooks to dress as members of the foreign \gls{wheatGuild} and start fights all over town.

This encounter can easily slip into the background -- the drunkard has no interest in annoying the \glspl{pc}, especially if they look well-armed.

Players may notice he's pretending to be drunk with a \roll{Wits}{Medicine} Group Roll, or notice that his insignia does not have the right flowers for \gls{southDale} with a \roll{Wits}{Academics} roll.
Both have \tn[10].

\NPC{\M}{\Gls{server} Carnpox}{Bobbing~Adams~Apple}{Pointing at people}{to get paid and go home}

\person{2}% STRENGTH
  {0}% DEXTERITY
  {1}% SPEED
  {{0}% INTELLIGENCE
  {-1}% WITS
  {+1}}% CHARISMA
  {0}% DR
  {1}% COMBAT
  {Athletics~1, Deceit~1}% SKILLS
  {\longsword, \completeplate}% EQUIPMENT
  {\addtocounter{xpbonus}{-3}}

If questioned, Carnpox says this is ``just a little joke'', but does not reveal the overall plan.

\paragraph{Investigating the matter}
might employ any number of tactics.
They may track down the \gls{weaversGuild} which created the fake \gls{southDale} insignia, or interrogate Carnpox with threats of the \gls{court}.
Every roll has a \gls{tn} of 11, but players can make as many guesses as they like, and spend a day to investigate each one.

\begin{boxtext}

  Suddenly the house to your right explodes, and water rushes down the street, knocking aside stalls, women, two stray dogs, and sweeping the lot down the road.  It foams and froths like mad, and then you notice -- this isn't water, it's ale!

\end{boxtext}

\sqpart{Town}% AREA
{\squash Ale Explosion}% NAME
{Barrels of Ale explode down the street}% SUMMARY

Play this encounter at the same time as the next on the list.

\Gls{alemaster} found that the more ale is brewed in a batch, the cheaper it becomes.
She bought a few cheap houses around the city, and commissioned massive barrels.
However, \gls{beardedalemaster} found where they're stored, and paid a few street-rat children to come in and mess the place up, pulling corks out of the barrels, and such.
Unfortunately, with just a little too much jostling and jumping on the barrels, the unstable equipment exploded.

As three houses, full of giant barrels of ale, all explode at once, it creates a tidal wave of unripe alcohol.
The troupe can avoid being swept down the street by the storm with a \roll{Wits}{Athletics} roll, \tn[8].

\paragraph{If the \glspl{pc} investigate,}
an \roll{Intelligence}{Vigilance} Team Roll, \tn[10], will allow the characters to find the bodies of the children who started the problem, along with the fact that they were recently speaking with \gls{beardedalemaster}, who currently drinks in \gls{pig}.%
\iftoggle{core}%
{\footnote{See the Core Rules, \autopageref{teamwork}, for Team Rolls.}}%
{}%

\begin{boxtext}

  A crowd is vomiting out of a pub, pushing six men out with them\ldots or rather three men and three dwarves, all heavily armed.
  The crowd shout for them to go back to the mountains and that they're not welcome in the area, but a dwarf, covered in metal from head to toe, and wearing the emblem of the \gls{wheatGuild} from \gls{southDale}, lifts his metal visor and barks back at crowd, listing a litany of laws concerning public houses and the rights of foreign \glspl{server}, with deafening volume.

  The crowd just jeer, making a large vein in the dwarf's head bulge while his face turns redder by the moment.

\end{boxtext}

\sqpart{Town}% AREA
{You Can't Drink Here}% NAME
{People jeer at envoys from \glsentrytext{southDale} \gls{wheatGuild} and a fight breaks out}% SUMMARY

A travelling troupe of three men and three dwarves from \gls{southDale} are tired from a long day's walk, and need a rest and drink, but the townsfolk think of the \gls{wheatGuild} from \gls{southDale} as nothing but troublemakers (the devious plan on \vpageref{drunkenOutlander} worked).

Strath, the angry dwarvish \gls{server}, has had enough of the bickering and feels tough enough in his full plate armour.
He has no idea that \gls{beardedalemaster} has been pulling stunts, such as destroying the stores of the local \gls{wheatGuild}.

\paragraph{If the characters do nothing,}
the crowd at one point pelt Strath with some old soup, and local ale.
He swings pokes at the jeering crowd with a weapon, and a fight breaks out instantly.
The group then flee the city, and all ale trade with \gls{southDale} stops, as people begin to complain, loudly and violently, outside any establishment which sells the distinctive swill made from \gls{southDale}'s dwarven spirits.

\paragraph{If the characters try to de-escalate the problem,}
give them an appropriate roll.
They have time to try multiple tactics, from asking the crowd to calm down, to threatening to call the guard.
However, the crowd are very angry, so all rolls are at \tn[10].

\dwarvensoldier[\NPC{\Dw\M}{Keeper Strath}{Double Braided Beard}{Strokes beard}{Experience}]

\humansoldier[\npc{\T[3]\Hu\M\M\F}{Bough, Fishhead and Carst}]

These two are heavy drinkers, and heavy fighters, but they will stop as soon as Keeper Strath gives the word.

\dwarventrader[\npc{\T[2]\Dw\M}{Drumlin \& Karst}]

\Gls{beardedalemaster} still drinks at \gls{pig}.  

\paragraph{Conclusion:} If the characters can track down \gls{beardedalemaster} and have her talk with \gls{alemaster} they might be able to make peace between the two groups, as noted \vpageref{aleResolution}.
In this case, crisis is averted, and the final part can be discarded.

\beardedalemaster

\sqpart{Town}% AREA
{\squash Dry}% NAME
{Guild fights have caused all ale supplies to run out}% SUMMARY

If the party did not manage to avert total disaster in the previous encounter, play this encounter together with the next Side~Quest part.

\begin{boxtext}

  Later that day, you can find no rest in a tavern.
  The first has run out of ale, and the second.
  Asking around, people are saying they've all dried up, and now serve nothing but foul water, and overpriced milk (at 3~\glspl{cp}).
  All of \gls{town} feels agitated.

\end{boxtext}

\noindent
For the next two encounters, all social rolls have a -2 penalty, as everyone around is feeling irritable.

Any characters drinking the water in \gls{town} contracts (speaking above a whisper inflicts \pgls{fatigue} as the throat closes).
