\section*{Parting Note}
\label{noEnding}

There is no ending here.

I've run this campaign, start-to-finish, three times over the years.
Each time it changes a little, and always has a different ending.
By the time the players have made their decisions, and their characters have a reputation among the factions moving across the \glspl{thread}, they could be anywhere, so I'm afraid I can't help you there, except to suggest taking stock of who's left alive, what resources they have, and what they want.

Perhaps \gls{banditking} has no troupe left and has to make a last, desperate attempt at lowering the taxes in \gls{whiteplains} by murdering \gls{townmaster}'s heir as a warning to anyone who would overburden \gls{whiteplains} again.

Perhaps \gls{banditking} arrives with a small army, and offers to clear the citadel of \glspl{ghast} in order to gain the favour of everyone in \gls{town}, then begins to sweet-talk \gls{town}'s guild leaders before making a play for leadership.

Perhaps the \gls{wolfhead} and \gls{whiteBandits} join forces and both get what they want.

Or perhaps all the primary characters died at the hands of the \gls{guard}, and this campaign comes to a halt far before the last \glspl{segment} can start.

However it turns out, happy gaming.

\section{Books}
\label{bookAppendix}

\begin{multicols}{2}

\subsection{A Complete Explanation of the \Glsfmttext{deep}}
\label{bookOfDeep}
\index{Books!\Glsfmttext{deep}}

This massive tome's disorganized chapters, unreferenced references to other books, and dense diagrams make it a pain to read.
However, it promises a complete account of \gls{deep}.

The entire book tells lies from start to finish.

If players ask what's inside, tell them it holds a lot of information, and they should simply ask.
If their question ends in a vowel, say `yes', and if their question ends in a consonant, say `no'.

\begin{description}
  \itshape
  \item[Do goblins live in the \gls{deep}?]
  No, the book states that the goblins have their own realm, unrelated to the \gls{deep}.
  \item[Do the creatures down there just carry lights all the time?]
  Yes -- the book explains that all creatures have some source of light, or carry \glspl{torch}.
\end{description}

Every two questions will take an entire \gls{interval} to answer.
And if answers contradict each other, so be it.

Little by little, the troupe can create a complete image of how the \gls{deep} works, all of it fictional.

\subsection{An Account of the Fingers}
\label{bookOfFingers}
\index{Fingers, The}
\index{Books!Fingers}

`The Fingers' can be found inside the Vore Gate (area \vref{shadowVore}).
The old \glspl{server} who once stayed there studied the passages through brute-force, and wrote various accounts of the process of mapping them, notes on correct tunnels, and descriptions of the items they found there.

\begin{exampletext}
  These brickwork tunnels show signs of advanced ageing.
  The first tunnel extends for five minutes (the books measures distance in minutes' walked), which then splits left and right.

  Once someone goes beyond this split, they sometimes return, and sometimes do not.
  Those that return, never take any light with them; therefore whatever danger lurks in the tunnel must come towards light.
  And everyone who returns walks silently, which means that the think which lurks in the fingers comes towards any noise.

  Through long trials, recording every success and failure, people mapped out tunnels.

  Some have returned with precious items -- items made of platinum, or steel.
  Nobody can tell if the creator intended to make the items for some purpose, or simply as art.
  However, a great deal of metallic items, stacked on shelves, in the dark, threatens to make a noise; any sliding, or drop will create loud bangs.
  So taking anything from this `treasure room', can mean death.

  Everyone who enters puts a single, silent, finger on the walls, and walks forwards, following the tunnel laid out for them.
  Hence the name, `the Fingers'.
\end{exampletext}

Each book ends with notes on the treasures gained.

Upon entering, a sense of dread emerges, as all \glspl{fp} disappear.
Anyone sneaking through to find treasures rolls \roll{Dexterity}{Stealth} at \tn[12], with a +1 Bonus for each book they have.
Success lets them filch an item from one of the treasuries.
Failure means death.

Form:

\begin{dlist}
  \item
  Statue of some kind of crab\ldots
  \item
  Two-headed blade (no handle)\ldots
  \item
  Sphere\ldots
  \item
  Diorama of cloud structures\ldots
  \item
  Disk\ldots
  \item
  Statue of a tree made out of teeth\ldots
\end{dlist}

Material:

\begin{dlist}
  \item
  \ldots made of platinum (worth 70~\glspl{gp})
  \item
  \ldots made of rock (worthless).
  \item
  \ldots made of crystal that hums, but only someone touching it can hear it (no precedence for price).
  \item
  \ldots made of red crystal (can be used as a Fire \gls{ingredient}, worth 6~\glspl{gp}).
  \item
  \ldots made of green clay (in fact a sleeping \superWierdzi)
  \item
  \ldots carved from steel (worth 6~\glspl{sp}).
\end{dlist}

\end{multicols}

\indexprologue{%
  \noindent
  By \gls{gmt}, the current year is \arabic{fenestraYear}.
  \label{historyIndex}
}

\label{talismanIndex}
\printindex[talismans]

\printindex[spells]

\printindex[history]

\printindex

\needspace{0.3\paperheight}
\section{\Glsfmtplural{segment} by \Glsfmttext{region}}

If you prefer to track all of the \glspl{segment} from one place, you can use this list, instead of the list under each \gls{region}.

\bigLine

\begin{multicols*}{2}

\raggedbottom

\needspace{5\baselineskip}
\subsection{Forest \Glsfmtplural{segment}}

\Gls{region} covered \vpagerefrange{forestChapter}{forestEnd}.

\printThreadsInRegion{Forest}

\bigLine

\needspace{16\baselineskip}
\subsection{Roads \Glsfmtplural{segment}}

\Gls{region} covered \vpagerefrange{roadsStart}{roadsEnd}.

\printThreadsInRegion{Roads}

\bigLine

\needspace{12\baselineskip}
\subsection{\Glsfmttext{town} \Glsfmtplural{segment}}

\Gls{region} covered \vpagerefrange{townStart}{townEnd}.

\printThreadsInRegion{town}

\end{multicols*}
