\section{\Glsentrytext{whiteplains} Outpost}
\label{banditLair}

\renewcommand\csComments{
  \randomdozen
  \callout[9]{14,12}{-.5,-2}{Watch Point}{\dicef{6}}
  \callout[10]{15.5,7}{-2.5,-1}{Beds,}{beers, and outhouse \dicef{12}}
  \callout[6]{12.8,2.5}{-2,1.3}{Horse Supplies}{70 days worth of food}
  \callout[8]{10,0.3}{0,0.5}{Stables}{with \dicef{12} horses}
  \callout{6.5,1.6}{.7,1.4}{Large Gate}{$\dicef{3}-1$}
  \callout{3.8,2.5}{1.3,2.5}{Watch Point}{$\dicef{2}-1$}
  \callout[7]{1.5,2}{0.8,4}{Archers}{play cards through the night $\dicef{6} + 1$}
  \callout[7]{0,4.5}{1.3,2.3}{Supplies \& Beds}{$3\times$ shortsword, \arabic{r12}00~\glspl{cp}.  $\dicef{6} + 1$}
  \callout[5]{0,9.5}{0.2,-1.7}{False Welcome}{}
  \callout[8]{6,11.3}{0,-1.5}{\Glsentrytext{banditking}'s Room}{\arabic{r12}0~\glspl{sp}}
  \callout[8]{2,11}{2,-1.3}{\Glspl{ingredient} Workshop}{}
  \callout[10]{9,13}{-0.1,-6}{shortsword x 12, longbow x 14, round shield x 2}{}
  \callout{11,10.5}{-0.9,-1}{Gate:}{murder holes $\dicef{3}-1$}
}

\widePic{Dyson_Logos/bandit_camp}

\begin{multicols}{2}
\histEvent{5}{6}{\Glsfmttext{banditking} begins building a secret \glsfmttext{village}}

\begin{exampletext}
  \noindent
  \Gls{banditking} heard about these interesting hills from \gls{sewerthief} last \gls{cycle}, and immediately began making connections with the nearby \glspl{village}.
  The area lets out almost no light throughout the night, even with a raging fire in the middle.
  The surrounding mountains provides an early dusk, which helps keeps the covert \gls{village} cool, and keep supplies fresh.
\end{exampletext}

When the weather clears, neighbouring \glspl{village} can see the light plumes of smoke from the \nameref{banditLair}.
They gossip about it on occasion, but won't mention it to outsiders -- they suspect the money's coming from some `tax-dodging new \gls{village}', and don't mind so long as they keep buying all the food for a good price.

As \gls{banditking} returns, he stores the wagons a mile from the outpost, then takes the horses the last bit of the journey, after covering the wagons in forest leaves.
He can't trust the bandits, so he buries his coinage in the forest, and collects it before leaving to make purchases at the four neighbouring \glspl{village}.

\begin{dlist}
  \item
  \Gls{banditking} returns from \gls{town} with \dicef{12} bandits.
  He has money from \gls{sewerking}.
  \item
  Bandits drink -- each has a -1 Penalty.
  \item
  Bandits have begun to fight.
  If \gls{banditking} is present, he breaks it up.
  \item
  The bandits kill, then eat, a wandering monster.
  \item
  \Gls{banditking} returns with \dicef{12} men, on horseback.
  \item
  \Gls{banditking} sneaks out with some bags of cash, to bury it in the forest.
\end{dlist}

\end{multicols}
