\sidequest[Town,Roads,Forest]{Entitlement}

\noindent
The \gls{whiteplains} \glspl{warden} cannot survive the tax hikes imposed on them when taking their boats through \gls{town}, so they have sent two of their most devious agitators to stir up trouble.
A \pgls{guard} \gls{jotter} -- \glsentrytext{traitor} -- has decided to join them, in return for promotion to Overseer once they have risen to power, and become \glspl{warden} of \gls{town}, and \gls{valley}.

Throughout this story, they slowly dismantle the existing power structures.

\sqpart{Roads}% AREA
{Rotten Breath}% NAME
{\Glsentrytext{traitor} sends the party to find a cure for his breath}% SUMMARY

\label{artPart1}
\begin{exampletext}
  When \pgls{guard} Rider reported finding a ruined temple%
  \footnote{See \vpageref{necromancers_lair}.}
  to \gls{traitor}, he went to investigate with \gls{sewerking}.
  At first, it appeared abandoned, so \gls{sewerking} picked up some interesting items he found in the hall.

  A moment later, a swarm of stirges swarmed around \gls{traitor}, and their bite carried an infection.
  \Gls{traitor} now has \textit{Breath Rot}.
  The two fled, carrying statues and a magical \gls{artefact}%
  \footnote{See \vpageref{The Bladder Skull}.}
  but \gls{traitor} still has foul breath from a disease which will slowly suffocate him to death.
\end{exampletext}

The \gls{jotter} awakens the troupe rudely, and gives them a foul lecture, with stinking breath.
He needs them to march, as fast as they can, and go to a spot past the \gls{edge} where Screeching Moss%
\exRef{judgement}{Judgement}{screeching_moss}
grows.
Screech Moss is the only thing \gls{traitor} knows about which can cure his disease.

How far the \glspl{pc} must march depends on where they start, and how well they can navigate,%
\exRef{core}{Core Rules}{navigate_land}
but the moss should be somewhere close.

\paragraph{If the troupe fetch the moss within a couple of days,}
\gls{traitor} rewards them with a longsword each, then asks them to go immediately to \gls{town} to request \gls{forestpriest} create a cure for him, and gives them a single note stating they have official business.%
\footnote{The \gls{guard} should not usually enter towns without official business.}

\paragraph{If the troupe enter \gls{town},}
they will find \gls{forestpriest} in the \gls{doulaShop}, not far from \gls{pig}.

\paragraph{If the troupe fail to make it back within a couple of days,}
\gls{traitor} will be furious with them, but will find another group of \glspl{guard} to bring him a cure.

\begin{boxtext}
  In the far distance, a trading caravan approaches.
  You can see the head rider's long hair trailing behind him in the \showTemperature\ wind.
  Both coaches have the usual archer on the top, though they don't look like \glspl{guard}.
\end{boxtext}

\sqpart{Roads}% AREA
{Art Collectors}% NAME
{\Glsentrytext{sewerking} introduces himself as a fence}% SUMMARY

\begin{exampletext}
  After raiding the \nameref{necromancers_lair} with \gls{traitor} (\vpageref{artPart1}), \gls{sewerking} stashed the \gls{artefact}, and decided to sell his more mundane (and valuable) prizes in \gls{lakeside}.
  He travels by road to avoid the heavy taxes levied in \gls{town}.%
  \Gls{lakeside} always has someone willing to buy valuable items, without too many questions.%
  \footnote{See \vpageref{lakeside}.}
\end{exampletext}

\setcounter{wounds}{2}

\sewerking

\humanarcher[\npc{\T[6]\Hu}{\arabic{noAppearing} \glspl{whiteBandits}}]

\Gls{sewerking} greets the troupe in a friendly way, and explains he's going to \gls{lakeside} to sell his wares for a `client'.
He refuses to divulge any information about this client, then begins hinting that if the troupe ever run into anything valuable, and need to sell it, he can be very discrete.

\begin{speechtext}
  If you brave warriors ever need to sell any `paintings' you find, you can always find me in \gls{whitehorse}, in \gls{town}.
  Just ask for me, and they'll show you right in.%
  \footnote{This is simply not true -- he keeps a very low profile.}

  Anyway, it's a dangerous road.
  Fancy turning the other way and joining me?
  You know, all the work you do in the \gls{guard} has real value.
  People don't tell you that enough, but you guys save everyone, every day, and nobody says `thank you'.
  Why don't you come and protect people on this road, instead of that one, and I'll say `thank you', at the end.
\end{speechtext}

\Gls{sewerking} then offers the troupe 1~\glspl{sp} per mile, in total, if they join him till \gls{lakeside}.
He will only travel by road, so he can avoid \gls{townmaster}'s taxes.

The length of the journey depends on how far this scene takes place from \gls{lakeside}.
\Gls{sewerking} takes a route not too far, or close to town, so encounters should consist of traders as much as beasts.

\paragraph{If anyone asks about the archers,}
\gls{sewerking} explains jovially.

\begin{speechtext}
  We come from the Temple of `Odd-Job', to save people from the god of messing-about and time-wasting!%
  \footnote{The characters will understand that this is a joke.}
\end{speechtext}

\paragraph{If the party press the issue,}
\gls{sewerking} explains that he comes from \gls{whiteplains}, and while his family were \glspl{warden}, they have become poor, due to the high taxes imposed by \gls{town}, so now he travels and takes work where he can, and hires people to help him.

\paragraph{If the \glspl{pc} abandon their mission,}
the next time they see \pgls{jotter}, the leader will have some explaining to do.
They should roll \roll{Intelligence}{Deceit} (\tn[12]), or suffer a demotion.
Fodder who behave in this way (the lowest rank) will find themselves escorted to the \gls{court} in \gls{town}, where \gls{townmaster} (or some other \gls{warden}) will sentence them.%
\exRef{judgement}{Judgement}{pitOfJustice}

\paragraph{The wagons hold,}

\begin{itemize}
  \item
  20 days' rations.
  \item
  2 ancient human skulls, with red stones inserted around the crown.
  \label{skullCrown}
  \item
  A stone statue of a half-dead man in repose, in a coffin.
\end{itemize}

\begin{boxtext}
  As the Sun casts red over the forest, darkness closes around you.
  Then in the distance, fire, then another, not far off.
\end{boxtext}

\sqpart{Forest}% AREA
{Guild Consciousness}% NAME
{\gls{sewerthief} talks politics}% SUMMARY

\Gls{sewerthief} wants a promotion, so he has taken on the dangerous mission of tracking down a griffin eyrie.
Since he's alone in the forest, he lights two fires, fairly far apart, then crawls under a little bush to hide.
His hope is that any predators in the area will wander up to the fire, and not him.

\sewerthief

\Gls{sewerthief} speaks to the troupe about \gls{lostcity}, then soon after -- politics.

\begin{speechtext}
  ``Just think about how wonderful it must be if all of this were a big city, with gardens, just like \glspl{warden} have, and we weren't sitting in the dark, away from the fires'', he moans.

  You know they say we can become \glspl{warden} by building a new \gls{village}, but I've never really seen it.
  We don't become \glspl{warden} really, and none of the \glspl{warden} I've seen ever started in the \gls{guard}.
\end{speechtext}

\sqpart{Roads}% AREA
{The Deal}% NAME
{The \glsentrytext{whiteBandits} request help}% SUMMARY

The \gls{whiteBandits} have gotten in a fight with the \gls{guard}, and both sides have left in a bad state.
They don't like the idea of two bandit rings in the area, so they plan to follow the \gls{whiteBandits} quietly, and kill them in their sleep.

\begin{boxtext}

  As you top the next hill, a group of six men wheel round and ready their bows at you, before their commander calms them.

\end{boxtext}

\Gls{sewerking} has noted he's being followed, so when he sees the party, he acts friendly, pretends to be a member of the Weapons Guild from \Gls{whiteplains}, and hopes they can travel together until the danger has passed.
He explains the situation while telling them not to look behind (``the bandits might notice you've spotted them!''), and asks for their help in formulating a plan.

\paragraph{If the \glspl{pc} ask more about his background,}
he tells them his current business is top-secret.

\sewerking

\humansoldier[\npc{\T[12]\Hu}{12 Woodspy Bandits}]

\paragraph{If the party agree to accompany the \gls{whiteBandits},}
then \gls{sewerking} stays with them for a day, but makes sure they do not follow him all the way to their secret home, and avoids town at all cost in case someone recognizes one of his men.

\paragraph{If the party push for a fight,}
they will have one.

\iftoggle{core}%
  {To easily resolve fights between \glspl{npc}, see the \textit{Judgement} book, \autopageref{npcfights}.}%
  {}

\begin{boxtext}
  A dead caravan lies ahead, with dead horses in front, and dead men at the side.
  Every wagon, person and horse has been filled with arrows.
\end{boxtext}

\sqpart{Roads}% AREA
{Dead Nobles}% NAME
{\Glsfmtplural{warden}' bodies float down a river}% SUMMARY

\Gls{sewerking} has pulled up a supply of diseased mushroom, and \gls{banditking} has poisoned an entire \gls{warden} family, before laying waste to the entire family, including servants.

\sqpart{Roads}% AREA
{Political Positions}% NAME
{\Gls{sewerthief} gauges how the troupe feel about dead \glspl{warden}}% SUMMARY

\Gls{sewerthief} approaches the crew shortly (or immediately) after they saw the \gls{warden} family dead.
He offers no firm opinion, but only gauges how they feel about the situation, then reports their attitudes to \gls{banditking}.

\sqpart{Roads}% AREA
{\gls{vlg} Dry Inkwells}% NAME
{When every \glsfmtplural{jotter} lies dead, the troupe discover freedom}% SUMMARY

The \gls{whiteBandits} have finally pulled off their plan to have every \gls{jotter} in \gls{valley} killed in a single night.
The troupe find one such \gls{bothy}, with a short clue as to the culprit.

\sqpart{Roads}% AREA
{Call to Aid}% NAME
{The troupe find \gls{banditking}'s men acting as the \gls{guard}}% SUMMARY

The troupe receive an order to help a \gls{village}, but upon arrival, find only \gls{banditking} and his troops have solved the issue.

If a road has become blocked by \pgls{village} inhabited by monsters, then select that road to be fixed.
Otherwise, just fill in some seasonally appropriate monster to have terrorized the \gls{village}.

\sqpart{Town}% AREA
{Bandits Caught}% NAME
{The bandits who plagued the countryside have been imprisoned}% SUMMARY

\label{banditsCaught}

\textbf{Background:}
The \glspl{pc} have captured \gls{banditking} alive.

\begin{boxtext}

  Hear, ye!  Hear all!

  Bandits who roamed the highways, lead by a man known as \gls{banditking}, have been apprehended.  The leader shall be drawn and quartered by week's end, and his companions hanged that night.

  Bakers are henceforth forbidden from purchasing the flour of the Quennome region, and any found doing so will be charged with consorting with elves.

  The temple of Alass\"e invites any charismatic men or women to aid the festivities, as playwrites and attractive actors are required for the upcoming festivities (not you, Margaret!).

\end{boxtext}

\Gls{banditking} will not be killed by law enforcement.
Those in \gls{pig} will inform \gls{sewerking} long before, and the rescue will commence as the bandits in the sewer storm the guards' holding.
Meanwhile, if \gls{necromancer}'s lair survives, the other bandits await instructions there.

\humansoldier[\npc{\T[10]\Hu}{10 Bandits}]

The only way for the characters to secure \gls{banditking}'s demise it to watch the guards' station all night.
If they do so, ten bandits stage an attack during the night.

\paragraph{The Distraction} starts by using ogre dust in three places in town to distract the local guards.

The attack begins once there are only ten guards left in the station.
\Glsentrytext{sewerking}'s men arrive, ready to break everyone out underground and take off into the nearest entrance to the sewer.

\stopcontents[sq]


