\section{Cinderfilch \Glsfmttext{broch}}

\mapNotes[\Large]{
  \huge Cinderfilch's \glsentrytext{broch}/78/96,
  Lower Block/08/46,
  \ref{cinderOne}/09/19,
  \ref{cinderTwo}/09/60,
  \ref{cinderThree}/50/19,
  \ref{cinderFour}/50/90,
  \ref{cinderFiveSide}/94/19,
  \ref{cinderFive}/84/24,
  \ref{cinderSix}/84/77,
  Middle Block/5/00,
  Upper Block/9/47,
}

\widePic{Dyson_Logos/broch_map}

\begin{multicols}{2}

\noindent
The \gls{guard}'s chief duty lies in maintaining \glspl{broch}.
Traders and travellers need these \glspl{broch} to stay somewhere overnight when the next \gls{village} lies too far away.

The \glspl{pc} will begin in the Cinderfilch \gls{broch} (named after \pgls{warden}'s daughter, who was eaten by \pgls{woodspy}).
The locals know it as being particularly antagonistic towards horses, which is a problem for any trader whose wagon does not double as a horse-stall, capable of withstanding the curiosity of \pgls{crawler}.
If the troupe happen to be here when that happens, they'll have to stay outside, with lit fires all around the \gls{broch}, to make sure the horses stay safe (people value horses far more than \gls{guard} Fodder).

Here the \gls{jotter} will give them orders to start on random missions, from room \ref{cinderThree}.%
\exRef{judgement}{Judgement}{NGmissions}
These might be easy (accompany these traders), or more challenging (guard that \gls{village} for a week), but once they step onto the road, they should have a little freedom to engage with the various \glspl{sq} before long.

The \gls{broch} contains:

\begin{enumerate}
  \item
  Six \glspl{guard}, chatting.
  \label{cinderOne}
  \item
  Straw and firewood.
  \label{cinderTwo}
  \item
  \Gls{jotter}'s office.
  \label{cinderThree}
  \item
  Archers' outpost, with plenty of arrows and hunting bows of every size.
  \label{cinderFour}
  \item
  Food storage (\rations, \rations, \rations, et c.)
  \label{cinderFiveSide}
  \item
  Two \glspl{ranger} currently passed out.
  \label{cinderFive}
  \item
  Bedding for three people, or a dozen \gls{guard}.
  Archery equipment and firewood for the beacon at the top.
  \label{cinderSix}
\end{enumerate}

\end{multicols}
