\subsection{\Glsentrytext{forestpriest}'s Camp}
\label{lostcity}
\mapPic{t}{Dyson_Logos/forgotten_city}{
  \ref{fallen_tower}/33/73,
  \ref{lostGriffins}/77/75,
  \ref{lostManaLake}/70/35,
  \ref{lostDoor}/63/21,
}

\textbf{Background:}
A city once stood in this area, evidenced by the stone ruins all around.
In this particular spot, a small group of alchemists gathered study material and crafted experiments; it was the prototypical \gls{college}.

\Glsentryfirst{forestpriest} has wondered for a long time about how \gls{lostcity} fell -- did elves destroy it out of malice, or did they destroy it because humans in the area began opening portals to the dangerous nura realms?
He has found the area by scouting in bird form for many months, all around the area, and determined its function.

One barrier to \gls{forestpriest}'s question remains; the alchemical basement swarms with undead.

\Gls{forestpriest} first tried to trick some of the Woodspy Bandits inside to find out the truth (he told them the place contained a lot of treasures).
Unfortunately, they never came out again.

\begin{boxtext}

  The trees and vines here cling to blocks of stone, as if trying to crush the last remnants of civilization.
  You sometimes wander for so long without seeing a single brick that you forget you're anywhere but a normal forest, but then another errant stone, or the marble hand of a statue juts up to remind you of the ghosts resting in this place.

  In the distance, a little plume of smoke rises, suggesting a camp fire.

\end{boxtext}

\paragraph{If the \glspl{pc} head towards the smoke}
anyone with MP will feel it recharging by the second.

\mapentry[fallen_tower]{The Fallen Tower}

\Gls{forestpriest} camps here alone, in the abandoned tower.
It still has a single room, with a stone ceiling standing strong, where a small tapestry showing a prayer to Sylph displays on the wall.
This simple tapestry with a children's rhyme (saying thanks to all the animals -- even the dangerous ones) functions as a shrine to Sylph.

\Gls{forestpriest} keeps spare torches at the side.

The nearby hidden trapdoor underground cannot be discovered from above -- in fact it's so tightly covered with rock, then earth, then well-made roofing, that it's nearly waterproof.

\begin{speechtext}

  The humans say that the elves tore the city down because the elves disliked humans growing so powerful.

  The elves say that the humans used nasty magics to open portals to the nura realm, and goblins spilled out.
  They say the city was already mostly ruined, and they had to save the area through magic.

  I feel the answer lies close.

\end{speechtext}

\paragraph{Once the \glspl{pc} approach,}
\gls{forestpriest} replies with a friendly greeting, sizes the troupe up.
He won't tell them the plan, or how to find the hidden entrance to the alchemical laboratory unless he trusts them.

\paragraph{If the \glspl{pc} encounter trouble with any beasts,}
\gls{forestpriest} can almost certainly deal with them using his knowledge of Aldaron.

\mapentry[lostGriffins]{Griffin Grove}

Two griffin couples live in this bountiful grove, and are tending to their nests (assuming the current season is not cold).
The trees are full of large, ripe fruits.

\griffin[\npc{\T[4]\A}{Four Griffins}]

\paragraph{If the \glspl{pc} approach during daylight hours,}
the griffins perk their heads up, but they can be threatened with a Strength + Wyldcrafting Team Roll (TN 10) by shouting and banging weapons together).

\paragraph{If the \glspl{pc} enter to get the food,}
the griffins attack together.

\mapentry[lostManaLake]{The Glistening Mana Lake}

This lake blossoms with magical energies, and regenerates 2 MP per turn to anyone nearby, and 4 MP to anyone touching it.%
\iftoggle{aif}{%
  \footnote{See \textit{Fenestra}, \autopageref{mana_lake} for more on mana lakes.}
}{}

Four woodspies rest just under the water's surface, camouflaged to look exactly like the base of the pool.

\paragraph{Anyone getting close to the lake}
must make a Wits + Vigilance roll, TN 10, to spot them.
Failure, of course, means being dragged under water by the first.
Anyone helping must roll or be dragged underwater by the second.

\paragraph{If \gls{forestpriest} walks with the characters,}
he can use his Aldaron magic to immediately put \emph{one} Woodspy to sleep by spending 2 MP, but he won't waste further mana on the task.

\paragraph{If the troupe want to rush past the woodspies without fighting,}
get a Speed + Athletics Group Roll (TN 8, plus 1 per person after the first).

\Gls{forestpriest} warns them to shout when they want to exit, so he can make sure the door is clear, otherwise the woodspies will be waiting for them the moment they exit.

\mapentry[lostDoor]{The Old Door}

The old door has brass braces and such solid oak that it has survived through centuries of rot and nastiness.
Despite the Woodspy Bandits recently opening the door, it has such a covering of mud that spotting it requires a Wits + Vigilance Team Roll (TN 10).

\begin{speechtext}
  This old door leads to the basement of some old alchemical research building.
  If a portal to the nura realm exists, it exists here.
  I need to know if it really does contain such a portal.

  If you could go down, we could know for certain what the answer is.
\end{speechtext}

\paragraph{If the troupe ask for payment,}
he says he's already paid all the money he can to local bandits to find out what's in the well, and they never returned.%
\footnote{Specifically, these were the Woodspy Bandits.}
Therefore, there should be plenty of silver on their bodies, if the troupe can only find the corpses.

\paragraph{If the troupe ask him to come with them,}
he'll only go down with the troupe if he has to, and if he trusts them, but will not allow himself to be surrounded by people he doesn't trust and could stab him in an instant.

\forestpriest

\paragraph{If the troupe ask him to clarify the plan,}
he explains that if he can get witnesses to spread the word about what really happened in \gls{lostcity}, he will have the political backing to put a stop to expansions into this area.

If men return here to uncover the ruins containing portals, they may repeat their past mistakes.
If the elves have destroyed the area in the past, they may do so again.

\paragraph{If asked about turning people into animals,}
he refuses to speak on the subject until after the contents of the old wooden door have been thoroughly inspected.


