\section{\Glsfmttext{greentower}}
\label{green_tower}

\begin{multicols}{2}

\noindent
\Gls{greentower} exists wherever the \glspl{pc} discover it when you start its \gls{segment} (\vpageref{green_tower_sq}).
\Gls{southSeeker} will arrive after \pgls{interval}, so the \glspl{pc} may have to endure an encounter before meeting him.

\mapPic[\Large]{t}{Dyson_Logos/green_tower}{
  \Huge\ref{greenGrounds}/62/55,
  \ref{greenConservatory}/26/35,
  \ref{green1}/10/35,
  \ref{green2}/23/85,
  \ref{green3}/84/84,
  \ref{greenTop}/90/24,
  \ref{underGreenTower}/01/35,
  \ref{underWatcher}/44/02,
  \ref{underPriests}/50/02,
  \ref{underDoors}/58/02,
  \ref{underSpiral}/68/07,
  \ref{Abyss}/65/00,
}

\histEvent{295}{9}{Priests at the temple of \glsfmttext{eldren} discover a deep pit, where highly valuable glowshrooms grow \glssymbol{eldren}}

\begin{exampletext}
  Some centuries past, in the time of \gls{lostcity}, a temple of \gls{eldren} stood here, and the priests commissioned a catacomb.
  Before the happy-go-lucky \gls{healersGuild} we know today, this temple had real priests who studied the magic of the Death Sphere.
  Priests of high standing would volunteer to continue serving the temple, even after death; they began with some kind of vow, then slowly passed into undeath.

  As workers excavated dirt for the new catacomb, they stumbled into a cave-shaft, going straight down, where little green-glowing mushrooms grew.%
  \exRef{judgement}{Judgement}{glowshroom}
  These `glowshrooms' serve as Fire \glspl{ingredient}, so the \glspl{helper} started `fishing' for them, with little fishing hooks.

  Soon after, little goblin heads pocked their noses up from the bottom of the shaft, and also began to collect mushrooms, but the priests of \gls{eldren} did not intend to share.
  The priests took a vow to ensure the temple would pick the glowshrooms, and nobody else.

  The temple prospered, with a steady supply of \glspl{ingredient} of the Fire Sphere.
\end{exampletext}

\subsection{The Tower}

\paragraph{Once they meet \gls{southSeeker},}
he will have to ask them to keep \gls{greentower} a secret.
He comes up with any number of excuses -- `the \gls{guard} \glspl{jotter} won't accept the need for \pgls{broch} here', `the locals need \pgls{broch}', `the \gls{templeOfCuriosity} want a private research outpost', and eventually admit that the \gls{templeOfCuriosity} want to know more about \gls{lostcity}.

\mapentry[greenGrounds]{Outer Grounds}

The area around the tower contains piles of rock which masons have collected from the surrounding ruins.

\paragraph{The masons}
work outside during the day, and will almost certainly notice the \glspl{pc} walking towards them, from the forest.
And with no roads in, they will feel immediate suspicion.
Seeing \gls{guard} uniforms will only deepen their worries.

Unless the \glspl{pc} give them a reason not to, they masons will act friendly, offer them a drink on the top floor (area \ref{greenTop}), lock the trapdoor from below, and leave them to the wind and the griffins.
If \gls{southSeeker} returns, he will have the masons release them, but ask they don't reveal the tower's location to anyone.

\humanfarmer[\npc{\T[6]\M\Hu}{6 Masons}]

\boxPair[t]{
  \southSeeker

}{
  \showStdSpells
}

\paragraph{If anyone searches for a passage below,}
they will find a rock covering, with \pgls{weight} of 12.
The \glspl{pc} will have to use \pgls{bandAct} to lift it.

\mapentry[greenConservatory]{Conservatory}

Overnight, the labouring equipment rests here.
The lock is a simple knot tied on the inside.
Getting in is easy -- \roll{Intelligence}{Larceny} (\tn[6]) to slide a knife through a crack and cut the rope.
Getting in undetected requires more thinking -- \roll{Intelligence}{Larceny} (\tn[14]) to thread a series of strings through, and create the leverage to undo the knot.

\mapentry[green1]{First Floor}

Basic straw-stuffed beds, clothes, and 10 longbows lie here (+2 Damage).
Half a dozen barrels contain fermented fish from \gls{lakeside}, salted meats, a wine-stew mix, and pickled vegetables.

\mapentry[green2]{Second Floor}

The men sleep here, though it's eventually planned as a station for lower-level archers.

\mapentry[green3]{Third Floor}

The top floor provides a place for \gls{southSeeker}, overseer of the operation, to get a good look at the surrounding area.
This is also where he keeps a stockpile of weapons:

\begin{description}
  \item[Wall Rack]
  with
  20 longbows
  \item[Leather bundles]
  with
  50 longswords
  \item[Wooden Chest 1]
  has
  50 suits of partial leather armour
  \item[Wooden Chest 2]
  has
  50 suits of partial chain armour
  \item[Small Chest]
  contains:
  \begin{itemize}
    \item
    \lootMagic
    \item
    \lootMagic $x 3$
    \item
    \lootMagic
    \item
    \lootTalisman
  \end{itemize}
\end{description}

\addtocounter{treasure}{-1}
\Gls{southSeeker} purchased the \lootTalisman\ recently, and left it here to ensure none of the \gls{sunGuard} would search him in \gls{town}, and take it from him.

\showTalisman

\mapentry[greenTop]{Top Floor}

This green roof meshes with the local trees for some distance around, but like any other camouflage, it seems obvious once you look at it.

From the top of the roof, anyone can see for miles around.
They can't see people or creatures sneaking about, but they can see \glspl{basilisk} and groups of men without fail, even by moonlight.

\subsection{Old Catacombs}

\mapentry[underGreenTower]{The Stairs}

\histEvent{287}{3}{The `\glsentrytext{goldenPriests}' of \glsfmttext{eldren} begin an eternal war with goblins for the mushrooms \N}

\begin{exampletext}

  Despite the wealth generated by the temple from their supply of glowshrooms, the surrounding civilization fell, as so many do, so the town and the tower fell to ruin, but the \glspl{goldenPriests} at this temple had taken a vow to continue their work, even past death.
  They would pick the mushrooms and destroy anyone who got in their way.
  They forgot the town, and forgot their own names, but an enchantment kept them focussed on their single goal -- pick mushrooms, and drink the souls of anything that interferes with this mission.

  And as the goblins below continued their attacks, the priests would kill them, and turn them into ghouls.
  These mindless undead creatures would move towards the nearest living thing -- often throwing themselves into the pit when goblins began to climb up.

  Whenever the larger hobgoblins attacked, the \glspl{goldenPriests} would begin with \pgls{spell} to turn them semi-undead, and then kill them, creating a ghast.%
  \exRef{judgement}{Judgement}{ghast}
  Finally, they would use spells from the Mind Sphere to have the ghast pick more mushrooms and place them in the chest.

  Nobody from the temple above comes down to collect the glowshrooms any more, but the \glspl{goldenPriests} continue their mission, to collect all they can, while the valuable mushrooms sit in a rotting pile on top of a chest.
\end{exampletext}

Many \glspl{cycle} of growth and soil-spillage have left a thin layer of mucus on the stairs.

\paragraph{Anyone descending}
must make a \roll{Dexterity}{Athletics} roll, \tn[8], or fall down one staircase, taking $1D6-2$ Damage.
Characters can get a bonus for proper equipment, such as rope.

The air down in the tomb has become so dry and foetid, that anyone spending time there gains 2~\glspl{ep} per \gls{interval}.
Leaving the place open to air out will clear away the bad air from \pgls{area} below every \gls{interval} (so leaving it open for 3 \glspl{interval} will clear 3 \glspl{area}).

The stairs and all hallways here are rather narrow, making weapons difficult to swing.%
\exRef{core}{Core Rules}{enclosedcombat}

\mapentry[underWatcher]{The Watcher}

The Pious Ghast guards this tomb from inside a closet.
He swore to protect the \glspl{goldenPriests} by waiting here in the dry air with a body so seized up that he cannot move.
But with a little time to shuffle his bones and crack his own skin, he will find enough flexibility to walk out of the closet door.

\mapPic{b}{Dyson_Logos/green_secret}{
  \rotatebox{15}{\nameref{underGreenTower}}/09/55,
  \ref{underGreenTower}/17/43,
  \rotatebox{-15}{\nameref{underWatcher}}/09/02,
  \ref{underWatcher}/18/09,
  \rotatebox{15}{\nameref{underPriests}}/20/78,
  \ref{underPriests}/28/57,
  \rotatebox{0}{\nameref{underDoors}}/40/02,
  \ref{underDoors}/375/31,
  \rotatebox{-15}{\nameref{underSideRoom}}/68/85,
  \ref{underSideRoom}/56/73,
  \rotatebox{-90}{\nameref{underSpiral}}/90/43,
  \ref{underSpiral}/81/40,
  \rotatebox{25}{\nameref{Abyss}}/67/49,
  \ref{Abyss}/68/36,
}

\paragraph{Opening the door}
requires a \roll{Strength}{Crafts} roll (\tn[14]), as the door is bolted shut from the inside, and will have to be busted in.

\paragraph{If a player insists on `picking the lock'}
(despite the lack of lock) they roll \roll{Intelligence}{Larceny} (\tn[16]).

\begin{boxtext}
  You swing the door open to find a highly decorated corpse with a pendant to \gls{eldren} made of gold, with bone strung along the copper thread.
  Silver earrings adorn his side, and his hands, in the classic death pose, have one golden ring on each finger.
  The clothes look like they were once silk, and the helmet's leather covering seems to be a human face, stretched out and tanned.
\end{boxtext}

\paragraph{If the \glspl{pc} stab the corpse,}
they can kill it\ldots after a few stabs.

\paragraph{If they pass the door,}
the Pious Ghast animates and comes to kill them.%
\footnote{I have seen three groups of players go through this area, observe the corpse, and walk on, leaving him unscathed.}

His use of a shortsword also means he will not gain any penalty from the narrow hallway.

\Person{\npc{\M\D}{The Pious Ghast}}%
  {{3}{2}{1}}% BODY
  {{0}{1}{0}}% MIND
  {%
    \set{Melee}{1}
    \set{Academics}{1}
    \set{Stealth}{2}
    \set{Vigilance}{1}
    \shortsword
    \completeplate
  }% SKILLS
  {\stunningstrike, \adrenalinesurge}% KNACKS
  {pendant necklace worth 2~\glspl{gp}, silver earrings worth 1~\gls{gp} each, and 2 golden rings worth 5~\glspl{gp} each}% EQUIPMENT
  {\undead}% ABILITIES

\mapentry[underPriests]{Hall of the \Glsfmtplural{goldenPriests}}

A long time ago, onlookers came here to gawk at the splendour of a glorious afterlife.
The priests of \gls{eldren} who gained the highest honours of the temple would remain here to guard it forever.
Each stands decked in golden jewellery.

\begin{boxtext}

  Five dead men, mummified and covered in golden jewels, stand in each of five enclaves at the side of the room.
  You notice head wounds and missing limbs upon some of the bodies.

  Little spears litter the area, as if a battle has taken place here.

\end{boxtext}

\demilich[\npc{\D\F\glssymbol{eldren}}{Demilich Delilah}]
{
  \footnotesize
  \showStdSpells[\setcounter{enc}{1}]
}

\demilich[\npc{\D\M\glssymbol{eldren}}{Demilich Jonah}]
{
  \footnotesize
  \showStdSpells[\setcounter{enc}{1}]
}

\demilich[\npc{\D\F\glssymbol{eldren}}{Demilich Tamar}]
{
  \footnotesize
  \showStdSpells[\setcounter{enc}{1}]
}

\paragraph{Once the \glspl{pc} enter,}
the demiliches cast hostile spells at them (their presence does not help extracting mushrooms).

\paragraph{Complementing the priests}
breaks the Mind spell, which has them focussed on their single task.
All of them have the code `Noble', so anything which would earn a player \glspl{xp} serves to break this spell.%
\exRef{stories}{Stories}{noble}
However, like all undead, the priests are deaf, so the \glspl{pc} can only communicate with the use of writing or spells (such as \textit{Soul Specks}).

%! Rephrase
If the troupe manage to compliment them, the \glspl{goldenPriests} picking mushrooms, and take some time to re-examine their unlives, and discuss (silently, with the unknowable communications of the undead) what they want to do, if anything.

\mapentry[underDoors]{Dirty Tunnels}

\begin{exampletext}
  These openings once had doors to hide the secret items given to the \gls{healersGuild}, but the centuries of battle destroyed the doors.
\end{exampletext}

Strange and rotten spears, made from unknown plant-matter, litter the area, along with rotten mushrooms.
A green glow emanates through the narrow paths.

\mapentry[underSideRoom]{Side Room}

\begin{exampletext}
  The natural tunnel was further excavated in order to horde the priests' treasures.
  The glowshrooms collected filled up the chests, but the priests just kept piling them on top, and ordering their undead hobgoblins to do the same.
\end{exampletext}

\begin{boxtext}
  An alcove to your left glistens, as shelves at the far side hold coinage and displays of precious jewellery.
  In front of them, a massive pile of rotting mushrooms stands as high as a dwarf -- those on top still glow a little, but the rest are overgrown with mould.

  Two lines of little creatures shuffle from the shadows, with pointed ears, bleach-white skin, drooping jaws, and a black abyss instead of eyes.
\end{boxtext}

At present, shelves at the back contain \lootMedium, \lootJewellery, \lootJewellery, \lootJewellery, \lootJewellery, and \lootBig.

The room also contains 11 undead goblins, standing ready to kill any nura who come up from the tunnel, or just anyone who enters.

\undeadgoblin

\undeadhobgoblin

\mapentry[Abyss]{Abyss}

This hole leads down a sharp and muddy incline, travels past 100 \glspl{step} through glowshrooms, and ends in a goblin warren.

\paragraph{If the \glspl{pc} dislodge and drop a mushroom,}
they may see shadows moving below, and wonder who lives down there.

\paragraph{If they somehow get down the hole alive,}
they have entered the goblin realm, and do not speak the language.
They are surely doomed.

\mapentry[underSpiral]{Downward Spiral}

\begin{exampletext}
  This tunnel swirls round the \nameref{Abyss}, heading down, until it ends in a barred door.
  Opening the door allows a place to `fish' for the little glowshrooms, then close the door before goblins ascend.
\end{exampletext}

\ghast[\npc{\D\N}{Hobgoblin Ghast}]

\bigLine

\paragraph{If the troupe manage to pretend they work for the \gls{templeOfSickness},}
and not alert any of the undead to their presence, they will be able to take enough glowshrooms for 10~Fire \glspl{ingredient} immediately, and one per week thereafter.

\paragraph{If any one of the \glspl{goldenPriests} die,}
the goblins kill the others and break out, and begin exploring \gls{valley}.
From then on, any encounter rolls of 3 are goblins, rather than the standard encounter.%
\exRef{judgement}{Judgement}{goblin_rating}

\end{multicols}
