\section{Village Locations}

\begin{multicols}{2}

\subsection{Markets}
\index{Market!Villages}

If the \glspl{pc} try to purchase anything from the villages, see the handout on the village market.

\widePic{Dyson_Logos/redfall}

\subsection{\glsentrytext{redfall}}
\label{redfallVillage}
\index{Redfall}

\Gls{redfall} lies safely away from the \gls{edge}, and lies close to its guardian keep where the villagers can run if serious trouble rises.
The people in the area create pottery from the rich clay deposits.

The recent hike in taxes has driven the now-hungry villagers to desperate means.%
\footnote{See page \pageref{desperatemeasures} for more on \glsfmttext{nurabaron}'s draconic taxes.}

\begin{boxtext}
  \Gls{redfall} seems peaceful, almost idyllic, as children play next to copse of trees without any fear of beasts waiting for them inside.
  A few women collect the red earth by the river so they can process it into their famous pottery later.
  Ahead, the keep stands three stories high.
\end{boxtext}

\paragraph{When the PCs enter,}
if they look like like might be officials or soldiers of any type, the villagers act natural at first, but arrange to surround the party at the bridge.

\begin{boxtext}

  As you step onto the bridge, you see a dozen men walking behind you with large bags covering their heads and another sack in their hands.
  In front, another ten with sacks gather as well.
  Ahead and behind, they pull the rocks out.

  ``No more taxes!'', they shout.

\end{boxtext}

\paragraph{If the PCs try to reassure the villagers,}
have them roll Strength + Empathy (TN 9) to holler their message clearly to everyone present.

Failure indicates a nasty pelting, although the villagers don't intend to kill the anyone -- just drive them off.

\npc{\T[4]\E\Hu}{20 Angry Farmers}
\person{2}% STRENGTH
{0}% DEXTERITY 
{0}% SPEED
{{0}% INTELLIGENCE
{-1}% WITS
{0}}% CHARISMA
{0}% DR
{0}% COMBAT
{Projectiles 1, Crafts~1, Wyldcrafting~1}% SKILLS
{Sack-of-rocks, face-covering}% EQUIPMENT
{}

\paragraph{If the PCs ask about the keep,}
the villagers complain bitterly, but have no idea that \gls{nurabaron} has become a monster.

\paragraph{If the party attempt to persuade the villagers to assault the keep,}
they can succeed with a Charisma + Tactics roll, TN 10
(the villagers feel more confident with a strong character leading them).
Of course the villagers also know that the fortress is armed with archers, and will only agree to enter if the party have a solid plan concerning the archers.

\paragraph{If the keep ever becomes surrounded by peasants,}
\gls{nurabaron} will run out to an archer's post with a massive bag of food doused in ogre-dust.
He will pour it down, shouting apologies about the lack of food, and any villagers who eat the food will begin to turn into ogres.
If the party aren't quick, they'll be in a keep surrounded by ogres.
There isn't enough food for everyone, so after some turn into ogres, they'll start to eat the others, and many will simply flee.
This will leave ten ogres who chase the villages, ten more who bang on the gates, and ten who decide to go round the back of the keep to look fruitlessly for alternative entrances.

\mapPic{t}{Dyson_Logos/redfall_keep}{
  \huge\ref{redTower}/05/68,
  \Large\rotatebox{0}{\nameref{redTower}}/05/80,
  \huge\rotatebox{-45}{\nameref{redYard}}/34/50,
  \ref{redYard}/28/46,
  \Large\rotatebox{-45}{\nameref{redToilet}}/52/26,
  \huge\ref{redToilet}/545/34,
  \Large\nameref{redKitchen}/31/79,
  \ref{redKitchen}/30/75,
  \Large\rotatebox{-45}{\nameref{redServants}}/43/75,
  \ref{redServants}/41/73,
  \huge\ref{redChild}/84/19,
  \Large\rotatebox{45}{\nameref{redChild}}/84/28,
  \Large\rotatebox{45}{\nameref{redSmolYard}}/75/34,
  \ref{redSmolYard}/65/36,
  \huge\nameref{redHall}/63/93,
  \ref{redHall}/63/75,
}

\subsection{\Glsfmttext{redfall} Keep}

The keep contains a conspiracy: everyone in there knows that they harbour monsters, but they also know that those monsters can be cured, and that if they tell anyone, they'll lose their employment, and will either have to beg or join the \gls{guard}.

\mapentry[redTower]{Towers}

Each of the towers has two archers, ready to protect their patron, \gls{nurabaron}, as long as nobody gets too close.

\humanarcher[\npc{\T[4]\M\Hu}{2 Archers}]

\boxPair[t]{
  \nurahorse[\npc{\N\A}{Janus, the Demonic Horse}]
}{
  \NPC{\M\N}{Benjie -- ``the Toddler''}{Playful}{Fingers in mouth}{Tribe}
  \person{3}% STRENGTH
  {-1}% DEXTERITY 
  {2}% SPEED
  {{-4}% INTELLIGENCE
  {-4}% WITS
  {-3}}% CHARISMA
  {0}% DR
  {1}% COMBAT
  {}% SKILLS
  {\quarterstaff (\glsentrytext{nurabaron} gave him a stick to `play' with the guards)}% EQUIPMENT
  {}
}

\boxPair[b]{
  \nurabaron
}{
  \ogre[\npc{\T[2]\N\F}{Marjorie \& Beth}]
}

\mapentry[redYard]{Courtyard}

This open courtyard makes archery an easy job.  Anyone outside can easily be picked off if they do not have adequate shielding.

\mapentry[redKitchen]{Kitchen}

The dwindling food supplies are kept here.  They build up to monstrous amounts, then get hurriedly eaten within a day or two.  Barrels of meats, stacks of bread, and multiple bottles of wine -- nothing lasts long.

\mapentry[redServants]{Servants' Quarters}

This place holds various cots, chests, and washing equipment.  At present only six members of staff remain -- two cooks, two butlers, one diplomat,\footnote{See page \pageref{nathaniel} for Nathaniel the diplomat.} and James the tax collector.

\mapentry[redToilet]{Toilet}

This spacious lavatory comes with a runoff to the river outside.
It also hosts arrow slits to fire at intruders on the river.
Small characters (with Strength of 0 or less) can fit through the gap from outside, if they are not wearing armour.

One of the horses here was accidentally hit by some of the ogre-dust which affected \gls{nurabaron} and his family.  It ate the others, but despite the men protesting, \gls{nurabaron} has insisted on keeping it alive and very well fed.

\mapentry[redSmolYard]{Small Courtyard}

This area holds a thin, thatched root, and plenty of space for games without getting wet.
It's used as a common area by the servants.

\mapentry[redChild]{Benjie's Room}

\Gls{nurabaron}'s youngest son Benjie is only a toddler.
He doesn't understand his condition, and has no self control.
This makes him dangerous, so the family have decided to lock him in this little room.
Characters on the river or anywhere near this room can hear intermittent banging, and infant-like gurgling.

\mapentry[redHall]{Great Hall}

\begin{boxtext}

  You open the door to a massive table full of opulent food, and more food stacked on top.  Layers of bloody bones poke out the side of three layers of filthy dishes, lining the bottom of the feast.  At the head of the table, sits \gls{nurabaron}, in a meat-stained dressing gown.

\end{boxtext}

A heavy wooden door guards the entrance well, and a gate sits in front of that.  Lifting the gate takes a Strength + Athletics roll, TN 10, but the locks on the door don't give much resistance; players can pick them with Intelligence + Larceny, TN 6.  The bars are slim enough that anyone with a Weight Rating of 5 or less can just about squeeze through.

The hallways contains a long, messy dining table, covered in scraps of bones from all manner of animal.  The side alcoves contain little beds for guards to sleep in.  Four guards are in the area at any one time.

The baron can usually be found dining here, shouting at guards about some imagined insult, or just terrifying people for the fun of it.  Nathaniel, his trusted advisor, is the only one who can calm him down when he gets into a rage.

\smolMapPic{Dyson_Logos/redfall_top}{
  \Large\rotatebox{-90}{\nameref{redFamily}}/07/38,
  \ref{redFamily}/175/20,
  \Large\rotatebox{-45}{\nameref{redStorage}}/67/44,
  \ref{redStorage}/74/20,
}

\mapentry[redStorage]{Old Storage Shelves}

Here the servants rest.
The armoury was once staffed by men at arms, but now has nothing but ogre-powder and other magical items from \glsentrylong{sewerking}.
Anyone disturbing the contents of this room must make a Dexterity + Crafts check, TN 7, or risk toppling something and spilling the powder everywhere, which will affect the characters as per the Saurecanta sphere (see \textit{Fenestra}\iftoggle{aif}{\autopageref{saurecanta}}{});
specifically, they get +2 to Strength and Speed, but -4 to Intelligence and Charisma.

\mapentry[redFamily]{Hidden Family}

In the upper floor, \gls{nurabaron}'s wife Marjorie stays with three of her children -- two boys and a girl.
All are a little too dangerous to be trusted wandering alone, so only one is let out of their room at a time.

These two attack fiercely, but retreat if any bargains have been made after a single round.

The two brothers were never good at listening, and will attack with abandon, unless Marjorie is nearby to talk them down.

\ogre[\npc{\T[2]\N\M}{Richard \& Jim}]

\subsection{Redfall, Fallen}
\label{redfallFallen}

\mapPic{t}{Dyson_Logos/redfall_keep_fallen}{
  \ref{nuramancer_tower}/50/5,
  \ref{keep_ogres}/37/71,
  \ref{keep_patrol}/84/50,
  \ref{keep_prisoners}/81/16,
}

If the citizens of the surrounding lands overrun Redfall (see \autopageref{mastersBounty}), it becomes a hotbed for nura.
They eat the servants, and soon after Krela, the goblin nuramancer, arrived from one of the open nura portals in the land.

Krela eats well with the ogres, and soon builds up an ogre army.
The nura begin eating their way through the surrounding villages, while Krela transforms humans into ogres.

The central fort continues amassing arms, and the ogres throw boulders at anyone who comes too close.

\mapentry[keep_ogres]{Philosophical Ogres}

Four ogres discuss if they are men, transformed, or ogres with the stolen memories of humans.

\ogre[\npc{\T[4]\N\Hu}{Four Ogres}]

\mapentry[keep_patrol]{Patrolling Ogre}

A single ogre patrols the keep.
He will talk with anyone who looks unthreatening, as he has eaten well already.
Otherwise, he attacks.

If Nathaniel the diplomat survived, this ogre is Nathaniel, and he hates Krela for taking his position as advisor.
He will help assassinate her, but not if it means putting \gls{nurabaron} in danger.

\boxPair[b]{
  \nurabaron
}{
  \goblinnuramancer[\npc{\F\N\Gn}{Krela}]
}

\mapentry[keep_prisoners]{Prisoners}

Four prisoners await death, once the ogres become hungry enough.

\mapentry[nuramancer_tower]{Nuramancer}

The nura goblin advises \gls{nurabaron}, and will use her vantage point to cast offensive spells at anyone attacking the keep.


\mapPic{b}{Dyson_Logos/lakeside}{
  \rotatebox{-40}{\nameref{lakeSquare}}/51/45,
  \ref{lakeSquare}/46/43,
  \rotatebox{-40}{\nameref{lakeTemple}}/78/81,
  \ref{lakeTemple}/70/79,
  \rotatebox{40}{\nameref{lakeDocks}}/16/68,
  \ref{lakeDocks}/21/63,
}

\subsection{Lakeside Village}
\index{Lakeside Village}
\label{lakeside}

\boxPair[t]{
  \humandiplomat[\npc{\M\Hu}{Guildmaster Solus}]
  \label{solus}
}{
  \humansoldier[\npc{\T[4]\E\Hu}{Lakeside Soldiers}]
}

Lakeside is a small, walled, village near the \gls{edge}, with a large and proud temple to Ohta resting at its side, waiting for battle.

The tall stone walls reach 4 metres into the air.
The bridges are made of wood, and ready to burn at a moment's notice if either side of the village falls to some enemy.
The river running through the centre is not dangerous, but is strong enough to sweep almost anyone away if they try to swim against it.

Lakeside has an unusually large number of well-armed young soldiers, ready to fight for their little patch of the world at a moment's notice.
It is lead by Village Master Solus, who is also the area's leader of the weapons' guild -- a small organization who are permitted to produce weapons, which are then sold to the \gls{guard}.

The ports here provide an important trade to the surrounding areas, and the river provides a relatively safe route out of the area.
This port provides the only  source of raw iron to the town, so if the village ever perishes, the price of weapons will double.

\paragraph{If you use this area for a ghoul attack with \gls{necromancer},}
the ghouls approach underwater and come up from the river.

\mapentry[lakeSquare]{Central Square}

The town's central square contains a statue of \gls{king} looking lordly.
It was built over a level 2 mana lake, so the entire town will allow a spell-caster to regenerate 1 MP per turn, and anyone closer to the statue will regenerate 2 per turn.

As only officials of the Temple of Ohta can sell weapons, the village takes pains to show support to \gls{king}, as the weapons provide the majority of its wealth.

\mapentry[lakeTemple]{Ohta's House}

The miniature citadel houses over 1,000 swords, 2,000 shields, and 20,000 arrows, ready for sale.
The PCs can buy just about any weapon they can name here, all for the basic prices in the core rules.

\paragraph{If a PC follows the code of Ohta,}
they can pray in the temple, or donate for XP.

\paragraph{If the PCs are looking to hire a soldier,}
they will find capable people here.

\mapentry[lakeDocks]{Docks}

Here, boats from the Shale enter, carrying dwarvish spirits.

\end{multicols}

