\section{\Glsfmttext{town} Market}

\begin{multicols}{2}

\noindent
All purchases in a village require a full morning or afternoon.
Villagers chat, then barter, and finally refer the buyer to someone else.

Specialized items require a Charisma + Vigilance roll to find (\gls{tn} 12).

\begin{boxtable}[Xcc]
  \index{Clothes}

  \textbf{Clothing} & \textbf{Weight} & \textbf{Cost} \\\hline

  Peasant clothes &  0 & 1 \gls{sp} \\

  Noble clothes &  0 &  18 \glspl{sp} \\

  \label{warmClothes}
  Warm clothes &  2 &  6 \glspl{sp} \\

\end{boxtable}

\begin{boxtable}[Xcc]

  \textbf{Professional Tools} & \textbf{Weight} & \textbf{Cost} \\\hline

  Bandages & 0 & 3 \glspl{cp} \\

  Lantern &  1 &  5 \glspl{sp} \\

  Rope, 50' &  1 &  4 \glspl{sp} \\

  \hline
  \textit{Specialized} & & \\
  \hline

  Metallurgy set &  15 &  60 \glspl{sp} \\

\end{boxtable}

\index{Camping Equipment}
\index{Food}
\index{Rations}

\begin{boxtable}[Xcc]

  \textbf{Travel} & \textbf{Weight} & \textbf{Cost} \\\hline

  Cart & 13 &  13 \glspl{sp} \\

  Tent for 2 & 1 & 3 \glspl{sp} \\

  Tent for 4 & 2 & 3 \glspl{sp} \\

  Tent for 6 & 3 & 3 \glspl{sp} \\

  Rations for a day &  1 &  15 \glspl{cp} \\

  Torch & 1 & 10 \glspl{cp} \\

\end{boxtable}

\begin{boxtable}[Xc]

  \textbf{Beast} & \textbf{Cost} \\\hline
  Horse & 20 \glspl{sp} \\

  Hunting Dog & 4 \glspl{sp} \\

  Donkey & 3 \glspl{sp} \\

  \hline
  \textit{Specialized} & \\
  \hline

  War Horse & 40 \glspl{sp} \\

\end{boxtable}
\end{multicols}

\subsection{Village Weapons}

  \begin{nametable}[XXXXXX]{M\^{e}l\'{e}e Weapons}


  \textbf{Name} & \textbf{Attack Bonus} & \textbf{Damage Bonus} & \textbf{\Glsfmtshort{ap} Cost} & \textbf{Weight} & \textbf{Cost} \\\hline

  \Dagger & \arabic{weaponBonus} & \arabic{damage} & \arabic{heft} & \arabic{weight} & 2\glspl{sp} \\

  \quarterstaff & \arabic{weaponBonus} & \arabic{damage} & \arabic{heft} & \arabic{weight} & 4 \glspl{sp} \\

  \shortsword & \arabic{weaponBonus} & \arabic{damage} & \arabic{heft} & \arabic{weight} & 18 \glspl{sp} \\

  \spear & \arabic{weaponBonus} & \arabic{damage} & \arabic{heft} & \arabic{weight} & 15 \glspl{sp} \\

  \hline
  \textit{Specialized} & & & & & \\
  \hline

  \longsword & \arabic{weaponBonus} & \arabic{damage} & \arabic{heft} & \arabic{weight} & 10 \glspl{sp} \\

\end{nametable}

\begin{boxtable}[XXXXXl]

  \textbf{Projectile} & \textbf{\Gls{ap}} & \textbf{Damage} & \textbf{Weight}  & \textbf{Reload Time} & \textbf{Cost} \\\hline

  Longbow &  4 & varies & 1 & (4 -- extra Str) \glspl{ap} & 8 \glspl{sp}  \\

\end{boxtable}

\pagebreak

Cut the following animal statblocks apart, for individual use.

\begin{multicols}{2}

\settoggle{examplecharacter}{true}
\horse[\npc{\A\F}{Long Trot (Horse)}]

\settoggle{examplecharacter}{true}
\horse[\npc{\A\M}{Short Saddle (Horse)}]

\settoggle{examplecharacter}{true}
\horse[\npc{\A\F}{Becka-de-Trot (Horse)}]

\settoggle{examplecharacter}{true}
\warhorse[\npc{\A\F}{Slowin Stedy (Warhorse)}]

\settoggle{examplecharacter}{true}
\warhorse[\npc{\A\M}{Waldo (Warhorse)}]

\settoggle{examplecharacter}{true}
\warhorse[\npc{\A\M}{Witless (Warhorse)}]

\settoggle{examplecharacter}{true}
\warhorse[\npc{\A\F}{Warpig (Warhorse)}]

\settoggle{examplecharacter}{true}
\warhorse[\npc{\A\M}{Werner (Warhorse)}]

\settoggle{examplecharacter}{true}
\huntingdog[\npc{\A\M}{Stayboy (Hunting Dog)}]

\settoggle{examplecharacter}{true}
\huntingdog[\npc{\A\F}{Reaver (Hunting Dog)}]

\settoggle{examplecharacter}{true}
\huntingdog[\npc{\A\F}{Singood (Hunting Dog)}]

\settoggle{examplecharacter}{true}
\huntingdog[\npc{\A\M}{Gallop (Hunting Dog)}]

\settoggle{examplecharacter}{true}
\huntingdog[\npc{\A\F}{Forager (Hunting Dog)}]


\settoggle{examplecharacter}{true}
\donkey[\npc{\A\M}{Noway (Donkey)}]

\settoggle{examplecharacter}{true}
\donkey[\npc{\A\F}{Nochance (Donkey)}]

\settoggle{examplecharacter}{true}
\donkey[\npc{\A\F}{Feckless (Donkey)}]

\settoggle{examplecharacter}{true}
\donkey[\npc{\A\M}{Socrates (Donkey)}]

\settoggle{examplecharacter}{true}
\donkey[\npc{\A\M}{Plato (Donkey)}]

\end{multicols}

\section*{Services}

\begin{multicols}{2}

\begin{boxtext}
  It's not safe to go alone.
  Take me, at a minimum of 5 \glspl{sp} per day, plus travelling expenses.
\end{boxtext}

To buy good services, the \gls{gm} rolls your Wits + Empathy in secret.
A bad roll means you have paid for a faker, but will find out too late.

Sellswords will fight with the troupe.

Guides will escort the troupe, but may disappear any time they feel less safe \emph{with} the troupe than without them.

\begin{boxtext}
  Don't know where you're going?
  No problem.
  I know the whole area.
\end{boxtext}

\noindent
\begin{tabularx}{\linewidth}{XX}

\textbf{Apothacary} & 1 \gls{sp} / level of Intelligence + Medicine \\\hline

Poison cure & 1 \gls{sp} \\

Poison & 4 \gls{sp} \\\hline

\textbf{Fence} & \\\hline

Common item & 20\% of the item's total value \\

Identifiable valuables & 40\% of the item's total value \\

Magical item & Varies considerably, 50\% chance the item is refused \\\hline

\textbf{Boat Trip} & \\\hline

Popular trading route & $2D6-2$ \gls{sp} (reroll each day) \\

Standard stream & $3D6$ \gls{cp} \\\hline

\textbf{Guide} &  150 \gls{cp}/ day \\\hline

  Inner villages & 50 \gls{cp} \\
  Near the \gls{edge} & 5 \gls{sp} \\
  Beyond the \gls{edge} & 15 \gls{sp} \\

\end{tabularx}

\noindent
\begin{tabularx}{\linewidth}{XX}
\hline
\textbf{Hospitality} &  \\\hline

Public House & 0 \gls{cp} \\

Meal & 5 \gls{cp} \\

Barn with breakfast & 10 \gls{cp} \\

City Inn & 40 \gls{cp} \\

Fancy Room & 1 \gls{sp} \\\hline

\textbf{Minstrel} &  15 \gls{cp}/ performance \\\hline

Large audience & 500 \gls{cp} \\

Massive audience & 1 \gls{gp} \\

Creating a new song & 2 \gls{sp} \\

Illegal song & 5 \gls{sp} \\\hline

\textbf{Sellsword} & 10 \gls{sp}/ day \\\hline

Opponent & \gls{xp}$^3$ \gls{sp} \\

Illegal Murder & 10 \gls{sp} \\\hline

\textbf{Tracker} &  5 \glspl{sp} / day \\\hline

  Inner villages & 1 \gls{sp} \\
  Near the \gls{edge} & 10 \gls{sp} \\
  Beyond the \gls{edge} & 20\gls{sp} \\
\hline

\end{tabularx}


\subsection{Sellswords}

\humansoldier[\NPC{\M\Hu}{Kartog}{Lively}{Hands on hips}{Wanderer}]

\humanthief[\NPC{\F\Hu}{Quartmeg}{Sarky, dark-eyes}{Raises right eyebrow}{Seeker}]

\humanfarmer[\NPC{\M\Hu}{Somnal}{Confident}{Thumbs-up}{Noble}]

\humanfarmer[\NPC{\F\Nl}{Hrash}{Slick and inquisitive}{Spits on palm, smoothes out fur}{Paladin}]

\subsection{Guides}

\humanfarmer[\NPC{\F\Hu}{Tenleck}{Dour, short black hair}{Picks nose}{Noble}]

\elf[\NPC{\F\El}{L\'ir\"e}{Golden ringlet~hair}{Giggles}{Wanderer}]

\columnbreak

\dwarvensoldier[\NPC{\M\Dw}{Derek of Clan Ut}{Short beard, practical}{Trims beard}{Tribalist}]

\vfill\null

\end{multicols}

