\sidequest[Town,Roads]{Rising Titles}
\label{risingTitles}

The \gls{whiteBandits} and \glspl{digger} finally start pushing their plans to destabilise the area.
And how these \glspl{segment} play out, depends heavily on the \glspl{pc} political positions.
They may support some of these actions, or push back against them.

\sqpart{Roads}% AREA
{\gls{vlg} Dry Inkwells}% NAME
{When every \glsfmtplural{jotter} lies dead, the troupe discover freedom}% SUMMARY

\begin{exampletext}
  The \gls{whiteBandits} have finally pulled off their plan to have every \gls{jotter} in \gls{valley} killed in a single night.
  Each \gls{jotter} has records of where all the \glspl{guard} go, including other \glspl{jotter}.
  \Gls{traitor} compiled the information, and made a plan.
\end{exampletext}

The troupe find \pgls{bothy} with a murdered \gls{jotter}, and with some ingenuity may figure out what happened.

\begin{enumerate}
  \item
  Half a dozen bandits arrived in secret
  \hint{footprints throughout the forest show they went offroad just before the \gls{bothy}}.
  \item
  They shot at the \gls{jotter} through a window
  \hint{arrows still lie around the opening}
  \item
  and wounded the \gls{jotter}
  \hint{blood spatters mark her desk}
  \item
  then fought with the \glspl{guard}
  \hint{blood and sword-marks remain around the tree border, just beyond the \gls{bothy}}
  \item
  but ultimately, the \glspl{whiteBandits} made peace with the \glspl{guard}
  \hint{when one died, they burried him respectfully, digging a grave with some rocks on top, and leaving him money, to trick \gls{wrecan} into not taking him}
  \item
  and so the \glspl{guard} left with the \glspl{whiteBandits}, becoming part of their group.
 \hint{A dozen tracks lead away, while the \gls{jotter} lies dead}
\end{enumerate}

The players may conclude any number of things from these events, but the tracks leading away should unambiguously tell them where complete answers lie.

\paragraph{If the troupe want to track down the culprits,}
they can roll \roll{Speed}{Wyldcrafting} (\tn[8]).
Success indicates that they locate the bandits just before Sundown, while they go off-road to wash the blood from their clothes (so none are wearing armour).
A tie indicates that they must either travel overnight, or make another roll the next day at \tn[10].

\paragraph{Following the bandits back to their hide-out}
requires a \roll{Strength}{Stealth} roll, at \tn[10], +1 per day of travel.
See \vpageref{Dyson_Logos/bandit_camp} for details.

\paragraph{Confronting the bandits immediately}
results in a political conversation.
\Gls{sewerthief} and the \glspl{guard} who have just now turned to banditry don't like being forced to live outside of civilization, or how people see them.
They want better pay and working conditions, and they want to know why the \glspl{pc} don't want the same thing.

\paragraph{If \gls{sewerthief} has any reason to think the \glspl{pc} are insincere,}
he will not show them the bandit hide-out.
The \glspl{pc} must make a \textit{Group Roll} of \roll{Charisma}{Empathy} (\tn[8]).
They can get a +2 Bonus for every time any of them recall supporting \gls{sewerking}'s political beliefs.

\sqpart{Town}% AREA
{Guards, Guards!}% NAME
{The \glspl{guard} run amuck in \gls{town}}% SUMMARY

\begin{exampletext}
  The entire market has been chatting about the recent murder of all the \gls{guard} \glspl{jotter}, and how many \glspl{guard} have come to town, to drink and cause trouble.

  Three of them have recently taken to stealing at the market, though they don't have the subtlety to do anything but snatch-and-run.
\end{exampletext}

After the gossip, three of the \gls{guard} (who snuck into town by hiding in a wagon) dart past the troupe, followed by Mousebark of the \gls{weaversGuild}.
She's out of breath, so she stops to hollar at the troupe.

The three \gls{guard} will recognise the \glspl{pc}, and hide behind them, laughing like children, while Mousebark shouts at them all.

\humanmaid[\NPC{\F\Hu}{Mousebark}{young, red-faced, and angry}{stamps feed}{to retain her pride}]

\paragraph{If the \glspl{pc} do not manage to return the clothing,}
Mousebark informs the \gls{sunGuard}, who begin searching for the lot of them.

The group should roll \roll{Intelligence}{Stealth} (\tn[8]).

\paragraph{If the \glspl{pc} try to take the clothes,}
the knavish \glspl{guard} turn violent quickly.

\humanthief[\npc{\T[3]\M\F\Hu}{\arabic{noAppearing} Knaves}]

\sqpart{Town}% AREA
{Underground Assassins}% NAME
{The bandits in the sewer cut \Glsentrytext{captain}'s throat}% SUMMARY

\begin{exampletext}
  \Gls{captain} announced the previous day that he would begin harsh raids against the people living under \gls{town}.
  The \glspl{digger} didn't like that, so they've organized an assassination.

  Five men walked casually behind him as he returned home from \gls{whitehorse} with his wife, then closed in so \gls{sewerthief} could stab him in the neck.
\end{exampletext}

If \gls{sewerthief} has died, replace him with \gls{sewerking}, or some other appropriate character.

\begin{boxtext}
  You hear guards shouting ``after them!'', in the distance, and quickly scurrying feet, as a woman shouts for someone to help her wounded husband.
\end{boxtext}

\paragraph{If the characters stay to help the wounded man,}
they find \gls{captain} with a knife-wound, next to his wife.
The roll is \roll{Intelligence}{Medicine} (\tn[9]) to save his life.

\paragraph{If they run after the thieves,}
the \glspl{pc} make a Group Roll of \roll{Speed}{Athletics}.

Remember that whoever's trying to patch up \gls{captain}'s bleeding neck won't be able to join the chase.

\begin{nametable}{Running Results}
  12 & \textit{``Giving chase, you catch up to four men running from the scene of the crime.''} \\
  11 & \textit{``You run round an alley, and see them entering \gls{town}'s underground.''} \\
  9 & \textit{``You run in hot pursuit, but the attackers have disappeared down a street, into thin air.''} \\
  7 & \textit{``The attackers sprint away, leaving you running in the dark.''} \\
\end{nametable}

\sewerthief

\humanthief[\npc{\T[1]\E\Hu}{\arabic{noAppearing} \Glspl{digger}}]

\humanthief[\npc{\T[1]\E\Hu}{\arabic{noAppearing} \Glspl{digger}}]

\paragraph{If the party follow the assassins underground,}
they run to the nearest entrance -- perhaps the \gls{doulaShop} or \gls{pig} (\vpageref{sewers}).
Otherwise, this incident may remain a mystery.

\sqpart{Town}% AREA
{Bandits Caught}% NAME
{The bandits who plagued the countryside have been imprisoned}% SUMMARY

\label{banditsCaught}

The \glspl{pc} have captured \gls{banditking} alive.

\Gls{banditking} will not be killed by law enforcement.
Those in \gls{pig} will inform \gls{sewerking} long before, and the rescue will commence as the bandits in the sewer storm the guards' holding.
Meanwhile, if \gls{necromancer}'s lair survives, the other bandits await instructions there.

\begin{speechtext}
  Hear, ye!  Hear all!

  Bandits who roamed the highways, lead by a man known as \gls{banditking}, have been apprehended.  The leader shall be drawn and quartered by week's end, and his companions hanged that night.

  The \gls{templeOfPoison} invites any charismatic men or women to aid the festivities, as playwrites and attractive actors are required for the upcoming festivities (not you, Margaret!).
\end{speechtext}

\Gls{sewerking} has recently discovered an underground tunnel which leads from the \nameref{stationDungeon}'s waste-shaft, \vpageref{dunGrate}, to the underground (\nameref{sewerWaterHall}, \vpageref{sewerWaterHall}).
So this night, he and some of the \glspl{digger} will crawl up from the underground, kill any \gls{sunGuard} around, and take him underground.

\boxPair[t]{
  \ghast[\npc{\T[7]\D}{\arabic{noAppearing} Ghasts}]
}{
  \ghast[\npc{\T[7]\D}{\arabic{noAppearing} Ghasts}]
}

\sqpart{Town}% AREA
{The Dead Rise}% NAME
{\Glsfmttext{sewerking} releases ghouls upon the citadel}% SUMMARY

If the \glspl{pc} have already stolen the \gls{bskulls} or somehow disbanded the \gls{digger} movement, nothing happens here.
All remains well in \gls{town}.

Otherwise, not a single soul in the city will sleep this night.

\begin{exampletext}
  The \glspl{digger} finally finished digging the tunnel underneath \gls{town}'s citadel, where \gls{townmaster} lives.%
  \footnote{See the sewers, \gls{area} \vref{citadelTunnel} for the underground tunnel, and \gls{town}'s \gls{area}~\vref{citadel} for the citadel.}
  They waited for the \gls{bskulls} to curse them with a touch of undead (so the ghasts would not attack them), barred all the doors and hatches leading to the all-too-lively catacombs, and let the unnatural army take its course, straight into the bowels of the citadel.
\end{exampletext}

\paragraph{If the troupe try to help,}
they find \gls{sunGuard} fleeing (and trying not to be seen) and about 100 ghasts in the citadel, devouring the face of anyone they encounter.

Move through the areas, rapidly.
Everywhere in the citadel remains dark unless a screaming, fleeing, servant is present.
A few of the \gls{sunGuard} remain, but most flee.

\humansoldier[\npc{\T[5]\E\Hu}{Palace Guard}]

\paragraph{If \gls{townmaster} dies,}
check the next part.

\sqpart{Town}% AREA
{Same Old New Management}% NAME
{The troupe clear the citadel of ghasts}% SUMMARY

After \gls{townmaster} dies, his eldest surviving son, Constance, takes over leadership (with the help of \gls{captain}).

The \gls{sunGuard} barricade the citadel, and Builder Cronblight%
\footnote{Find him \vpageref{cronblight}.}
at \gls{lakeside} designates new \glspl{jotter}, who then order the \glspl{pc} to clear the citadel of the dead, along with five other \glspl{guard}.%
\footnote{The \gls{sunGuard} explain that, while the ghasts exist within the citadel, the citadel counts as `beyond the \gls{edge}', and is therefore not their jurisdiction.}

Twenty ghasts remain inside the citadel, while another thirty remain in the catacombs.
Both groups of ghasts will attack en mass, rather than splitting up.

\bigLine

At this point, the primary arc of the story has so many forks that I have no idea where your story lies.
Perhaps \gls{banditking} has no troupe left and has to make a last, desperate attempt at lowering taxes by murdering \gls{townmaster}'s heir as a warning to anyone who would overburden \gls{whiteplains} again.

Perhaps \gls{banditking} arrives with a small army, and offers to clear the citadel of ghasts in order to gain the favour of everyone in \gls{town}, then begins to sweet-talk \gls{town}'s guild leaders before making a play for leadership.

Perhaps the \gls{wolfhead} and \gls{whiteBandits} join forces and both get what they want.

Or perhaps all the primary characters died at the hands of the \gls{guard}, and this campaign comes to a halt far before the last few \glspl{segment} can even start.

However it turns out, happy gaming.
