\sidequest[Town,Roads]{Desperate Measures}
\label{desperatemeasures}


\histEvent{1}{12}{\Glsfmttext{banditking} curses \glsfmttext{nurabaron} with strength and hunger}
\begin{exampletext}
  \Gls{banditking} approached \gls{nurabaron} and asked him to join `the new \glspl{warden}', with dramatically decreased taxes.
  \Gls{redfall} receives none of the benefits, as it doesn't sit along the primary river, so \gls{nurabaron} seemed like he was in the perfect position to be receptive.

  Unfortunately for \gls{banditking}, \gls{nurabaron} took offense to the idea of deposing \gls{townmaster}, and began threatening \gls{banditking}.
  \Gls{banditking} responded with a curse.

  \begin{speechtext}
    Live off this land, as long as you can.
    This tiny place will not sustain you.

    The \gls{redfall} family will starve.

  \end{speechtext}
  This spell made \gls{nurabaron} and his family massive, muscular, angry, and clumsy.
  \Gls{banditking} took that moment to flee, leaving the \gls{redfall} \gls{warden} family cursed.

  Initially, \gls{nurabaron} enjoyed his `curse' -- he felt strong, and soon adjusted to his new size, and felt less clumsy.
  His family too, adjusted.%
  \footnote{Even his horse was affected, which has caused no end of trouble among the guards, as the nightmarish creature can now barely fit inside its own stable, and breaks out any time it feels hungry.}

  The curse came with an extra-large appetite, which seemed fine at first.
  But a family of six, with a horse, eating four times the normal amount, means they consume the food of twenty-one extra people.
  And worse, the \gls{redfall} family began to enjoy food far more than they once did.
  In a small \gls{village}, the extra consumption quickly started to put pressure on the locals.

  \Gls{nurabaron} then ran into an additional complication -- his massive proportions had made him monstrous.
  He could not show his face to other \glspl{warden}, and found it difficult to write letters.
  All correspondence had to go through a single, well-lettered servant.
  \Gls{redfall} has been mismanaged for some time.

  The staff won't reveal their \gls{warden}'s secret.
  If he becomes deposed, all the \glspl{sunGuard} who serve him would lose their position, and would most likely join the \gls{guard}.
  All the inhabitants of \gls{redfall} know something has changed, but they have no idea that the \gls{warden} family have become monsters.
\end{exampletext}

The \gls{sq} \glspl{segment} below show the echoes of a mismanaged, isolated property, where the inhabitants starve, and the staff must keep their \gls{warden}'s secrets.

\sqpart{Roads}% AREA
{Bad Bandits}% NAME
{Starvation has pushed \glsentrytext{redfall}'s residents to banditry}% SUMMARY

Foxmoss is healthy enough, but the rest of his crew of eight men look nearly emaciated.
They demand silver, or at least copper, but then quickly settle for any rations the characters might have.

\begin{boxtext}
  A single arrow hits the road ten feet in front of you with a dull thud.
  A man stands up from the bushes nearby saying ``Stand forth, and deliver!''.
\end{boxtext}

\paragraph{If the characters refuse,}
the bandits might shoot, but they're easily intimidated.
If the characters attack, the bandits flee.

Of course, these aren't proper bandits.
This is the first robbery they've attempted.
If pushed, they explain that they're really farmers in the nearby village \gls{redfall}, and the local sheriff's been demanding steadily more and more meat and grain as taxes.
They don't have the strength to go on.

\humansoldier[\NPC{\M\Hu}{Foxmoss}{pessimistic}{squints}{to stop being a bandit}]

\setcounter{wounds}{3}
\npc{\T[4]\Hu}{Emaciated ``Bandits''}
\person{1}% STRENGTH
  {-1}% DEXTERITY
  {-1}% SPEED
  {{0}% INTELLIGENCE
  {-1}% WITS
  {0}}% CHARISMA
  {0}% DR
  {1}% COMBAT
  {Crafts~1, Wyldcrafting~1}% SKILLS
  {\Dagger, (three have shortbows)}% EQUIPMENT
  {}

\paragraph{If the characters investigate further,}
they may well end up at \gls{redfall} Keep.
In that case, have them stopped at the gate, and play out the encounter below with Thorn the Seneschal.
He won't let them in the keep, but he will promise all he can if the characters complete the mission he has for them.

Wherever the troupe have encountered these bandits, \gls{redfall} Keep is nearby, so if you want to pen a map as you go, at it here.

\sqpart{Roads}% AREA
{Wrong Direction Chickens}% NAME
{A tradesman is taking chickens \emph{from} town to \glsentrytext{redfall}}% SUMMARY

\Gls{redfall} needs a lot of food to keep \gls{nurabaron}'s family fed, so they have started ordering more food.
Normally, \glspl{village} feed the towns, but in this case the town is feeding the village.

\begin{boxtext}
  The road is speckled with light rain, and you pass by various traders.
  All of them are coming from \gls{town}, so most trundle by with empty wagons, though one has a full cart of chickens in cages.
  The rain lets off just as the Sun sets, leaving everyone damp.
\end{boxtext}

Slip in the fact that a trader is travelling with chickens away from \gls{town} casually.
If the troupe notice, they can ask, and he'll tell them he's going to \gls{redfall} because he was paid a lot to do so.
Otherwise, just leave the clue dangling.

\sqpart{Roads}% AREA
{The Search for \Glsentrytext{forestpriest}}% NAME
{\Glsentrytext{nurabaron}'s seneschal asks the \glspl{pc} to help him}% SUMMARY
\label{nonstarter}

\begin{exampletext}
  Thorn has left to complete a trade-deal for pottery, and has to hurry back to \gls{redfall} to make sure the estate does not land itself in any trouble.
  He's heard that the renowned \gls{doula} -- \gls{forestpriest} -- sometimes sells her wares in \gls{town}, and he thinks she can help, but has no time to fetch her.
\end{exampletext}

Thorn sees the \gls{pc}-troupe on the road while travelling with a caravan, and asks them to deliver a letter to \gls{forestpriest}, in \gls{town} urgently.
He pays them 5~\glspl{sp} upfront, and tells them they will receive 10 more if they deliver it successfully, and accompany her.

He refuses to give his name.
The sealed letter reads as follows:

\begin{speechtext}
  Renowned \pgls{forestpriest},

  I respectfully request your expedient services at \gls{redfall} estate.
  Some dark curse has transformed the family and one horse into ravenous beasts.
  We can pay whatever remains in the power of this diminished estate for your herbal cures, sufficient for a man, and (if immediately available) for four children and \gls{nurabaron}'s wife.

  The horse is also afflicted, and all present a danger, with their increases size and appetite.

  The family must be harmed \underline{in no way}.
\end{speechtext}

\thornSeneschal

\label{thorn}

\paragraph{If the troupe go to \gls{town},}
they will find the usual shenanigans and some new \gls{sq} \gls{segment} before they locate \gls{forestpriest} in her shop in \gls{town}'s area \vref{greyDoulaShop} (unless circumstances have ensured she's elsewhere).

\Gls{forestpriest} will take some supplies, and agree to accompany the troupe to \gls{redfall} (\autopageref{redfallVillage}).

\sqpart{Roads}% AREA
{Rumours of the Beast}% NAME
{\gls{vlg} People on the road chatter about the beast who rides at night by \gls{redfall}}% SUMMARY
On the road, people discuss sightings of the `giant rider'.
In fact people have seen \gls{nurabaron} riding his massive horse at night (he just wants to ride for fun).

\paragraph{If the troupe save \gls{nurabaron},}
skip the next \gls{segment}.

\sqpart{Town}% AREA
{\gls{vlg} The Master's Bounty}% NAME
{\Glsentrytext{nurabaron} has been found out, and everyone in \glsfmttext{town} wants the bounty on his head}% SUMMARY
\label{mastersBounty}

A guard at \gls{redfall} has fled, and informed the whole town that \gls{nurabaron} has turned into an ogre.

\begin{speechtext}
    Hear ye! Hear ye!

    Oi! I said ``Bloody well listen!''

    The current price of dwarvish coin is to be lowered by a tenth of the current value.

    Guards are no longer allowed to urinate\ldots in public.
    Guards caught urinating in public, may be reported, to the local {\footnotesize guard station}.

    Honest work is to be found digging fortifications in the Wetlaw village.

    It can wait till I'm bloody-well finished, Murkrash.
    Shut it!

    Listen good to this one!

    \gls{nurabaron} of \gls{redfall} Keep has turned-evil, become-a-depraved-monster, and is to be \underline{\large killed.on.site}.
    His last known whereabouts is his own keep.
    Within this establishment, his own staff may be \emph{killed} on the basis that they harbour a criminal.
    All goods found therein are considered legal property by the finder.
\end{speechtext}

Arkblow the crier knows nothing more than he's said.  A number of townsfolk quickly decide to take up arms and slay the local monster, hoping the ransack his house and loot anything of value.

Of course, the only way to put a stop to this is for the characters to find \gls{forestpriest} and bring her to the keep before the angry mob arrive, convince the mob that they have already cured \gls{nurabaron}, or somehow rush \gls{nurabaron} to safety.

\paragraph{Stalling the impending trouble}
before it starts could involve extolling laws (\roll{Strength}{Academics}), pleading (\roll{Charisma}{Empathy}), or anything else.
However they approach the problem, the \gls{tn} is 12, but they should get at least three rolls before the townsfolk stop listening.

\paragraph{Journeying to \gls{redfall} before the crowd}
won't be a problem if they have horses.
If no horses are present, a few traders will arrive before them, at the very least.

%\sqpart{Town}% AREA
%{The Goblin Fort}% NAME
%{\Gls{redfall} becomes a goblin fortress}% SUMMARY
%
%If any goblins remain alive in \gls{redfall}, it becomes a bastion for the goblins, and the \glspl{pc} hear all about what happened in \gls{town}.
%
%If farmers and townsfolk stormed the keep, they tore it apart to gain entry, and the goblins inside pulled off bricks to hurl down on their heads.
%
%What the villagers don't know is that a goblin druid has arrived as the \gls{warden}'s advisor.
%
%See \autopageref{redfallFallen}.

