\subsection{\Glsentrytext{pig}}
\index{Taverns}

\begin{boxtext}

  Two men are pummelling each other in front of the pub's door.
   One limps and the other's nose is burst open and streaming down his shirt, but they continue circling like boxers.
   Two guards cry out and run forward to stop the public disturbance, and the two men immediately run together into \gls{pig}, a disreputable tavern near the city's entrance.
   The guards stop at the door, look at each other for a moment, and then walk away.

\Gls{pig} never treats \glspl{guard} well.

\end{boxtext}
 
The roughest and oldest pub in \gls{town} sits just across from one of the major entrances, enticing traders in with the promise of the latest news and cheap ale.

The owner, \gls{pigowner}, keeps the place in order with a mixture of social contacts with the roughest characters in \gls{town}, and rare but sudden violence.

The place gets lenient treatment from the guards as it's an official Temple of Alass\"{e}, complete with an official priestess.
The fact that she spends most of her time drunk doesn't detract from her status, or stop the occasional noble asking her to sneak contraband into the city.

Currently, \gls{pig} allows a few of the Immortal Bandits to stay under the bar, as they help her move things in and out of town without going through the \gls{guard} at the gates.%
\footnote{See page \pageref{farmExit} for the exterior route.}

\mapPic{b}{Dyson_Logos/mincing_pig}{
  \ref{pigHall}/11/46,
  \ref{pigKitch}/10/73,
  \ref{pigPrivate}/25/73,
  \rotatebox{-90}{\large F}/26/785,
  \ref{pigDen}/35/81,
  \ref{pigRoom}/41/89,
  \ref{pig_pantry}/35/98,
  \ref{runoff}/37/35,
  \ref{pigShaft}/51/58,
  \ref{pigTemple}/73/77,
  \rotatebox{-90}{\large S}/70/71,
  \huge\ref{pigDogs}/81/33,
  \large S/78/46,
  \rotatebox{-90}{\large S}/755/43,
  \ref{pigDown}/85/04,
}

\mapentry[pigHall]{Beerhall}

The cat's name is Bob, and his collar is made from dried, woven daffodil.  The collar is activated by shouting the elvish word for `dragon', at which point Bob will turn into a nura cat until someone says the elvish word for `cat'.%
\footnote{The collar was a gift from \gls{sewerking}, who found it among the old treasures below.}

\begin{boxtext}

  Alassean song and roasted pig wafts hits you in the face as soon as the door opens.
  With only three tables in the room, people have carved out little seating circles on the ground.
  A fat cat with a brown collar sits in the rafters and eyes you suspiciously as you struggle through the disorganized crowd to get to the bar.

\end{boxtext}

Only \gls{pigowner} knows about the collar's power, and as a result, elves and people who speak elvish (such as many academics) are not welcome in \gls{pig}.
She plans to use it for self-protection (or for her final vengeance) in case anything goes seriously wrong one day.

When in nura-form, these are his stats:

\morphcat[\NPC{\N\A}{Bob}{slick}{licks paw}{colourful birds}]

\mapentry[pigKitch]{Kitchen}

People cook here, mostly.

\paragraph{If the \glspl{pc} observe the area carefully,}
they notice \gls{sewerthief} porting sacks to room 3 (the `private room'), followed by others.
These contain dirt, used to make fake corpses so \gls{sewerking} can swap them for real corpses.

In total, eight men enter the private room, and don't return.

\pigowner

\mapentry[pigPrivate]{Private Room}

\Gls{alemaster} often sleeps in \gls{pig}'s quieter side-room after a long night of drink and song.
She gets on well with \gls{pigowner}, helps with the books, and provides cheap ale to many of the taverns around.%
\footnote{Although, not all taverns, as the Ale Guild of the Shale is cheaper.
See page \pageref{troubleAle}.}

She has a lot of respect and time for the dispossessed nobles of Whiteplains as she detests \gls{king}, but has no idea about their plans, murders, or that the undead are wandering below her.

\begin{boxtext}

  Perfumes, spices, and stale sex fill your noses.
  The wide room practically begs for shoes to be removed as it's filled with pillows, throws, and blankets.
  The only raised platform is a table strewn with fortune-telling cards, where \gls{alemaster} sits with a headband made of gold.

\end{boxtext}

Under \gls{alemaster}'s fortune-telling card table the floorboards are loose, and lead down to a new room, muffled by a thick curtain.
The number of people entering here has lead to wild rumours about the number of men \gls{alemaster} satisfies each day, and the number of hours they spend in there.
However, the reality is that almost everyone who enters the room simply wants to go through the secret hatch to the room below.

\alemaster

\mapentry[pigDen]{Thieves' Den}

\textbf{Background:}
Priests of Qualm\"{e} once lived, studied and prayed in these rooms before an underground flood made the place unlivable.
Currently it hosts card games.

A number of local thieves know of this secret and secluded room.

\begin{boxtext}
  Three men sit cross-legged on the floor, quietly playing cards.
  The second they see you, an additional layer of silence enters the room.
\end{boxtext}

\humanthief[\npc{\T[3]\Hu}{Three Cutthroats}]

\mapentry[pigRoom]{\Glsentrytext{pigowner}'s Room}

\Gls{pigowner} lives in a mess of old notes about what she owes to whom, chests of illegal weapons%
\footnote{Weapons are not illegal but stockpiling more weapons than an individual can use \emph{is}.}
hidden under various clothes (swords mostly), and various expensive alcohols, along with poisons, all lying about without labels.

\mapentry[pig_pantry]{Pantry}

\textbf{Background:}
\Gls{pigowner} stores additional casks of ale, the good wine, and the best salted pork in here.

\paragraph{If this encounter occurs after the ghast escapes,}
then the Immortal Bandits have trapped it in this room, along with an unfortunate maid whom the monster turned into a ghoul (see page \pageref{ghastEscape} for more on the ghast).

The thieves who live in the sewers have apologized to \gls{pigowner} for letting the creature escape, but none have volunteered to open the door.
On its way out they could see it was a different sort of undead -- not a regular ghoul, but something with a mind, and the ability to plan.

The creature looks like a regular, skinny woman, with long brown hair, dead around six months.
However, the simple shell hosts a powerful necromancer.

\npc{\D}{Monster in the Cellar}

\person{0}% STRENGTH
  {1}% DEXTERITY
  {0}% SPEED
  {{2}% INTELLIGENCE
  {0}% WITS
  {-5}}% CHARISMA
  {2}% DR
  {2}% COMBAT
  {Academics~2, Caving~1, Medicine~1, Stealth~3, Vigilance~3}% SKILLS
  {None}% EQUIPMENT
  {
    \setcounter{Air}{2}
    \setcounter{Fate}{2}
    \setcounter{Water}{3}
  }

The creature has already risen the maid from the dead, and has an escape plan.
It will create a magical mist as it hears anyone attempting to enter the door.
Once the door opens, the mist pours out, obscuring all vision, and the ghoul-maid will come shambling out.
Anyone attempting to kill the creature inside will probably attack the maid, and in the confusion, the monster from the cellar will attempt to stealth its way outside.
In the private room above, it will cover itself in blankets, posing as an embarrassed man who must leave unseen.
Once on the street, it can find an alley to hide in, and begin its murderous rampage before diving into the river at the first sign of a mob.

\ghoul[\npc{\D\F}{Undead Maid}]

\mapentry[runoff]{Runoff}

Various little pipes, nooks, and gutters in the city lead underground.
This little drain pops out here, and heads steadily downhill, eventually landing in the sewers below (see page \pageref{sewerPig}).

The first member of the party to go down the tunnel rolls to spot the tripwire (Wits + Vigilance, TN 8), and failure means they immediately go tumbling downwards to the sewers.

\begin{boxtext}

  A little river can be heard ahead.
  The torchlight shines on a thin but taught rope, stretching across a passage to the right.
  The little river flows down steeply, fed by a gushing crack in the wall.
  It's not clear if the rope was to server as a poor guard-rail or as a tripwire to send people tumbling down.

\end{boxtext}

\mapentry[pigShaft]{Ventilation Shaft}

This little tunnel reaches upwards to allow a modicum of fresh air to circulate down in the nasty little dungeon.  Characters with a Strength of 0 or greater are too large to fit through the narrow hole.  It emerges on a street, just below a rich man's house.

\mapentry[pigTemple]{The Temple of Qualm\"e}

\textbf{Background:}
When the Immortal Bandits cleared this hallway, they found an entrance to the Temple of Qualm\"e.
But instead of entering, they pulled out the door, and quietly replaced it with stone.

Finally, they carved through the rock underneath to create a crawl-space, and replaced the stone tile on the floor with another which would give way when pushed from below.

This ensured that their access would remain secret.
Once the waters receded, the Temple priests started to use the room for its original purpose -- cleaning the dead, in preparation for their burial.

The bandits can now sneak in here every could of nights with a fake corpse-bag, made of sack-cloth and filled with earth, and replace corpses with fakes.
The bandits then take the real corpses down to the underbelly, where \gls{sewerking} can resurrect them from the dead.

\mapentry[pigDogs]{Sleeping Dogs}

When not getting up to no good, the Immortal Bandits sleep in these little alcove-bedrooms.
Each one has little more than blankets and clothing hooks.

\textbf{Background:}
\Gls{sewerthief} has the room to the far right, and while everyone else was digging where \gls{sewerking} ordered, he quietly dug himself a little hiding-hole to stash money and other valuable he's taken for himself.
In total, he's collected \lootMedium, and one \lootMagic.

When \gls{sewerking} found out about this, he became annoyed, and placed a ghast in the room, instructing it to frighten (but not kill) \gls{sewerthief}.

\paragraph{If the \glspl{pc} enter \gls{sewerthief}'s room,}
the ghast jumps out at them.

\npc{\D}{Ghast-in-the-Box}
\ghast

\mapentry[pigDown]{The Descent}
This path downwards leads to the thieves' den underground (see page \pageref{sewerPigWalk}).


