\sidequest[Villages]{The Little Prince}\label{littleprince}

\noindent
An elf is assaulted by brigands.
If the characters help, they receive help in return later.
If they join the brigands and rob the elf, other elves will have their vengeance later.

\sqpart{Forest}% AREA
{The Elven Prince}% NAME
{The Woodspy Bandits are attacking a rich elf}% SUMMARY

\Gls{elfprince} wanted to see the sea.
Without knowing where it lies, he figured that with enough walking, he would find it eventually.
However, brigands found him first.

\begin{boxtext}
  A voice in the distant forest cries out.
  \begin{quote}
    I'll summon griffins to pull your stomach out!  I'll enchant you to make you eat until your stomach explodes!
  \end{quote}

  A gruff voice laughs nearby.

  \begin{quote}
    ``If you could, you'd have done it already.  And that's some pretty jewels you got there.  Rich ladies like elf jewels.''
  \end{quote}

\end{boxtext}

\humansoldier[\npc{\T[8]\Hu}{Eight Bandits}]

\elfprince

If saved, \gls{elfprince} will promise to repay the characters sometime, but immediately leaves.
If the elf dies, the party notice a magpie eyeing them (it will later relay the information to other elves).

\sqpart{Villages}% AREA
{\squash Karma}% NAME
{Three elves return to repay the characters for their previous actions}% SUMMARY

Play this encounter at the same time as the next Side Quest.
The prince's friends journey towards the sea, and they have heard of the characters.
If they aided \gls{elfprince} before, the troop will aid them in return.
If the characters harmed \gls{elfprince}, the elven troop will have heard of it from the brigands, or through a sentient bird.

The elves will not approach at first, but attempt to sneak and observe the party for a while.

\paragraph{If the elves want to hurt the \glspl{pc},}
they use their highest level spheres, hopefully while the \glspl{pc} have already entered combat with someone.

\paragraph{If the elves want to help the \glspl{pc},}
they either aid in a battle, or offer a single favour.
The \glspl{pc} must ask for the favour immediately, or they will never see the elves again.

\elf[\NPC{\M\El}{Sindon}{Lively}{strokes blonde hair}{to see what's happening in the world}]

\paragraph{If the \glspl{pc} ask about the brigands,}
Sindon can give them an approximate idea of where the Immortal Bandits are, as long as they can understand his references (he does not direct them according to which road and \glspl{village} are near, but by river-currents and tree-types).
Understanding him requires \roll{Intelligence}{Wyldcrafting} (\tn[10]).

\elf[\NPC{\F}{Vanw\"e}{Dour}{Wipes eyes}{to find \gls{elfprince}}]

Vanw\"e was in love with \gls{elfprince}, and plans to either aid the characters well, or \emph{really} hurt them, depending upon their previous actions.

\elf[\NPC{\M}{Neuror}{jovial}{spits}{to not get left behind}]
\label{neuror}

\paragraph{If the \glspl{pc} ask about \gls{lostcity},}
Neuror begins a repetitive rant about how it was all the humans fault for messing with alchemy, although he doesn't really know many details.

