\section{\Glsfmttext{redfall}}
\label{redfallVillage}
\begin{multicols}{2}

\Gls{redfall} is a standard inner settlement -- a hamlet.%
\footnote{Like to many terms, this one has become slightly twisted in \gls{fenestra}, as these `hamlets' are characterized by being inside the great barrier of \glspl{village}, meaning far fewer predators will approach them.}
If trouble arrives, the \gls{sunGuard} archers in the keep typically make an awful lot of noise to draw the creature in, then loose their arrows when it approaches close enough.

\widePic[t]{Dyson_Logos/redfall}

The people in the area create pottery from the rich clay deposits.
They also enjoy a rarity in \gls{fenestra} -- fruit trees.
Large patches of foliage, fern, and trees invite predators to hide in their shadows, but these creatures so rarely approach this close to \glsentrytext{town}, that \gls{redfall} enjoys them safely.
\ldots or they did until \gls{nurabaron} sent his \glspl{sunGuard} out to take all of their fruit, and demanded seconds.

The recent hike in taxes has driven the now-hungry villagers to desperate measures.%
\footnote{See \vpageref{desperatemeasures} for more on the consequences.}

\begin{boxtext}
  \Gls{redfall} seems peaceful, almost idyllic, as children play next to copse of trees without any fear of beasts waiting for them inside.
  A few women collect the red earth by the river so they can process it into their famous pottery later.
  Ahead, the keep stands three stories high.
\end{boxtext}

\paragraph{When the \glspl{pc} enter,}
if they look like like might be officials or soldiers of any type, the villagers act natural at first, but arrange to surround the troupe at the bridge.

\begin{boxtext}
  As you step onto the bridge, you see a dozen men walking behind you with large bags covering their heads and another sack in their hands.
  In front, another ten with sacks gather as well.
  Ahead and behind, they pull the rocks out.

  ``No more taxes!'', they shout.
\end{boxtext}

\npc{\T[4]\Hu}{\arabic{noAppearing} Angry Farmers}
\person{2}% STRENGTH
{0}% DEXTERITY 
{0}% SPEED
{{0}% INTELLIGENCE
{-1}% WITS
{0}}% CHARISMA
{0}% DR
{0}% COMBAT
{Projectiles 1, Crafts~1, Wyldcrafting~1}% SKILLS
{Sack-of-rocks, face-covering}% EQUIPMENT
{}

\paragraph{If the \glspl{pc} try to reassure the villagers,}
have them roll \roll{Strength}{Empathy} (\tn[9]) to holler their message clearly to everyone present.

Failure indicates a nasty pelting, although the villagers don't intend to kill the anyone -- just drive them off.

\paragraph{If the \glspl{pc} ask about the keep,}
the villagers complain bitterly, but have no idea that \gls{nurabaron} has become a monster.

\paragraph{If the troupe attempt to persuade the villagers to assault the keep,}
they can succeed with a \roll{Charisma}{Tactics} roll, \tn[10]
(the villagers feel more confident with a strong character leading them).
Of course the villagers also know that the fortress is armed with archers, and will only agree to enter if the troupe have a solid plan concerning the archers.

Roll Morale checks for all involved, as usual.%
\exRef{judgement}{Judgement}{morale}
The battle will likely end before either side loses too many members.

\mapPic{t}{Dyson_Logos/redfall_keep}{
  \huge\ref{redTower}/05/68,
  \Large\rotatebox{0}{\nameref{redTower}}/05/80,
  \huge\rotatebox{-45}{\nameref{redYard}}/34/50,
  \ref{redYard}/28/46,
  \Large\rotatebox{-45}{\nameref{redToilet}}/52/26,
  \huge\ref{redToilet}/545/34,
  \Large\nameref{redKitchen}/31/79,
  \ref{redKitchen}/30/75,
  \Large\rotatebox{-45}{\nameref{redServants}}/43/75,
  \ref{redServants}/41/73,
  \huge\ref{redChild}/84/19,
  \Large\rotatebox{45}{\nameref{redChild}}/84/28,
  \Large\rotatebox{45}{\nameref{redSmolYard}}/75/34,
  \ref{redSmolYard}/65/36,
  \huge\nameref{redHall}/63/93,
  \ref{redHall}/63/75,
}

\subsection{\Glsfmttext{redfall} Keep}

The keep contains a conspiracy: everyone in there knows that they harbour monsters, but they also know that those monsters can be cured, and that if they tell anyone, they'll lose their employment, and will either have to beg or join the \gls{guard}.

The various staff will only use their bows -- none are dim enough to fight toe-to-toe.

\humanarcher[\npc{\T[4]\M\Hu}{2 Archers}]

\mapentry[redTower]{Towers}

Each of the towers has two archers, ready to protect their patron, \gls{nurabaron}, as long as nobody gets too close.
If approached, they surrender.

\boxPair[t]{
  \nurabaron
}{
  \morphhorse[\npc{\N\A}{Janus, the Demonic Horse}]
}

\mapentry[redYard]{Courtyard}

This open courtyard makes archery an easy job.  Anyone outside can easily be picked off if they do not have adequate shielding.

\mapentry[redKitchen]{Kitchen}

The dwindling food supplies are kept here.  They build up to monstrous amounts, then get hurriedly eaten within a day or two.  Barrels of meats, stacks of bread, and multiple bottles of wine -- nothing lasts long.

\mapentry[redServants]{Servants' Quarters}

This place holds various cots, chests, and washing equipment.
At present only six members of staff remain -- two cooks, two butlers, one seneschal, and Tollfen the tax collector.

\mapentry[redSmolYard]{Small Courtyard}

This area holds a thin, thatched roof, and plenty of space for games without getting wet.
It's used as a common area by the servants.

\mapentry[redToilet]{Toilet}

This spacious lavatory comes with a runoff to the river outside.
It also hosts arrow slits to fire at intruders on the river.
Small characters, with Strength of 0, can fit through the gap from outside, if they are not wearing armour.
Those with Strength -1 or less can fit through even with armour on.

\Gls{nurabaron}'s horse -- Janus -- was affected by the monstrous spell which gave him such strength.
He still rides Janus, happily, but only at night, when nobody can see him.
The horse eats an obscene amount of food each day.

\mapentry[redChild]{Bairnpelt's Room}

\Gls{nurabaron}'s youngest son Bairnpelt is only a toddler.
He doesn't understand his condition, and has no self control.
This makes him dangerous, so the family have decided to lock him in this little room.
Characters on the river or anywhere near this room can hear intermittent banging, and infant-like gurgling.

\NPC{\M\N}{Bairnpelt -- ``the Toddler''}{Playful}{Fingers in mouth}{Milk}
\person{3}% STRENGTH
{-1}% DEXTERITY 
{2}% SPEED
{{-4}% INTELLIGENCE
{-4}% WITS
{-3}}% CHARISMA
{0}% DR
{1}% COMBAT
{}% SKILLS
{\quarterstaff (\glsentrytext{nurabaron} gave him a stick to `play' with the guards)}% EQUIPMENT
{}

\boxPair[t]{
  \smolMapPic{Dyson_Logos/redfall_top}{
    \Large\rotatebox{-90}{\nameref{redArchers}}/07/38,
    \ref{redArchers}/175/20,
    \Large\rotatebox{-45}{\nameref{redKids}}/67/44,
    \ref{redKids}/74/20,
    \Large\nameref{redSeneschal}/42/80,
    \ref{redSeneschal}/40/71,
  }
}{
  \smolMapPic{Dyson_Logos/redfall_top}{
    \Large\rotatebox{-90}{\nameref{redFamily}}/07/38,
    \ref{redFamily}/175/20,
    \Large\rotatebox{-45}{\nameref{redStorage}}/67/44,
    \ref{redStorage}/74/20,
  }
}

\mapentry[redHall]{Great Hall}

A heavy wooden door guards the entrance well, and a gate sits in front of that.
Lifting the gate takes a \roll{Strength}{Athletics} roll, \tn[10], but the locks on the door don't give much resistance; players can pick them with \roll{Intelligence}{Larceny}, \tn[8].
The bars are slim enough that anyone with a \gls{weight} of 5 or less can just about squeeze through.

\begin{boxtext}
  You open the door to a massive table full of opulent food, and more food stacked on top.
  Layers of bloody bones poke out the side of three layers of filthy dishes, lining the bottom of the feast.
  At the head of the table, sits \gls{nurabaron}, in a meat-stained dressing gown.
\end{boxtext}

The hallways contains a long, messy dining table, covered in scraps of bones from all manner of animal.
The side alcoves contain little beds for guards to sleep in.  Four guards are in the area at any one time.

The baron can usually be found dining here, shouting at guards about some imagined insult, or just terrifying people for the fun of it.
Thorn, his trusted advisor, is the only one who can calm him down when he gets into a rage.

\mapentry[redKids]{Kids' Rooms}

The two brothers were never good at listening, and will attack anyone who enters the upper floor, unless Carnfin is nearby to talk them down.

\ogre[\npc{\T[2]\N\M}{Coreolis \& Sinfall}]

\mapentry[redSeneschal]{Thorn's Room}

Debts, expenses, promises to neighbouring \glspl{village}, and late-payments on monies owed to \gls{townmaster} -- this room has it all, and \gls{redfall} has nothing.

Thorn remains here, fingers in ears, trying to calm everything down.
And if a single member of the \gls{redfall} family dies, he will pay \emph{nothing}.

\thornSeneschal

\mapentry[redArchers]{More Archers}

Two more archers, stand ready to protect their \glspl{warden}.
The troupe cannot convince them to stop firing while their \glspl{warden} stand nearby (or they risk becoming supper).

\humanarcher[\npc{\T[2]\M\Hu}{2 Archers}]

\mapentry[redStorage]{Old Storage Shelves}

\Gls{nurabaron} sold most of the arms here to purchase food, so the room now mostly holds pickled fish, wines, salted meats, and vegetables.

A \roll{Wits}{Larceny} roll (\tn[10]) reveals some bags of coinage, cleverly wedged under the stacks of pickled fish.
Removing the coins, without making a sound, requires a \roll{Dexterity}{Larceny} roll (\tn[12]).
Bag 1 has \lootMedium, bag 2 has \lootMedium, and bag 3 has \lootBig.

\mapentry[redFamily]{Hidden Family}

The family have taken to sleeping in a single room -- a pile of straw and knotted bedding which stinks like sickness.
\Gls{nurabaron}'s wife Carnfin is here, with her daughter.

\ogre[\npc{\T[2]\N\F}{Carnfin \& Cloistra}]

\end{multicols}
