\subsection{Redfall, Fallen}
\label{redfallFallen}

\mapPic{t}{Dyson_Logos/redfall_keep_fallen}{
  \ref{nuramancer_tower}/50/5,
  \ref{keep_ogres}/37/71,
  \ref{keep_patrol}/84/50,
  \ref{keep_prisoners}/81/16,
}

If the citizens of the surrounding lands overrun Redfall (see \autopageref{mastersBounty}), it becomes a hotbed for nura.
They eat the servants, and soon after Krela, the goblin nuramancer, arrived from one of the open nura portals in the land.

Krela eats well with the ogres, and soon builds up an ogre army.
The nura begin eating their way through the surrounding villages, while Krela transforms humans into ogres.

The central fort continues amassing arms, and the ogres throw boulders at anyone who comes too close.

\mapentry[keep_ogres]{Philosophical Ogres}

Four ogres discuss if they are men, transformed, or ogres with the stolen memories of humans.

\ogre[\npc{\T[4]\N\Hu}{Four Ogres}]

\mapentry[keep_patrol]{Patrolling Ogre}

A single ogre patrols the keep.
He will talk with anyone who looks unthreatening, as he has eaten well already.
Otherwise, he attacks.

If Nathaniel the diplomat survived, this ogre is Nathaniel, and he hates Krela for taking his position as advisor.
He will help assassinate her, but not if it means putting \gls{nurabaron} in danger.

\boxPair[b]{
  \nurabaron
}{
  \goblinnuramancer[\npc{\F\N\Gn}{Krela}]
}

\mapentry[keep_prisoners]{Prisoners}

Four prisoners await death, once the ogres become hungry enough.

\mapentry[nuramancer_tower]{Nuramancer}

The nura goblin advises \gls{nurabaron}, and will use her vantage point to cast offensive spells at anyone attacking the keep.


\mapPic{b}{Dyson_Logos/lakeside}{
  \rotatebox{-40}{\nameref{lakeSquare}}/51/45,
  \ref{lakeSquare}/46/43,
  \rotatebox{-40}{\nameref{lakeTemple}}/78/81,
  \ref{lakeTemple}/70/79,
  \rotatebox{40}{\nameref{lakeDocks}}/16/68,
  \ref{lakeDocks}/21/63,
}


