\section*{Services}

\begin{multicols*}{2}

\begin{boxtext}
  It's not safe to go alone.
  Take me, at a minimum of 5 \glspl{sp} per day, plus travelling expenses.
\end{boxtext}

To buy good services, the \gls{gm} rolls your Wits + Empathy in secret.
A bad roll means you have paid for a faker, but will find out too late.

Sellswords will fight with the troupe.

Guides will escort the troupe, but may disappear any time they feel less safe \emph{with} the troupe than without them.

\begin{boxtext}
  Don't know where you're going?
  No problem.
  I know the whole area.
\end{boxtext}

\noindent
\begin{tabularx}{\linewidth}{XX}

\textbf{Apothacary} & 1 \gls{sp} / level of Intelligence + Medicine \\\hline

Poison cure & 1 \gls{sp} \\

Poison & 4 \gls{sp} \\\hline

\textbf{Fence} & \\\hline

Common item & 20\% of the item's total value \\

Identifiable valuables & 40\% of the item's total value \\

Magical item & Varies considerably, 50\% chance the item is refused \\\hline

\textbf{Boat Trip} & \\\hline

Popular trading route & $2D6-2$ \gls{sp} (reroll each day) \\

Standard stream & $3D6$ \gls{cp} \\\hline

\textbf{Guide} &  150 \gls{cp}/ day \\\hline

  Inner \glspl{village} & 50 \gls{cp} \\
  Near the \gls{edge} & 5 \gls{sp} \\
  Beyond the \gls{edge} & 15 \gls{sp} \\

\end{tabularx}

\noindent
\begin{tabularx}{\linewidth}{XX}
\hline
\textbf{Hospitality} &  \\\hline

Public House & 0 \gls{cp} \\

Meal & 5 \gls{cp} \\

Barn with breakfast & 10 \gls{cp} \\

City Inn & 40 \gls{cp} \\

Fancy Room & 1 \gls{sp} \\\hline

\textbf{Minstrel} &  15 \gls{cp}/ performance \\\hline

Large audience & 500 \gls{cp} \\

Massive audience & 1 \gls{gp} \\

Creating a new song & 2 \gls{sp} \\

Illegal song & 5 \gls{sp} \\\hline

\textbf{Sellsword} & 10 \gls{sp}/ day \\\hline

Opponent & \gls{xp}$^3$ \gls{sp} \\

Illegal Murder & 10 \gls{sp} \\\hline

\textbf{Tracker} &  5 \glspl{sp} / day \\\hline

  Inner \glspl{village} & 1 \gls{sp} \\
  Near the \gls{edge} & 10 \gls{sp} \\
  Beyond the \gls{edge} & 20\gls{sp} \\
\hline

\end{tabularx}

\end{multicols*}

\cleardoublepage

\section*{Sellswords}

\begin{multicols*}{2}

\humansoldier[\NPC{\M\Hu}{Kartog}{Lively}{Hands on hips}{Wanderer}]

\humanthief[\NPC{\F\Hu}{Quartmeg}{Sarky, dark-eyes}{Raises right eyebrow}{Seeker}]

\humanfarmer[\NPC{\M\Hu}{Somnal}{Confident}{Thumbs-up}{Noble}]

\humanfarmer[\NPC{\F\Nl}{Hrash}{Slick and inquisitive}{Spits on palm, smoothes out fur}{Paladin}]

\end{multicols*}

\cleardoublepage

\section*{Guides}

\begin{multicols*}{2}

\humanfarmer[\NPC{\F\Hu}{Tenleck}{Dour, short black hair}{Picks nose}{Noble}]

\elf[\NPC{\F\El}{L\'ir\"e}{Golden ringlet~hair}{Giggles}{Wanderer}]

\dwarvensoldier[\NPC{\M\Dw}{Ben of Clan Longhall}{Short beard, practical}{Trims beard}{Money}]

\end{multicols*}

