\sidequest[Forest,Town,Roads]{The Spider's Song}

\noindent
When elves become old, they get weird.
\Gls{spiderqueen} has left her people, and devoted her life to enchanting animals with song and fostering a kinship with them.
Currently, she has collected three pet chitincrawlers, but she's having trouble keeping them, because they require too much food.%
\exRef{judgement}{Judgement}{chitincrawler}
She has also begun Polymorphing her own body to look progressively more like a chitincrawler.
Currently, her lower body has six legs and a thorax, which produces thin webbing.
Her skin has begun to harden, and sprout thick, brown hair.

Over the course of these encounters, \gls{spiderqueen} becomes progressively more irritating to the troupe and the local area, until the players finally happen upon her lair.

Chitincrawlers hibernate over the colder seasons, so if \gls{fenestra} has entered a cold season, skip these encounters until later.%
\exRef{judgement}{Judgement}{astronomy}

\sqpart{Forest}% AREA
{The Arachnid Double Cross}% NAME
{\Gls{spiderqueen} double-bluffs the troupe, attacking with illusory chitincrawlers, mixed in with real ones}% SUMMARY
\label{spiderqueenssong}

\Gls{spiderqueen} sat with her babies, serenely in the forest, wondering what to feed them.
She cast a \textit{Witness Life} spell, and discovered the \glspl{pc}, then hatched a cunning plan\ldots


\begin{enumerate}
  \item
  She will cast illusions of chitincrawlers, who attack beside her real babies.
  \item
  The characters will spot the illusions (they aren't very good) and think they are in no danger.
  \item
  A moment later, she creates an illusion of a gnome, so the characters will \emph{think} that they understand where the illusions came from.
  \item
  As the real chitincrawlers grab the characters, they will be taken completely by surprise.
\end{enumerate}

She casts her spells by singing songs.

\begin{boxtext}
  You can always tell elven music by a sort of off-beat, where the beat goes wrong in a regular way.
  This one is soft and high-pitched, and interrupted by the sound of snapping twigs.
  More crackles come from in front.
  The setting Sun casts a red shimmer over the armoured bodies of a dozen man-sized black-clad, crawling creatures.
  The trees drop a small platoon of arachnids, and in a moment a hundred eyes are calculating how you taste.

\end{boxtext}

The \glspl{pc} roll \roll{Wits}{Vigilance} to understand their environment.

\begin{boxtable}

  \textbf{TN} & \textbf{Result} \\\hline
  8 & The Sunset red on the chitin is too much, like the creatures don't look right.  You instantly spot that these are illusions. \\
  9 & On a nearby branch a little gnome sits, quietly giggling to himself, then looks shocked as you spot him. \\
  11 & The distant song seems to be coming from a single chitincrawler in the distance, \\
  12 & though she looks different from the rest. \\
  13 & Looking past the poor chitincrawler illusions in front of you, you notice that the rest are completely and definitively real. \\
  14 & The little gnome, however, is entirely fake. \\

\end{boxtable}

Thirty chitincrawlers attack (3 real, 27 fake).

\paragraph{If any \gls{pc} cannot tell the real chitincrawlers from the fakes,}
they will have real problems in combat as they will expend all their \glspl{ap} on the fake ones (which attack first).

\paragraph{If they kill a chitincrawler,}
\gls{spiderqueen} `changes her tune', and sings another song to bring them back to her.

\chitincrawler[\npc{\A\T[3]}{3 Chitincrawlers}]

\paragraph{If the \glspl{pc} approach \gls{spiderqueen},}
she casts another illusion to make herself appear as a bush (\tn[10] to spot).

\paragraph{If two \glspl{pc} die,}
the chitincrawlers all stop to feed.

\spiderqueen
\label{spiderqueen}

\showStdSpells[
  \spell{Spider Hive}% Name
    {duplicated,detailed}% Enhancements
    {Warp}% Action
    {Air, Fire}% Spheres
    {\roll{Wits}{Vigilance}}% Resist with
    {The caster rapidly lists every known property of spiders, and \arabic{spellTargets} chitincrawler illusions emerge from every shadow}% Description
    {Each chitincrawler has Body Attributes at +\arabic{spellPlusOne}, and vanishes once anything touches them.}
  \input{config/spells/Light2.tex}
  \input{config/spells/Life3.tex}
  \setcounter{enc}{3}
]


\sqpart{Roads}% AREA
{Sheep Stampede}% NAME
{\Glsentrytext{spiderqueen} summons sheep to be eaten by her chitincrawlers}% SUMMARY

\begin{exampletext}
  \Gls{spiderqueen} has gathered more chitincrawlers, and she needs to feed them again, so they have laid out their webs, and await their dinner.
\end{exampletext}

\begin{boxtext}

  A nearby shepherd suddenly shouts out ``Hey!'', as he loses control of his flock.
  A distant song entices the sheep to run toward its discordant melody. It is as if the singer caused the music itself to decay.

\end{boxtext}

\paragraph{If the \glspl{pc} do nothing,}
the chitincrawlers feed for thirty minutes, then leave.

\begin{boxtext}

  The sheep go beyond sight, and into the distant trees, then the song stops, and they begin to cry out in a way you've never heard sheep cry before.  Half of them flee straight back out of the forest.

\end{boxtext}

\paragraph{If the characters pursue,}
they encounters webs (\roll{Wits}{Vigilance} (\tn[9]) to spot), then see the chitincrawlers feasting on the sheep.
They will disengage and attack the characters if they take any Damage.

\paragraph{If the players mention specifically to look out for webs,}
their characters should spot them immediately.

\chitincrawler[\npc{\A\T[6]}{\arabic{noAppearing} Chitincrawlers}]

As before, \gls{spiderqueen} waits in the distance, and flees at the first sign of trouble.

\sqpart{Roads}% AREA
{Quiet Little Hamlet}% NAME
{An entire hamlet has been eaten by chitincrawlers}% SUMMARY

\widePic{Dyson_Logos/ruined_village}

Chitincrawlers don't usually reach the inner hamlets -- they get distracted along the way by traders or \glspl{village}.
But \gls{spiderqueen} can lead her babies anywhere, including past the dangerous, outer \glspl{village}, and into the quiet little areas inside.
So no matter which road the \glspl{pc} walk, they can encounter a village destroyed by \gls{spiderqueen}.

If the \glspl{pc} have arrived at a known \gls{village} or \gls{bothy}, use that one.
Otherwise, use this example.

\begin{boxtext}

  The little hamlet rests quietly.
  The air is cool, but then a single cockerel lets off half a crow in the distance, and goes suddenly silent before he's finished.
  It's only then you really notice: the fields have no animals, and the farmhouse chimneys don't give out any smoke.

\end{boxtext}

However, inside each of the four farmhouses, rooms are filled wall-to-wall with webbing.  Each house contains the same thing:

\begin{enumerate}
  \item
  Dead villagers in webs.
  \item
  Half-dead villagers in webs, waiting to be eaten.
  \item
  Great sacks of chitincrawler eggs, ready to burst out and feed.
  \item
  One male and one female chitincrawler.
\end{enumerate}

\Gls{spiderqueen} herself has since moved away and left her creatures to multiply.

\paragraph{If the troupe want to leave}
then they can, without issue.

\paragraph{If the \glspl{pc} make a lot of noise,}
all of the male chitincrawlers come out, and pursue.
The females remain with their eggs.

\chitincrawler[\npc{\A\T[3]}{Male Chitincrawlers}]

\chitincrawler[\npc{\A\T[3]}{Female Chitincrawlers}]

\sqpart{Town}% AREA
{Another Village Down}% NAME
{Everyone in \glsentrytext{town} talks about another village, taken by \glsentrytext{spiderqueen}}% SUMMARY

Select any village on the map and cross it out.
\Gls{spiderqueen} has raided it, and the place has become so full of chitincrawlers that people now avoid it, and take another road.

If the \glspl{pc} journey to kill the chitincrawlers, they find 10 chitincrawlers in total, and a lot of remains of dead villagers.

\sqpart{Forest}% AREA
{The Lone Ranger}% NAME
{A member of the \glsentrytext{guard} stalks \glsentrytext{spiderqueen}}% SUMMARY

Bilefen, a Ranger in the \gls{guard}, went out to track down \gls{spiderqueen}.
He has succeeded, but won't approach her alone.

\begin{boxtext}

  A man ahead, dressed in greens, stares at you, then slowly wanders forward.  He puts his finger to his mouth, indicating you need to be silent.

\end{boxtext}

Bilefen approaches slowly, and explains his solo mission to track down \gls{spiderqueen}.
He confesses he feels scared, and asks the troupe to come with him (``but quietly.!.'').

\paragraph{If the troupe continue following the tracks,}
they encounter \gls{spiderqueen}'s lair.

\begin{boxtext}
  In the distance, you see trees covered in so much webbing it seems like a fortress of goo.
  No clear path presents itself, and shortly after the webs you can see five, then ten, arachnid silhouettes.
  A few move slowly down their trees.
\end{boxtext}

Having found the location, Bilefen only wants to return to \gls{town} and give his report.

\paragraph{If the \glspl{pc} fight,}
the chitincrawlers don't move out quickly -- they feel safer in their lair, but they may come out if fire begins to burn the houses.

Twelve chitincrawlers in total remain in the fortress of webs, and two emerge each round.
\Gls{spiderqueen} then moves out to cast offensive spells.

\paragraph{If the \glspl{pc} push for Bilefen to join them,}
someone needs to roll Charisma + Combat, TN 10.
Whether or not they succeed, Bilefen impresses on them that they have no duty to fight.

\humansoldier[\NPC{\M\Hu}{Bilefen}{Suspicious}{Purses lips}{get promoted to builder}]

\paragraph{If the troupe attempt to light the forest on fire,}
they will have a hard time.
The forest is muggy and damp at the best of times.
Even in the warmer seasons, lighting a fire requires an Intelligence + Wyldcrafting roll, TN 13.
No fire will spread fast, so the chitincrawlers will still have time to attack.

\sqpart{Town}% AREA
{\squash The Disappearing Fortress}% NAME
{The \gls{spiderqueen} has moved her fortress}% SUMMARY

While the next Side Quest plays out, drop the bad news on the \glspl{pc} -- the \gls{guard} moved out en masse to defeat \gls{spiderqueen}, but by that time she had moved her home and brood elsewhere.

Nobody has any idea where she might build her new home, but they know the walls of civilization cannot take much more.

\sqpart{Forest}% AREA
{The Cunning Plan}% NAME
{Three gnomes have an elaborate plan for the troupe to kill \gls{spiderqueen}}% SUMMARY

\begin{exampletext}
  Three gnomes have been debating about how to approach the troupe about their plan.
  \Gls{keras} thinks that it's best to honest, and just approach the troupe and ask if they would like to fight giant spiders.
  However, Leta is the decision-maker, and her nose is longer than \gls{keras}'s,\footnote{Gnomes consider this to be a very important point.} so she says there's no use talking to the troupe without testing if they really can fight chitincrawlers.
  Mayelo, meanwhile, just wants both of them to stop fighting and make a decision.
  He's been depressed ever since their village was eaten by chitincrawlers.

  Their final plan is to cast an illusion of a chitincrawler and see how the troupe react.
  If they appear as skilled warriors, the gnomes approach and tell them the plan to defeat \gls{spiderqueen}.
\end{exampletext}

\begin{boxtext}

  As you nip to the side to take a quick piss, a rustle above you shows that a giant arachnid has suddenly appeared, and looks down at you with dripping fangs.
  In the distance, high-pitched snickering can be heard.

\end{boxtext}

\paragraph{If the troupe flee,}
the encounter ends.

\paragraph{If the illusion of a chitincrawler has been vanquished,}
the three gnomes step forward.
Leta begins talking like she's some kind of trader.

\begin{speechtext}

  So you don't like the chitincrawlers?

  You really hate them?

  How much would it be worth to you to be rid of \gls{spiderqueen}, who guides them through the human \glspl{village}?

  And you seem to be adventurers, in the employment of destroying monsters, is that so?

  And what if I told you that we could aid you pushing back against \gls{spiderqueen}?

\end{speechtext}

It's only after the characters emphatically agree that they do want to kill \gls{spiderqueen} that Leta informs them that she's feeling so generous that she's going to help them for free, and indeed has already laid plans.

If the players ask how the gnomes know exactly where she is, they explain they have triangulated her position through her periodic singing.
If they ask how the gnomes can be so certain that a half-kilometre tunnel, going somewhere the gnomes have never seen, can be so precisely dug, Bilefen shows them his calculations.
An \roll{Intelligence}{Academics} roll at \tn[11] shows that they are correct.

The players should be aware that if they jump out \emph{near} \gls{spiderqueen}, but not quite at her, they will be attacked instantly, with little hope of survival.
Their only hope is to break out of the earth, kill her in an instant, and hope the chitincrawlers flee once her spell has been broken.

\begin{speechtext}

  It's simple really.
  Anyone wandering close to that pit of spiders will be eaten by spiders.
  Any large army approaches, and she will flee, with no option to track here whereabouts.
  The only way to be rid of her is a fast, decisive attack.
  But she has herself covered there too -- not yesterday we spoke to an elf who had spoken to local birds, who informed us that even the tops of the trees there are covered in webs.
  Her mobile fortress is impregnable, and hungry, and they will feed again soon.

  However, with our compass and our calculations, we have found a different way.
  We know that she rests not a kilometre \emph{that} way, and so half a kilometre that way there is a tunnel which we have almost completed.
  Once done, it will open \emph{directly} beneath the very place \gls{spiderqueen} sits.

  You know what you need to do.

\end{speechtext}

If the characters agree to squeeze through the tunnel, dig the very last few feet, then burst out, then each one has to make a Speed + Athletics check at TN 7.
Success indicates that the character can spend 4 Initiative to climb out of the hole.
Failure indicates that the character will not be able to get out of the hole that round, and neither will anyone behind them.

\begin{boxtext}

  You look up at the wide eyes of \gls{spiderqueen}.
  She immediately starts climbing higher up the tree, as dozens of chitincrawlers all around race towards you.

\end{boxtext}

Once out, they can shoot at \gls{spiderqueen}, climb the tree, or otherwise attack her.
Two of the chitincrawlers will arrive to attack each round, but once \gls{spiderqueen} dies, any who have not yet come forward do not attack.

\keras

\showStdSpells

\gnome[\NPC{\Gn\F}{Leta}{Inquisitive}{Picks nose}{less chatter, more action}]

\gnome[\NPC{\Gn\M}{Mayelo}{Creepy}{Scratches Adams apple}{to double-check the Maths}]

\spiderqueen

\showStdSpells[
  \input{config/spells/Fate2.tex}
  \input{config/spells/Fire2.tex}
  \setcounter{enc}{3}
]

\chitincrawler[\npc{\A\T[6]}{Chitincrawlers}]

\paragraph{Success} means \gls{spiderqueen} has been killed or quelled.
If she's damaged and her chitinous children pushed back, she flees to seek new adventures elsewhere, and without killing random villagers.

\paragraph{Failure} occurs when the characters fail to damage \gls{spiderqueen} or her children before they flee.
Things get difficult here.
She destroys two more \glspl{village}, then wanders off to find something else to entertain her, as elves often do.

\stopcontents[sq]
