\sidequest{Random Meetings}
\label{randommeetings}

\sqpart{Town}% AREA
{Pickpocketed}% NAME
{Someone has stolen one of the characters' items}% SUMMARY

\begin{boxtext}

  You feel the side of your leg and suddenly your heart stops.
  You wonder where is\ldots \textit{which item is the last one written on your character sheet?}

\end{boxtext}

The player with the highest Intelligence Bonus makes a Wits + Vigilance roll, TN 9.
Failure indicates a thief has stolen the last item on the player's character sheet, and successfully fled.

It might be possible to track the thief, down with enough time spent investigating, but it'll require an Intelligence + Vigilance roll at TN 11.

Oaklick, a local pickpocket, has no excuse except for his young age, and bad luck in life, though he's 25 and was recently kicked out of an apprenticeship for drinking too heavily on the job.

If the players turn him in, he will be pulled up about previous crimes at the same time, and hanged by the end of the week.
With the right deal, he might agree to accompany them on a dangerous mission.

\humanthief[\NPC{\M}{Oaklick}{pudgy cheeks}{picks nose}{a stiff drink}]

\sqpart{Town}% AREA
{The Riddle}% NAME
{\Glsentrytext{college} have raised a bounty on a riddle}% SUMMARY

The townsfolk are abuzz with a riddle.
The mage's guild have become tired of only getting students sent by rich parents with no real ability.
They've raised a bounty of 5gp to anyone who can solve the riddle.
Their hope is that the most talented young men of the realm will come forward, and once they do, a long talk proceeds, as the mages tell whoever gets the correct answer why they should join \gls{alchemists}.

\begin{boxtext}
Three gods stand in front of you.  One always says the truth, one always lies, and one speaks randomly.  They refuse to speak your language, but they understand what you are saying.  You have three questions to identify each god.
\end{boxtext}

To answer the riddle correctly, the characters must pose three questions which guarantee they will correctly identify each god -- guessing is not allowed.
\footnote{This question is mostly here for fun.  Most players will have zero chance of answering this riddle.
It's placed here solely as a conversation piece, but be aware that this is technically possible, and the party may soon be very rich.}

\sqpart{Town}% AREA
{\squash The Captain}% NAME
{\Glsentrytext{captain} jumps into another encounter to help the party}% SUMMARY

\Gls{captain} is heading home after a long night (if this is the afternoon, it's been a \emph{very} long night).
Combine this encounter with the next Side Quest part.
If the party are in trouble, he helps.
If they're known thieves, he tries to follow them, then brings guards.

\captain

\sqpart{Town}% AREA
{Illegal Songs}% NAME
{A bard is caught singing about how much better it was before the current ruler, \Glsentrytext{king}}% SUMMARY

\begin{boxtext}
  A little crowd have gathered in the side street, occasionally clapping their hands to a beat.
  Getting closer, you can hear a mandolin and a soft voice, singing of great heroes fighting back nura hordes coming up from the depth.
\end{boxtext}

The singer is \gls{warningbard}, and he's here to sing the praises of any nobles who might pull together an army to push back the nura, like nobles did in the old days.
However, such an army would be illegal, as only \gls{king} can gather armies, or amass large amounts of weaponry, and so far the area does not have enough of the \gls{guard} to defend itself from rising levels of nura.

\begin{boxtext}

  Moving slowly through the crowd, you spy \gls{captain}.

\end{boxtext}

\paragraph{If the characters are members of the \gls{guard},}
\gls{captain} will reprimand them for not arresting \gls{warningbard}.
They will be sent to watch over the station's dungeon (page \pageref{stationDungeon}), then sent on some dangerous mission at the \gls{edge}.

Either way, \gls{captain} will arrest \gls{warningbard}.

\paragraph{For the rest of the day,}
all of \gls{town} is full of talk about how in the old days, the nura were not a threat, because adventurers would always come to save them, or individual town masters could pull together the armies they needed to quell nura uprisings.

\paragraph{If the party do not intervene,}
\gls{warningbard} will end up in the cells for six months.
\footnote{For the cells under the \glsentrytext{guard} station, see page \pageref{guardstation}.}

\warningbard

\paragraph{If the party spend any length of time speaking with \gls{warningbard},}
he mentions that he knows \gls{forestpriest}.
He also happens to know where \gls{forestpriest}'s stays in the forest, but will not reveal that information unless he trusts the PCs.
\footnote{See page \pageref{lostcity} for the location.}

\sqpart{Town}% AREA
{Pickpocketed Again!}% NAME
{Someone else picks a character's pocket}% SUMMARY

The player with the highest Academics Skill rolls Wits + Vigilance, TN 8.

\begin{boxtext}

  You feel your trouser leg, and suddenly think ``Oh, not again!''.  \textit{What's the last item written on your character sheet?}

\end{boxtext}

This time it's a young woman, down on her luck as her family farm was consumed entirely by nura.
The rest have died, and she's now alone.

\paragraph{If caught,}
Gabile apologizes profusely, and explains her situation.

\humanthief[\NPC{\F}{Gabile}{beady eyes}{messes up her hair}{to join a guild}]

