\mapPic{t}{Dyson_Logos/white_horse_2}{
  \ref{horseHall}/18/45,
  \ref{horseKitch}/68/53,
  \ref{horseYard}/88/57,
}

\begin{boxtext}

  A massive man with a butter-tipped moustache throws a lanky man from the door.
  The lanky man recoils with a grimace, and shouts `you owe me my wages!'.

\end{boxtext}

\mapentry[whitehorse]{\Glsentrytext{whitehorse}}
\index{Taverns}

\begin{exampletext}
  \Gls{sewerthief} took a job as a cook at \gls{whitehorse} to learn more about \gls{townmaster}, but \gls{townmaster} instantly took umbrage at his \glsentrytext{whiteplains} accent.
\end{exampletext}

\humandiplomat[\NPC{\M\Hu}{Barkwind}{Proud}{Curling moustache}{ensure everything is `proper'}]

Entry through deception requires a roll against Barkwind's \roll{Wits}{Vigilance} (\tn).
The players can roll anything as long as it relates to a reasonable plan.
Otherwise, he forgets their faces within a week.

The \glspl{pc} \emph{must} agree with Barkwind (the doorman) about \gls{sewerthief} (and about \gls{whiteplains} in general) before he agrees to let them in.

\Gls{whitehorse} has no locks as nobody expects thieves to enter.
 
\begin{enumerate}
  \item
  The drinking hall contains various \gls{village} \glspl{warden} playing games, and half a dozen local guards (sometimes including \gls{captain}).
  \label{horseHall}
  \item
  \label{horseKitch}
  The staff sleep in the kitchen here during long shifts.
  The lack of proper ventilation makes the air difficult to breathe.
  \item
  \label{horseYard}
  The courtyard usually contains a couple of carriages, and nobles playing ridiculous games.
  \begin{boxtext}

    \Gls{townmaster} is running away from a coterie of chuckling men with his hands tied behind his back.
     A chicken runs out in front of him with a little paper hat.
     He lunges forwards and grabs the chicken in his teeth, then shakes it like a mad dog until it stops squawking.
     He gives a triumphant grin as the crowd clap and another man steps forward to have his hands tied.

  \end{boxtext}

  \item
  \label{horseUpstairs}
  The bookshelves contain rather a lot of history books, most focussing upon anti-elven propaganda, such as the time they destroyed \gls{lostcity}.

  A map on the wall shows all of \gls{valley}.
  Show your players the map in the handouts, but don't give it to them unless the \glspl{pc} want to steal the map.
  \item
  \label{horseCupboard}
  This cupboard contains cleaning supplies, two Fire \glspl{ingredient} (bear hearts), and one Water \gls{ingredient} (a woodspy beak), in case someone becomes sick.
  \item
  \label{horseSideRoom}
  Tavern equipment, bookshelves for less popular books, and beds for the favoured servants, lie in semi-organized heaps and stacks.
  \item
  \label{wolfRoom}
  \Gls{beardedalemaster} and Courtbile of the \gls{wolfhead} sleep in the larger room.%
\end{enumerate}

\smolMapPic{Dyson_Logos/white_horse_1}{
  \ref{horseUpstairs}/55/27,
  \ref{horseSideRoom}/55/80,
  \ref{wolfRoom}/28/27,
  \ref{horseCupboard}/85/08,
}

