\sidequest[Town,Roads,Forest]{Wolf Heads}
\label{wolfHeads}

\noindent
The \glspl{wolfhead} \glsdesc{wolfhead}; however, this coterie lacks manpower and finances.
\Gls{beardedalemaster} has plans for gaining wealth (covered in \nameref{troubleAle}, \vpageref{troubleAle}).
If the plans there go South, the \glspl{wolfhead} will struggle to hire people.

\sqpart{Roads}% AREA
{\squash Wanted Poster}% NAME
{The troupe see a wanted poster for \gls{southRogue}}% SUMMARY

A poster proclaims a 10~\glspl{gp} reward for returning \gls{southRogue} to the \gls{guard} of \gls{southDale}.

\begin{boxtext}
  A new poster in the \gls{bothy} proclaims a 10~\glspl{gp} reward for a young woman.
  The picture seems worthless, but then it described as `exhuberant', `wicked', short-haired, and `expert archer'.
  The instructions say to return her via the \gls{village} of \gls{lakeside}, and not to let her near oils of any kind.

  \Pgls{guard} is staring into the poster, and starts explaining that she must be a wayward soul, and that he `could fix her'.
\end{boxtext}

Move onto the next \gls{sq} immediately.
If the \glspl{pc} persue her, they will find her before long.
Otherwise, just leave this as a feint half-memory for the players.

\paragraph{If the troupe ask about finding her,}
everyone recommends \gls{town} or \gls{lakeside}.

\sqpart{Town}% AREA
{\squash Rumours of Glory}% NAME
{The troupe hear about the \glspl{wolfhead}}% SUMMARY

The locals gossip about local heroes, known as the \glspl{wolfhead}, recently protecting a \gls{village} from a basilisk.
People say they act like the adventurers from the stories.

\sqpart{Roads}% AREA
{New Friends}% NAME
{\Gls{southRogue} follows the troupe}% SUMMARY

\Gls{beardedalemaster} wants to know more about the local \gls{guard}, so she sends \gls{southRogue} out to find out what the score is.
She has bought \gls{southRogue} some black, hardened leather armour, so she would look like \pgls{guard}, then explained the excuse she should use, and \gls{southRogue} joined the first trader caravan leaving \gls{town}.

\paragraph{Once she meets the troupe,}
she insists on joining them.

\paragraph{If the troupe recognize her from the poster,}
she protests very quickly.

\begin{speechtext}
  Listen-but-no!
  
  They {\scshape told me}, that I had to join a trader's caravan.
  I was in Bogpeak (that's in \gls{southDale}), but they went West (\gls{southDale} lies East of here), and I'm not meant to go with them into \gls{town} because I'm a Digger.
  
  And listen, LISTEN\ldots

  I can't register with \pgls{jotter} because he won't have my name, because I'm not in the \gls{guard}.

  I mean, not here I'm not.
  But I'm here now, and I need to save up my pay to get back to Bogpeak (which is in \gls{southDale}).
\end{speechtext}

\paragraph{If the troupe take her to \pgls{jotter},}
the \gls{jotter} will begin writing a letter, and ask the troupe to keep a \textit{very} close eye on her in the meantime.

\paragraph{If the troupe take her to \gls{court} in \gls{town},}
then \gls{beardedalemaster} intervenes, explaining that \gls{southRogue} must return to her father, the \gls{warden} of Bogpeak, and that she suffers from `Hysterophantasia', and joined the \gls{guard} due to going unmedicated.

\southRogue

However it goes, the troupe must travel with her for a few weeks, at least.
She attempts to steal anything that looks like `information', but cannot read, so any piece of paper that `looks like something' may go missing.
Have the \gls{pc} roll \roll{Wits}{Vigilance} against her \roll{Dexterity}{Larceny} (\tn).

\paragraph{If danger emerges,}
she keeps her distance, and uses her bow.

\paragraph{After a couple of weeks,}
she plans her escape, however she can.
She will act on the spur of the moment, at just the right time, and it will probably involve fire.

\sqpart{Forest}% AREA
{Just out for a Walk}% NAME
{\Gls{southSmith} wanders the forest, looking for \gls{lostcity}}% SUMMARY

\Gls{southSmith} has hired eight men from the nearest \gls{village} to join him (at 150~\glspl{cp} per day), to hunt for \gls{lostcity}.
However, he's told them that he's hunting for a magical mushroom called `Dryad's Kiss'.%
\exRef{judgement}{Judgement}{dryads_kiss}
He's also told them not to even look at it, because even a single glance at the mushroom will make you incredibly gullible for the rest of the month.

\renewcommand\npcQuote{You don't need to trust us to speak politely.  Can we start again?}
\southSmith

\paragraph{If he sees the \glspl{pc},}
he assumes they're bandits, and hides, along with the archers.

\humanarcher[\npc{\T[3]}{8 Archers}]

\paragraph{If violence occurs,}
\gls{southSmith} will start by asking anyone he doesn't know to keep their distance, then asking the archers to shoot, and then negotiating peacefully.

If anyone scary-looking gets within \pgls{step} of the archers, they all surrender immediately.

\paragraph{If the \glspl{pc} ask \gls{southSmith} about his business in the forest,}
he continues to lie about his real intentions, then returns the question to them.

\begin{speechtext}
  Someone doesn't believe the things I say (would you believe that?), so I need the mushrooms to make sure they understand I'm telling the truth.
\end{speechtext}

\sqpart{Forest}% AREA
{A Lonely Tower}% NAME
{The troupe discover \gls{southSeeker}'s secret tower in the forest}% SUMMARY

%! Link song about golden priests and mushrooms.

\Gls{greentower} does not have an exact location on the map.
Wherever the \glspl{pc} have arrived in the forest, \textit{that's} where it is, and where it has always been.

``Where do you go next?'', you ask innocently.

And no matter where the \glspl{pc} decide to travel through the forest, they stumble into somewhere they've never been before, and spot \gls{greentower}.

\begin{exampletext}
  \Gls{southSeeker} found the tower's remains while searching for one of the magical gateways in \gls{lostcity}.
  Currently, he thinks a magical gateway lies in tunnels underneath \gls{greentower}, or that a gateway lies close to this tower.
  He has commissioned workers to start rebuilding \gls{greentower}, so he can use it as a base of operations.%
  \footnote{You'll have to play this one by ear.
  If \gls{southSeeker} has already found the magical gate in `\nameref{old_alchemy_basement}' (\vpageref{old_alchemy_basement}), then he must be looking for the other gate, behind the mountains.
  Or if he's found the latter already, he must be searching for the former.
  And if he's found both, then he's checking in on his half-way house\ldots unless \gls{greentower} isn't half way between anything, in which case\ldots you'll figure something out.}
\end{exampletext}

\paragraph{Once they meet \gls{southSeeker},}
he will have to ask them to keep \gls{greentower} a secret.
He comes up with any number of excuses -- `the \gls{guard} \glspl{jotter} won't accept the need for \pgls{bothy} here', `the locals need \pgls{bothy}', `the \gls{templeOfLight} want a private research outpost', and eventually admit that the \gls{templeOfLight} want to know more about \gls{lostcity}.

If they accept, he breathes a sight of relief and thanks them.
Otherwise, he decides to tempt them into the opening below, where he suspects the golden priests existed.%
\footnote{See room \vref{underPriests}.}

\paragraph{If a portal really does lie nearby,}
then \gls{southSeeker} has deduced the proper location, and will use this as a half-way house and base of operations when he finally discovers the portals.

\paragraph{If the portals lie nowhere remotely close to the tower,}
\gls{southSeeker} will soon realize this, and leave the tower abandoned; but he will never forget its location and potential uses.

Go to \vpageref{green_tower} for details on \gls{greentower}.

\sqpart{Forest}% AREA
{\squash Mixed Karma}% NAME
{The troupe encounter the \glspl{wolfhead} while dealing with some other situation}% SUMMARY

\begin{exampletext}
  The \glspl{wolfhead} went out together, to secretly scout out a potential location of one of the magical gateways in \glspl{lostcity}.%
  \footnote{They now believe there were multiple towns, not just a single, large city.}
\end{exampletext}

The \glspl{wolfhead} come across the troupe at the same time as another encounter.
How they react depends entirely on their previous dealings -- those who like the \glspl{pc} help, those who don't stand back.

\paragraph{If the \pgls{pc} has tried to kill any of the \glspl{wolfhead},}
none of them help.
Instead, they stand back and have a good laugh.

\sqpart{Roads}% AREA
{A Cry for Help}% NAME
{The troupe find the \glsfmtplural{wolfhead} under attack}% SUMMARY

While on their many expeditions past the \gls{edge}, three of the \glspl{wolfhead} have run into trouble.
Select the highest possible encounter for the season (such as a basilisk during a mild season), then double their usual numbers, and have them attack the \glspl{wolfhead}.

\basilisk[\npc{\T[2]\A}{\arabic{noAppearing} Basilisks}]

\setcounter{wounds}{5}

\southSmith

\Gls{southSmith}'s arm bleeds from a nasty wound.

\setcounter{wounds}{3}
\beardedalemaster

\southRogue

\sqpart{Roads}% AREA
{The Deal}% NAME
{The \glsentrytext{wolfhead} ask the troupe to join them}% SUMMARY

The \gls{wolfhead} have found both magical gateways, and need to secure their assets.

What happens after the other \gls{sq} \glspl{segment} have resolved depends on so much.
Perhaps the \gls{wolfhead} feel indifferent to the \glspl{pc}.
Perhaps they want to kill the \glspl{pc}.
However, if they feel they can trust the \glspl{pc}, then they will propose an alliance, just as soon as they can find the \glspl{pc}.

As luck would have it, \gls{southRogue} meets up with them first.

\paragraph{The setting}
depends on where exactly the \glspl{pc} find themselves.
Perhaps \gls{southRogue} finds them in \pgls{bothy}, or while travelling with a caravan of traders on the roads.

\paragraph{The proposal}
must wait until the \glspl{pc} meet the \glspl{wolfhead} in \gls{town}.
The \gls{wolfhead} could do with some muscle, both to help them get about safely, and to secure their magical gateways.

\paragraph{If all goes well,}
the \glspl{pc} and \glspl{wolfhead} can make a plan.
\Gls{beardedalemaster} will agree to finance the plan (assuming the troupe did not conclude \nameref{troubleAle} and leave her penniless), \gls{southSmith} will agree to find any information required (or at least find out how to find it), and \gls{southSmith} will agree to complete any task he can.

\Gls{southRogue} will agree to complete any task, then not do it.

The rest of the tale depends on your table.
