\thread[town,Forest]{The Trouble with Ale}

\label{troubleAle}

\noindent
What dwarves call ale, humans call `hard spirits'.
If you water it down, it makes for a cheap beer substitute.
\Gls{southCook} has decided to capitalize on this by smuggling barrels of dwarven spirit into \gls{town}, through \gls{pigowner}.

\Gls{southCook} has no idea how \gls{pigowner} manages to smuggle the barrels in, and doesn't much care, as she still makes a killing in profits, while undercutting the local \gls{wheatGuild}.

\Gls{alemaster} isn't happy with \gls{southCook} cutting into her profits, so the two sides sabotage each other and shenanigans ensue.

\subsubsection*{Resolutions}

The troupe may resolve this in a number of ways.

\paragraph{The troupe can find the culprits}
in their respective taverns.
\Gls{alemaster} owns \gls{whitehorse}, while \gls{southCook} drinks with \gls{pigowner} when not travelling with the other \glspl{wolfhead}.

\paragraph{Prosecuting the \gls{wheatGuild} members}
in the \gls{court} may work, but \gls{townmaster} does not always make predictable rulings, and the \glspl{pc} may end up in trouble for raising the matter.%
\exRef{judgement}{Judgement}{courtVerdicts}

\paragraph{Coercing both \glspl{server} to the \gls{armourHall}}
will require a clear incentive, but once done, the \glspl{armourer} will ensure they resolve their dispute amicably.
They will demand that \gls{southCook} give \gls{alemaster} a cut of the profits, in return for helping with distribution.
\label{aleResolution}

\paragraph{Failure to resolve}
means the two fight until the fights have destroyed the ale supply on both sides.
People will riot, and the troupe will not be able to drink ale.

And even worse, the townsfolk will begin drinking the water around \gls{town}, and soon contract diseases, such as Spychoke and Guardbane.%
\iftoggle{judgement}{\footnote{See the book of \textit{Judgement}, \autopageref{Spychoke}, for details on diseases.}}


\segment[\squash]{town}% AREA
{The Drunken Outlander}% NAME
{A local \glsentrytext{wheatGuild} \glsentrytext{server} starts fights while pretending to be from \glsentrytext{southDale}'s \glsentrytext{wheatGuild}}% SUMMARY
\label{drunkenOutlander}

Reputation is paramount among the guilds, so \gls{alemaster} wants to discredit \gls{southDale}'s \gls{wheatGuild}.
She pays a few of her staff to dress as members of the \gls{southDale} \gls{wheatGuild} and start fights all over town.

This encounter can easily slip into the background -- the drunkard has no interest in annoying the \glspl{pc}, especially if they look well-armed.

\begin{boxtext}
  A rank wind blows through \gls{town}.
  From the street ahead a drunken man in full plate armour falls against a wall, before getting back up and shouting at passers by that they're pathetic for drinking elvish nonsense, and need a proper dwarvish drink.
\end{boxtext}

Players may notice he's pretending to be drunk with a \roll{Wits}{Medicine} roll, or notice that his insignia does not have the right flowers for \gls{southDale} with a \roll{Intelligence}{Academics} roll.
Both have \tn[10].

If questioned, Carnpox says this is ``just a little joke'', but does not reveal the overall plan.

\paragraph{Investigating the matter}
might employ any number of tactics.
They may track down the \gls{weaversGuild} which created the fake \gls{southDale} insignia, or interrogate Carnpox with threats of the \gls{court}.
Every roll has \pgls{tn} of 11 and takes at last \pgls{interval}, but players can keep trying new approaches while time allows.

\Person{\NPC{\M\Hu}{\Glsentrytext{server} Carnpox}{Bobbing~Adams~Apple}{Pointing at people}{to get paid and go home}}%
  {{2}{0}{1}}% BODY
  {{0}{-1}{1}}% MIND
  {%
    \set{Melee}{1}
    \set{Athletics}{1}
    \set{Deceit}{1}
    \longsword
    \completeplate
  }% SKILLS
  {}% KNACKS
  {\lootMedium}% EQUIPMENT
  {}% ABILITIES

\segment{town}% AREA
{Ale Explosion}% NAME
{Barrels of Ale explode down the street}% SUMMARY

\Gls{alemaster} found that the more ale she brews in a batch, the cheaper the overall brewing process.
She bought cheap houses around the city, and commissioned massive barrels.
However, \gls{southCook} found where they're stored, and paid street-rat children to come in and mess the place up, pulling corks out of the barrels, and such.
Unfortunately, with just a little too much jostling and jumping on the barrels, the unstable equipment exploded.

As three houses, full of giant barrels of ale, all explode at once, it creates a tidal wave of unripe alcohol.
The troupe can avoid being swept down the street by the storm with a \roll{Wits}{Athletics} roll, \tn[8].

\begin{boxtext}
  Suddenly the house to your right explodes, and water rushes down the street, knocking aside stalls, women, two stray dogs, and sweeping the lot down the road.  It foams and froths like mad, and then you notice -- this isn't water, it's ale!
\end{boxtext}

\paragraph{If the \glspl{pc} investigate,}
an \roll{Intelligence}{Vigilance} \gls{bandAct} (\tn[10]) will allow the characters to find the bodies of the children who started the problem, along with the fact that they were recently speaking with \gls{southCook}, who currently drinks in \gls{pig}.

\segment[\squash]{town}% AREA
{The Captain}% NAME
{\Glsentrytext{captain} introduces himself}% SUMMARY

\Gls{captain} is heading home after a long night (if this is the afternoon, it's been a \emph{very} long night).
He introduces himself in a friendly way, points out that he knows they're in the \gls{guard}, but doesn't mind them coming to town once in a while if they don't cause trouble.

\captain

Combine this \gls{segment} with the next \gls{segment} in the \gls{region}.
He helps out the troupe if he can, and may even grant them \glspl{weapon} from the station's armoury if they're in need.

Simply knowing \gls{captain} and where he stays could suggest to the players that they can report \gls{alemaster} or \gls{southCook}, as long as they have any evidence.

\segment[\squash]{Forest}% AREA
{Broken Sword}% NAME
{One of the characters' weapons breaks}% SUMMARY

One of the characters' \glspl{weapon} shatters at just the wrong time.
Whoever uses their \gls{weapon} first has their sword, maul, or whatever break.
However, if the weapon has a name, you should move onto the next potential weapon to break.

This might happen when the character smashes their weapon into an enemy's, or perhaps when stabbing at an enemy so deeply the weapon embeds in a creature's hide, and then snaps off when the weapon is withdrawn.

\begin{boxtext}
  Your sword plunges into the \gls{crawler}'s face, but as you pull it out, the creature twists its body, and your sword shatters.
  You pull out the handle with a metal stump, and the next creature attacks\ldots
\end{boxtext}

This \gls{segment} exists purely to space out the current \gls{thread}, ensuring time for the \glspl{pc} to react.

\segment{town}% AREA
{You Can't Drink Here}% NAME
{People jeer at envoys from \glsentrytext{southDale}'s \glsfmttext{wheatGuild} and a fight breaks out}% SUMMARY
\index{Dwarves!\Glsfmttext{wheatGuild}}

A travelling troupe of three men and three dwarves from \gls{southDale} are tired from a long day's walk, and need rest and drink, but the townsfolk think of the \gls{wheatGuild} from \gls{southDale} as nothing but troublemakers (the devious plan \vpageref{drunkenOutlander} worked).

\Gls{landlord} Strath, an angry dwarvish \gls{server}, has had enough of the bickering and feels tough enough in his full plate armour.
He has no idea that \gls{southCook} has been pulling stunts, such as destroying the stores of the local \gls{wheatGuild}.

\begin{boxtext}
  A crowd is vomiting out of a pub, pushing six men out with them\ldots or rather three men and three dwarves, all heavily armed.
  The crowd shout for them to go back to the mountains and that they're not welcome in the area, but a dwarf, covered in metal from head to toe, and wearing the emblem of the \gls{wheatGuild} from \gls{southDale}, lifts his metal visor and barks back at crowd, listing a litany of laws concerning public houses and the rights of foreign \glspl{server}, with deafening volume.

  The crowd just jeer, making a large vein in the dwarf's head bulge while his face turns redder by the moment.
\end{boxtext}

\paragraph{If the characters do nothing,}
the crowd pelt Strath with some stale pies, and local ale.
He pokes at the jeering crowd with his weapon, and a fight breaks out instantly.
The group then flee the city, and all ale trade with \gls{southDale} stops, as people begin to complain, loudly and violently, outside any establishment which sells the distinctive swill made from \gls{southDale}'s dwarven spirits.

\paragraph{If the characters try to de-escalate the problem,}
give them an appropriate roll.
They have time to try multiple tactics, from asking the crowd to calm down, to threatening to call the guard.
However, the crowd are angry, so all rolls are at \tn[10].

\paragraph{The resolution}
depends on the \glspl{pc} resolving the situation between \gls{southCook} and \gls{alemaster}.
They might be able to make peace between the two, as noted \vpageref{aleResolution}.
In this case, crisis is averted, and you can discard the next \gls{segment}.

If the troupe calms the situation down, they will have Strath's thanks (he insists on buying them all an ale at \gls{pig}), and then \gls{southCook}'s thanks as well.

Alternatively, they may think this situation is not the business of the \gls{guard}.
Officially, they would be correct, but of course the wider world still has consequences, so with or without official duties, they will suffer the consequences.

\dwarvensoldier[\NPC{\glsentrysymbol{abderian}\Dw\M}{\Glsfmttext{landlord} Strath}{Double Braided Beard}{Strokes beard}{Experience}]

\humansoldier[\npc{\T[3]\Hu\M\M\F}{Bough, Fishhead \& Scale}]

These two are heavy drinkers, and heavy fighters, but they will stop as soon as Strath gives the word.

\dwarventrader[\npc{\T[2]\Dw\M}{Drumlin \& Karst}]

\southCook

\segment[\squash]{town}% AREA
{Dry}% NAME
{Guild fights have caused all ale supplies to run out}% SUMMARY

If the party did not manage to avert total disaster in the previous \gls{segment}, play this \gls{segment} together with the next available one.
\Gls{southCook} will not have enough money for the bounty, so skip the last part.

The price of ale has risen steeply, and everyone in \gls{town} feels a little grouchy without their ale.

\paragraph{If the troupe speak with anyone,}
give them a -2 penalty, and have them complain about the lack of good drinks.

\paragraph{If the troupe want a drink,}
the price is 5~\glspl{cp} for alcohol of any kind, or 3~\glspl{cp} for milk (the increased alcohol prices has had a knock-on effect).

\paragraph{If the troupe don't pay for drinks,}
they will have to drink water.
Have them roll \roll{Strength}{Medicine} (\tn[10]) or contract \iftoggle{judgement}{Spychoke.\exRef{judgement}{Judgement}{diseases}}{a nasty disease.}

\segment{town}% AREA
{The Riddle}% NAME
{\Glsentrytext{southSeeker} has raised a bounty on the Riddle of the Gate}% SUMMARY

\Gls{southSeeker} has read about the Riddle of the Gate,%
\footnote{Find the full riddle \vpageref{hardestRiddle}.}
but cannot figure it out.
He's asked \gls{southCook} to put up a bounty on it, but announced it through the local \gls{paperGuild} (area \vref{paperGuild} in \gls{town}).

Now the townsfolk are abuzz with the riddle -- everyone is discussing it, and the 50~\glspl{gp} reward.

If the troupe approach the local \gls{paperGuild}, only \gls{greyLibrarian} knows who posted the reward, but she will -- as usual -- be far too busy to say who.

