\sidequest[Roads,Forest]{The Little Prince}
\label{littleprince}
\index{Elves!Prince}

\noindent
An elf is assaulted by the \glspl{whiteBandits}.
If the characters help, they receive help in return later.
If they join the bandits and rob the elf, other elves will have their vengeance later.

\sqpart{Forest}% AREA
{The Elven Prince}% NAME
{\Glsfmtplural{whiteBandits} attack an elf}% SUMMARY

\begin{exampletext}
  \Gls{elfprince} has become sick of his mother keeping \glspl{crawler} as pets, and decided to see the sea.
  Without knowing where it lies, he figured that if he walked down-hill long enough, he would find it eventually.
\end{exampletext}

However, members of the \glspl{whiteBandits} found him first.

\begin{boxtext}
  A voice in the distant forest cries out.
  \begin{quote}
    I'll summon griffins to pull your stomach out!  I'll enchant you to make you eat until your stomach explodes!
  \end{quote}

  A gruff voice laughs nearby.

  \begin{quote}
    ``If you could, you'd have done it already.  And that's some pretty jewels you got there.  Rich ladies like elf-jewels.''
  \end{quote}

\end{boxtext}

\humansoldier[\npc{\T[8]\Hu}{\arabic{noAppearing} \Glspl{whiteBandits}}]

These bandits were recently \gls{guard} \glspl{gDigger}, but abandoned their post to join \gls{banditking}'s cause.
An \roll{Intelligence}{Empathy} roll (\tn[10]) can indicate that the \glspl{pc} know who they are (or, on a tie, they feel at leat one face is familiar).

\paragraph{If saved,}
\gls{elfprince} will promise to repay the characters sometime, but immediately leaves.

\paragraph{\Gls{elfprince}'s pendant}
is \pgls{artefact}, made from blue-blood crystal, encased in amber.
Its creator made it as \pgls{talisman} to point towards the sea; now it has awakened, it wants to journey to the sea with \gls{elfprince}.

\paragraph{If the \glspl{whiteBandits} take the Seaward Pendant,}
then they eventually run into a troupe of elves (\vpageref{karmaElves}).
The Seaward Pendant tells them exactly what happened, and will describe the \glspl{pc} present when it was taken from \gls{elfprince}.

\paragraph{If the \glspl{pc} take the Seaward Pendant,}
it will silently swear vengeance, and wait for the worst possible time to perform some viscous Water-\gls{sphere} \gls{spell}.
The \glspl{pc} may not notice who exactly cast the spell.

\artefact[1]{Seaward Pendant}% Name
  {A blue-blood crystal shard, encased in amber}% Body
  {0}% Intelligence
  {0}% Wits
  {2}% Charisma
  {to see the sea with \glsentrytext{elfprince}}% Mission
  {Gull Call}% Base Spell
  {
    \setcounter{Water}{3}
    \setcounter{Vigilance}{2}
    \setcounter{Performance}{1}
    \setcounter{Survival}{1}
  }% Spheres

\showStdSpells

\elfprince

\showStdSpells

\sqpart{Roads}% AREA
{\squash~The Debt Repaid}% NAME
{Three elves return to repay the characters for their previous actions}% SUMMARY
\label{karmaElves}

An elven troupe from the same place as \gls{elfprince} decided to journey after him.
If the \glspl{pc} aided \gls{elfprince} before, the troop will aid them in return.
If the characters harmed \gls{elfprince}, the elven troop will have heard of it from the Seaward Pendant.
Or the elves may have no way of knowing what happened, and will pass the \glspl{pc}, and ignore them.

The elves will not approach the \glspl{pc} immediately, but attempt to sneak and observe the party for a while.

\paragraph{If the elves want to hurt the \glspl{pc},}
they use their highest level spells, hopefully while the \glspl{pc} have already entered combat with someone.

\paragraph{If the elves want to help the \glspl{pc},}
they either aid in a battle, or offer a single favour.
The \glspl{pc} must define the favour immediately, because they will never see the elves again.

\elf[\NPC{\M\El}{Sindon}{Lively}{strokes blonde hair}{to see what's happening in the world}]

\ifnumcomp{\value{mp}}{>}{7}{
  \showStdSpells
}

\paragraph{If the \glspl{pc} ask about the brigands,}
Sindon can give them an approximate idea of where the \glspl{whiteBandits} stay, as long as they can understand his references (he does not direct them according to which road and \glspl{village} are near, but by river-currents and tree-types).
Understanding him requires \roll{Intelligence}{Survival} (\tn[10]).

\elf[\NPC{\F\El}{Vanw\"e}{Dour}{Wipes eyes}{to find \gls{elfprince}}]

\ifnumcomp{\value{mp}}{>}{7}{
  \showStdSpells
}

Vanw\"e was in love with \gls{elfprince}, and plans to either aid the characters well, or \emph{really} hurt them (even if it puts her in danger), depending upon their previous actions.

\elf[\NPC{\M\El}{Neuror}{anxious}{spits}{to not get left behind}]
\label{neuror}

\ifnumcomp{\value{mp}}{>}{7}{
  \showStdSpells
}

\paragraph{If the \glspl{pc} ask about \gls{lostcity},}
Neuror begins a repetitive rant about how it was all the humans fault for messing with alchemy, although he doesn't really know many details.

\paragraph{If the \glspl{pc} ask if they have any information about some other elves,}

\begin{description}
  \item[Sindon] says \textit{`elves are not as common as humans, and we have a lot longer to know each other, so ``yes'', we know all the other elves.'}
  \item[Vanw\"e] says \textit{`elves change too often, in form, body, thinking, and (of course) name -- we surpass any human understanding of identification.'}
  \item[Neuror] says \textit{`that's racist.'}
\end{description}

\paragraph{If the \glspl{pc} travel with the elves,}
they ask about buying human clothes, as they don't care about changes in temperature, and travel mostly naked.%
\exRef{stories}{Stories}{elvenInheritance}
