\thread[Roads,town]{The Necromancer's Friend}

\label{necroStory}
\histEvent{320}{05}{\Glsfmttext{necromancer} swears to protect the \glsentrytext{templeOfSickness}}
\begin{exampletext}
  \noindent
  In the time of \gls{lostcity}, high priests of \gls{eldren} took a vow to protect \gls{oldTemple} forever, even past death.
  The priest would then enter a state of semi-death, and remain in eternal meditation, ready to defend against intruders.
  \Gls{necromancer} took the job because he liked archery and birdwatching, and he figured the undead would have a lot of time to watch birds, even if their eyes don't work very well.%
  \exRef{judgement}{Judgement}{undead_senses}

  \histEvent{260}{09}{The \glspl{village} around \Glsfmttext{necromancer}'s temple go empty, due to a combination of economic collapse and increased predators in the area.
  \Gls{necromancer} continues guarding the decaying \glsfmttext{oldTemple}}

  Over the next decades, the \glspl{village} by \gls{oldTemple} collapsed, due to poor governance and knock-on effects.
  \Gls{necromancer} and his stone temple remain, giving him unlimited time to stare at birds.

  After time lost all meaning, bandits came to rest within his temple.
  \Gls{necromancer} felt a sense of dread at the thought of living, self-moving, people approaching him.
  He waited until they slept, then summoned a choking fog to suffocate them, and bashed in their skulls.
  Their death filled him with mana -- the first alchemical power he had access to since his mortal years.
  And he used his knowledge of \gls{alchemy} to create \pgls{talisman}.

  \histEvent{120}{3}{\Glsfmttext{necromancer} kills two burglars, and uses their bodies to make \glsfmttext{bskulls}}
  Using the bandits' bloody skulls as a Fate \gls{ingredient}, and \gls{griffin} wings as an Air \gls{ingredient} (his hunting skills still work), he extracted the bandits' bladders, stuffed them with the griffin wings, stuffed the bladders inside the skulls, and tied the three skulls together with the intestines.
  The completed \gls{talisman}, infused with the Death \gls{sphere}, held a single purpose: to infuse anyone living with undead energy, making them see as the dead see.
  The \gls{talisman} stood as an insult to the robbers, and a beautiful mark of change -- something \gls{necromancer} had not seen in a long time.

  The next century saw a lot of change, as he spoke to the strange, little \gls{talisman}, about birds, and hunting, and his disgust of living things.
  The \gls{bskulls} could not speak, or move, but \gls{necromancer} could see some response in the simple, silent, language of the dead.
  And slowly, over patient decades, the \gls{bskulls} began to talk back.
  The tiny spark of consciousness, present in all \glspl{talisman}, blossomed, and the \gls{bskulls} became \pgls{artefact} -- a thinking, magical construct, focussed intently on its mission.

  \Gls{necromancer} and the \gls{bskulls} Philosophized, and watched the birds together, and forgot that time existed again.

  But time persisted, and one day it brought three more souls to the temple.
  \Gls{necromancer}'s disgust of the living had grown into a phobia, so he rushed up the stairs of the temple's only standing tower, with his bow in hand.
  He shot an arrow, wounded one, then missed with several others as the intruders picked up the \gls{bskulls}, and fled.
  He stood like only the dead can stand, and silently mourned his broken oath, and lost friend.
\end{exampletext}

\Gls{necromancer} has a plan.
He wants an army of \glspl{ghoul} surrounding his temple, to ensure no more \emph{people} approach.
He wants armour, to protect himself and his army.
And he needs a steady supply of living souls.
However, they will have to be \textit{unconscious} living souls, as \gls{necromancer} has developed a serious phobia of living people.
Once he has all this, he can tear apart \gls{valley} until he finds where they took his \gls{bskulls}.

Over the course of this \gls{thread}, \gls{necromancer} grows his army, and destroy several \glspl{village} along the way.
If the \glspl{pc} do nothing, \gls{banditking} will eventually stop him, and gain a lot of support from the remaining \glspl{village}.

\paragraph{If the \glspl{pc} want to search for \Glsentrytext{necromancer}'s Lair}
\label{huntingNecro}
they have a number of options, all of them bad.

\Gls{town}'s \gls{paperGuild}%
\footnote{See \autopageref{paperGuild}.}
has records of the original temple, but they could only research about him if they have something to go on.
A successful \roll{Intelligence}{Academics} roll (\tn[12]) reveals the map in the handouts, and reaching \tn[14] reveals his lair's location (as the map does not have the location on it).

Following the tracks of the undead host will take a long time, although the footprint-path they leave will make them easy to follow\ldots at first.
The \glspl{pc} can roll \roll{Wits}{Survival} at \tn[5], with +2 to the \gls{tn} each day thereafter, and +3 on any day it rains or snows.

If they succeed, find \gls{oldTemple}, but if they need multiple days' of travel to catch up to the host then the tracks may vanish.

\paragraph{If the \glspl{pc} return the \Glsfmttext{bskulls}}
then \gls{necromancer} will stop attacking \glspl{village}.
This resolution is unlikely, but it does indeed resolve the issue.
\Gls{necromancer} will then live peacefully, until his temple crumbles to nothing, and the local stirges eat his body.

\segment[\gls{vlg}]{Roads}% AREA
{The Undead Horde}% NAME
{A botched spell leaves \glsentrytext{necromancer}'s \glspl{ghoul} wandering alone}% SUMMARY
\label{necroHorde}

\begin{boxtext}
  The \gls{village}'s front gate hangs open.
  The houses give off weak smoke, but every door lies open, as if trying to show you the empty darkness inside.
  The only sound comes from a barn, where upset sheep plead for food.
\end{boxtext}

\begin{exampletext}
  \Gls{necromancer}'s first attempt at raiding \pgls{village} did not go according to plan.
  His foul fog made everyone sick.
  Most of the \gls{village} scattered, and he entered to kill the few remaining inside, and consume their souls.
  He stuffed dead spirits inside their empty shells, to raise and consume the living.

  Each of the new \glspl{ghoul} fled in a different direction, chasing the living.
  He spent a little while trying to round them up, but they had gone beyond the range of his spells.

  Eventually, he gave up and returned to his temple, while the dead stood scattered, from river to hill.
\end{exampletext}

Run this \gls{segment} when the troupe approach \pgls{village} which \gls{necromancer} might travel to.
His temple is marked with a `\gls{D}' on the map (\vpageref{Irina/greylands}), and lies upstream of a number of \glspl{village} and hamlets.
He can comfortably travel downriver, since he has no need to breathe.%
\footnote{He can also cast \textit{Bubble} spells to float a little in the water.}
\Gls{necromancer} will never return via roads -- instead, he uses the light which comes off \glspl{village} like sailors use starlight.

\paragraph{Once the troupe reach \pgls{village}}
you should ease slowly into a mounting sense of dread.
The \glspl{ghoul} return to their old \gls{village}, one by one.

\begin{boxtext}[]
  Behind you, a single farmer has returned to the \gls{village}.
  He approaches you, with a sense of urgency\ldots
\end{boxtext}

\ghoul[\npc{\D}{Ghoulish Farmer}]

Each round, more arrive.

\ghoul[\npc{\T[3]\D}{More \Glsfmtplural{ghoul}}]

\ghoul[\npc{\T[7]\D}{Still More \Glsfmtplural{ghoul}}]

Over 100 \glspl{ghoul} head towards them, so keep adding a larger amount each time, until the \glspl{pc} run (or die with bravery, honour, and stupidity).

\paragraph{Once the troupe realize they need to flee}
they can march 2 miles away, add \pgls{ep}, and will probably out-pace the \glspl{ghoul}.

Ask them `where to next?', and continue as if the \gls{segment} had ended, then pull out the next \gls{thread}'s \gls{segment}.
They may head back along the road, or try to go around the ghoulish \gls{village}, by taking a short detour through the forest.
Once the next \gls{segment} begins, have them roll \roll{Intelligence}{Stealth} (\tn[12]).
Success means that they understand how far the dead can see, and how to hide the light of their souls.%
\footnote{Thick clothing helps, as long as it covers everything. Hills and rivers also helps, as they block some of the light of a soul, just like any other light.}
Failure means the \glspl{ghoul} catch up, this time travelling together, as an army.

\paragraph{If they flee to \pgls{broch} or \gls{bothy},}
they will find safety, but won't have any clear means of escape.
Roll encounters as usual -- the \glspl{ghoul} will attack any traders or \glspl{woodspy} which approach, which gives the \glspl{pc} a moment to run out the door, but not much of a head start.

\paragraph{If they flee to \pgls{village},}
then the archers there can help pick off the dead, but they will run out of arrows before the \glspl{ghoul} all drop down\ldots immobile.

\paragraph{If they encounter \pgls{basilisk},}
then they have been saved!
(\glspl{basilisk} have no problem eating \glspl{ghoul}, and the \glspl{ghoul} will not find killing it an easy task).

\paragraph{Tracking down \gls{necromancer}}
presents a thousand challenges.
Have the players roll \roll{Wits}{Survival} (\tn[14] or higher) if they figure out that someone started the massacre, and attempt to track them.

\paragraph{Whatever happens,}
you will have to think on your feet to interpret the clashing of plans with events, as will the players.

\segment[\squash\gls{vlg}]{town}% AREA
{Rumours of a Breach}% NAME
{\Glsentrytext{necromancer} destroys a remote \glsentrytext{village}}% SUMMARY
\label{necroRumours}

\Gls{necromancer} has destroyed yet another \gls{village}, and now has a horde of \arabic{segNo}00 \glspl{ghoul}, along with some \gls{ghast}.
\Glspl{guard} found the \gls{village} two days ago, and now all of \gls{town} is talking about it.

Take a moment to impress on the players what this means for the \glspl{village} around the missing one, and what it means for people travelling across that road, who would otherwise have a place they might rest for the night, behind a wall, with archers.

By this time, \gls{necromancer} has gathered an army of \arabic{segNo}00 undead, and 4~\gls{ghast}.

\segment[\gls{vlg}]{Roads}% AREA
{The Survivors}% NAME
{A few farmers flee a massacre}% SUMMARY

\begin{boxtext}
  On the horizon, four humanoid silhouettes stumble forward silently.
  Once they see you, they start running towards you.
\end{boxtext}

(Run this part only when somewhere close the \gls{necromancer}'s temple, or somewhere downriver, West of \gls{town}.)

The farmers arrive famished.
Most request food.
Fangkrist does not, and doesn't feel like eating.

Fangkrist has been affected by a \textit{Soul Specks} spell.
\Gls{necromancer} cast it on him in order to communicate, and continuously ask where his `beloved \gls{bskulls}' went.%
\footnote{Last night, \gls{necromancer} attacked \pgls{village}, successfully created some \glspl{ghoul}, then enchanted them to follow him.
\Gls{necromancer} noted that they carried a necklace with the symbol of \gls{eldren} --- `\glssymbol{eldren}' --- and instructed the \glspl{ghoul} to spare them.}

Fangkrist will tell everyone what he saw, and ask how to break the curse, before explaining the strange things he can see.
He can also tell the troupe that \gls{necromancer} never went near him, and seemed afraid of going near people.

The curse wears off by the end of the day, as long as he keeps moving.
Until it wears off, he gives everyone strange stares, especially people who can store \glspl{mp}.

\begin{speechtext}
  I can see your inner lights.
  They feel blinding.
  Especially \emph{yours}.%
  What did that creature in the darkness mean?
  He kept on saying it.

  ``My beloved \Glsfmttext{bskulls}''

  ``Where did they take my \Glsfmttext{bskulls}?''
\end{speechtext}

\paragraph{If the characters try to track the ghoulish army,}
they find only one challenge -- if they approach too close, the \glspl{ghoul} may turn, and attack.
An \roll{Intelligence}{Survival} roll (\tn[10]) lets them keep the proper distance.

\Gls{oldTemple} now hosts \arabic{segNo}00 \glspl{ghoul}, a few \gls{ghast}, and an undead \gls{basilisk}.%
\footnote{See \nameref{antBasilisk}, \autopageref{antBasilisk}.}
The farmers will not accompany the troupe when pursuing the undead horde.

Cross out the nearest \gls{village} on \gls{valley} map, as it no longer exists.
Note the nearby \glspl{broch} --- they'll struggle to source food, and many traders will avoid that road now that they can't stay in that \gls{village} overnight.

\boxPair[t]{
  \thenecromancer
}{
  \showStdSpells
}

\newcommand\deadProgressChart{
  \begin{nametable}{Dead Tactics}

    \textbf{Round} & \textbf{Event} \\\hline

    1 & 200 \glspl{ghoul} assault the gate. \\

    2 & 4 \gls{ghast} each attack a quarter of the \gls{village} each (one attempts to open the gate). \\

    3 & \Gls{necromancer} casts offensive spells on anyone at the gate. \\

    4 & The \glspl{ghoul} have formed a pyramid at the gate. \\

    5 & 5 \glspl{ghoul} climb over the gate. \\

    6 & 10 more \glspl{ghoul} climb over the gate. \\

    7 & 15 more \glspl{ghoul} climb over the gate. \\

    8 & Resolve the roll. \\

  \end{nametable}
  \label{necroTactics}
}

\segment[\squash]{town}% AREA
{Armourless}% NAME
{\Glsentrytext{necromancer} kills a trading wagon for their armour}% SUMMARY
\label{necroArmour}

The next time the troupe enter \gls{town}, everyone's talking about the lack of armour.
The prices of armour in all of \gls{valley} doubles for two \glspl{cycle}.
That single wagon may not have carried all \emph{that much}, but when supply problems appear, people panic-buy.

\paragraph{Finding out what happened}
will take time and patience with so many rumours running around \gls{town} about what happened.%
\exRef{core}{Core Rules}{verify_rumours}

\begin{speechtext}
  Some say a dragon took the armour.
  Others say it was the dead.
  Now that's all true enough, but the \underline{real truth} is that the \gls{southDale} \gls{wheatGuild} orchestrated the whole thing.
  Think about it.
  Makes sense, right?
\end{speechtext}

\begin{exampletext}
  \Gls{necromancer}'s \gls{ghast} journeyed out on a mission --- to seize armour for him.
  They found a trading caravan, with one wagon of armour from \gls{southDale} --- leather, chain, helmets, brigandine, the elf-stuff --- she had the lot.
\end{exampletext}

\Gls{necromancer} now has a horde of \arabic{segNo}00 \glspl{ghoul}, along with a few \gls{ghast}, and an undead, armour-plated \gls{basilisk}.
If the troupe try to track him down, remember to check the conditions \vpageref{huntingNecro}.

\boxPair{
  \pic{Decky/necromancer}
}{
  \deadProgressChart

  \ghoul[\npc{\T[9]\D}{200 \Glsfmtplural{ghoul}}]
}

\segment{Roads}% AREA
{The Dead Devour}% NAME
{The necromancer consumes an entire \glsentrytext{village}}% SUMMARY

\begin{boxtext}
  The \gls{village} falls quiet at night, except for shuffling feet as people try to be quiet going out to the toilet at night, or chattering about local town gossip.
  A man in the distance tells his child off harshly for going out at night, past the \gls{edge}, with his friends.
\end{boxtext}

\Gls{necromancer} has gathered an army of \arabic{segNo}00 \glspl{ghoul}.
He takes only 200 \glspl{ghoul} and the 4 \glspl{ghast} out for the raid, leaving the rest behind (too many \glspl{ghoul} can become unmanageable).
Whichever \gls{village} the troupe have arrived at (or near), is the one he assaults.

He arrives at night, and begins some miles away with his \textit{Marshweed} spell (the spell will not work at close range).
The \gls{village} will know he's coming, but they will not be able to do much about it.

\begin{boxtext}
  Crackling sticks indicate someone walks close by, and a moment later indicates a full procession walking somewhere close by.
  But you wait, and no voices come out -- only crackling sticks.
\end{boxtext}

\deathStormSpell

\ghast[\npc{\T[2]\D}{\arabic{noAppearing} \Glsfmtplural{ghast}}]

\ghast[\npc{\T[2]\D}{\arabic{noAppearing} \Glsfmtplural{ghast}}]

\ghoul[\npc{\T[7]\D}{200 \Glsfmtplural{ghoul}}]

\paragraph{The Events}
occur, round by round, as above \vpageref{necroTactics}.

\paragraph{Survival}
depends on tactics, brutality, and -- as ever -- luck.
Give a player a cup with $2D6$ inside, ask them to shake it, and place it face-down on the table.
Explain that the battle will be decided by a single roll of \roll{Intelligence}{Melee} at \tn[16].
The troupe and farmers cannot make this \pgls{bandAct} due to all the commotion, but they can still help each other by killing the enemy, or making a clever plan.

\begin{nametable}{Bonuses}

  \textbf{Bonus} & \textbf{Condition} \\\hline

  1 & per 10 \glspl{ghoul} felled. \\

  1 & per \gls{ghast} felled. \\

  2 & for organizing the \gls{village} with \roll{Strength}{Performance} (\tn[10]). \\

  3 & per clever plan the \glspl{pc} come up with. \\

  4 & for killing \gls{necromancer}, or forcing him to flee. \\

\end{nametable}

Every time they achieve a Bonus, place a die next to the cup, showing their running total.

\paragraph{Spotting \gls{necromancer}}
won't be easy, but the \glspl{pc} may notice the arrows come from well outside the \gls{village}, and that they cannot target anyone properly (they go up and out).

\Gls{necromancer} sends another arrow into the \gls{village} whenever he can see someone.

Despite this large clue, finding \gls{necromancer} in the dark requires an \roll{Intelligence}{Projectiles} roll (\tn[12]).
He stands 30 \glspl{step} away, in the dark.

\paragraph{If anyone approaches \gls{necromancer},}
he flees immediately.%
\footnote{His isolation has given him a phobia of the living.}

\paragraph{If the battle-roll exceeds 16,}
the farmers fight well enough to push the dead back, and \gls{necromancer} flees, along with any still-functional \glspl{ghast} and 100 \glspl{ghoul}.
The \glspl{pc} may take this time to hunt \gls{necromancer} down, but he still has potent spells at his call.

\paragraph{Failure}
means the dead swarm through the \gls{village}, while some small handful of inhabitants flee.

\paragraph{If the dead take the day,}
the \glspl{pc} may be able to flee (the dead have plenty of farmers, and don't need to chase the \glspl{pc}).
Half of the \gls{village} will flee as well.

If the dead continue tearing \glspl{village} apart, civilization will quickly develop problems, as the outer protections no longer protect, and creatures venture farther and farther into the lands of unprotected hamlets.

\segment[\squash]{town}% AREA
{Last Ride}% NAME
{\Glsfmttext{town} leaders argue about the next steps, as all the \glsfmtplural{ranger} died fighting \glsfmttext{necromancer}}% SUMMARY

\Gls{valley} has had enough of \gls{necromancer}'s rampage.
Once \gls{greyLibrarian} figured out where \gls{oldTemple} rested, \gls{lochWarden} ordered every \gls{ranger} in \gls{valley} to approach \gls{oldTemple} and destroy \gls{necromancer}.

\paragraph{If any of the \glspl{pc} are \glspl{ranger},}
then they will hear about this mission while in \gls{town}.
They will have to fight, or prosecution in the \gls{court}.

The details of the fight are up to you.
It should probably begin with a lot of introductions to complaining \glspl{ranger}, and should end with a climactic battle.

\paragraph{If none of the \glspl{pc} are \glspl{ranger},}
then all of the \glspl{ranger} went out a week ago, and never returned.

\begin{boxtext}
  A deep, angry noise interrupts everyone, and \gls{town} becomes silent.
  For a moment, it sounds like \pgls{storm}, then you hear words.

  \Gls{captain} is arguing with someone.
\end{boxtext}

\Gls{investigator} and \gls{lochWarden} have approached \gls{captain}, to tell him that he and the \glspl{sunGuard} must deal with the undead horde which threatens all of \gls{valley}.
\Gls{captain} points out that undead threats don't fall under the purview of the \gls{templeOfJustice}, and that dead \glspl{ranger} only indicate a complete failure in the leadership and planning ability of the \gls{templeOfBeasts}.

The sound of the argument travels half-way across \gls{town}.

\paragraph{If \gls{captain} has already died,}
use \gls{townmaster} or some other substitute.

\segment[\squash~\gls{vlg}]{Roads}% AREA
{More Bad News}% NAME
{yet another \glsfmttext{village} falls to \glsfmttext{necromancer}}% SUMMARY

The \glspl{pc} hear of yet another \gls{village} \gls{necromancer} has destroyed.
He now boasts an army of \arabic{segNo}00 \glspl{ghoul}.

Encounters with \glspl{monster} increase dramatically, all around \gls{valley}, as the thin outer barrier diminishes,%
 %\exRef{judgement}{Judgement}{civilizationRating}
so the \glspl{pc} also hear about various \gls{monster} encounters (select the standard encounters, depending on the current \gls{cycle}).

\segment{town}% AREA
{Rise of the Hero King}% NAME
{\Glsfmttext{banditking} has killed \glsfmttext{necromancer}, and everyone thinks he's cool now}% SUMMARY

The \glspl{whiteBandits} marched out to war with pikes and barricades.
\Gls{sewerking} did all the strategy, and his plan worked perfectly -- the \glspl{whiteBandits} lost only a dozen people during the fight.

For the rest of the \gls{cycle}, everyone in \gls{valley} talks about \gls{banditking}.
Most talk about him as a saviour, though the \glspl{keeper} talk about him as a murderous bandit, and upstart.
