Here comes the mayhem!

\nameref{necroStory} introduces another \gls{fiend}, who tears apart \gls{valley} to feed his undead army.

In \nameref{risingTitles}, the \glspl{diggers} and \gls{whiteBandits} attack the established political powers in \gls{valley}.

Unless the \glspl{pc} intervene, \gls{town} loses its \gls{warden}, and the \gls{valley}'s \gls{templeOfBeasts} loses most of its \glspl{jotter}.
Without its established political powers, \gls{valley} remains defenceless, and the dead will tear it apart.

Hopefully the \glspl{pc} have dealt with \gls{spiderqueen} by this point.
Hopefully \nameref{troubleAle} did not conclude with \gls{town} ravaged by disease.
Hopefully they found the source of all the undead under \gls{town} before the citadel becomes empty, leaving a child in charge of \gls{valley}.
Hopefully they have managed to make a couple of friends or allies to work with.
Because any group which remained politically neutral (and therefore inert) will find their world crumbling around them.

Pulling these \glspl{thread} together depends entirely on what kind of mess the \glspl{pc} have found themselves (and \gls{valley}) in.
The real conclusions rely on what the players manage to discover around the locations, starting in \autoref{forestChapter}, and ending \vpageref{noEnding}.

\setcounter{track}{\thefenestraDay}%
\divide\value{track} by 20%
\set{age}{\thecycle}%
\stepcounter{age}%

The \glspl{thread} assume they take place around
\ifcase\thetrack%
  early \showCycle.
\or%
  mid \showCycle, moving into \showCycle[\theage].
\else%
  late \showCycle, just in time for \pgls{storm} to break for \nameref{risingTitles}.
\fi%

