\section[\Glsfmttext{oolery}]{\Glsfmttext{oolery}~\glsentrysymbol{oolery}}
\label{gnomishPart}
\index{Gnomes!\Glsfmttext{oolery}}

\histEvent{266}{2}{\Glsfmttext{deep} gnomes establish a warren outside of \glsfmttext{town}}

\begin{multicols}{2}
\noindent
Gnomes have enjoyed the safety of living in the centre of \gls{valley} for almost two centuries, but rarely want to enter \gls{town}.
The horses, cattle, drunkards and noise all seem like too much hassle.

By law, they may only have three openings across the hill (so the \gls{sunGuard} can properly monitor them\ldots in theory) and must give a single cart of carrots to the \gls{warden} at the end of \gls{cFive}.
The gnomes certainly deliver the carrots, and ensure no more than three openings exist \emph{at a single time}, but never allow outsiders to enter.
The narrow, twisting tunnels, the doors which open wrong, the signs in three languages (one of them dead) present too much of an obstacle for any of the big folk.
Those not proficient in Gnomish must roll \roll{Intelligence}{Academics} to navigate the warren, at \pgls{tn} equal to 12 plus double their Strength Bonus.

From the outside, the warren looks like a hill peppered with root vegetables, since Gnomes farm from under the soil.%
\exRef{stories}{Stories}{gnomishWarrens}
But underneath the farmland, over five hundred gnomes eat, sleep, and update technical manuals concerning under-farming and the rules for riddles.
\index{Books!Riddle Manuals}
\index{Riddles!Books}


\paragraph{The guardian gnome}
retired from the \gls{guard} some years ago as \pgls{thane}.
The other gnomes use names like `Slicer', `Cutter', `Giggler', and `Go-for-it', but the humans only know the name `Tompf'.

While well-natured, Tompf has a razor-thin rational-streak across a heart of impulse-control problems.
If the \glspl{pc} cause any trouble for the gnomes, they will find this gnome reacts fiercely.

\Person{\NPC{\glsentrysymbol{sylf}\Gn\E}{\Glsfmttext{thane} Tompf}{cleans glasses (refuses to explain what `glasses' are)}{wanders off quietly, while people are talking}{to never feel the sting of boredom}}%
  {{1}{3}{2}}% BODY
  {{2}{1}{1}}% MIND
  {%
    \npcQuote{I had one of them once, but it turned out it wasn't one of them}
    \set{Academics}{1}
    \set{Athletics}{2}
    \set{Crafts}{1}
    \set{Deceit}{1}
    \set{Empathy}{2}
    \set{Medicine}{3}
    \set{Performance}{3}
    \set{Seafaring}{1}
    \set{Stealth}{1}
    \set{Vigilance}{2}
    \set{Melee}{3}
    \set{Projectiles}{1}
    \rapier
    \partialleather
  }% SKILLS
  {\weaponmaster, \guardian}% KNACKS
  {\rations}% EQUIPMENT
  {}% ABILITIES

\paragraph{If the troupe ask about \gls{keras},}
the gnomes say he's out in the forest, `gathering cobwebs'.

\end{multicols}

