\section{\Glsfmttext{pig}}
\index{Taverns!\Glsentrytext{pig}}

\begin{multicols}{2}

\begin{boxtext}
  Two men are pummelling each other in front of the pub's door.
   One limps and the other's nose is burst open and streaming down his shirt, but they continue circling like boxers.
   Two guards cry out and run forward to stop the public disturbance, and the two men immediately run together into \gls{pig}.
   The guards stop at the door, look at each other for a moment, and then walk away.

  \Gls{pig} never treats the \gls{sunGuard} well.
\end{boxtext}
 
The roughest and oldest pub in \gls{town} sits close to \gls{town}'s entrance.
\Gls{pigowner}, keeps the place in order with a mixture of services for the roughest characters in \gls{town}, friendships with guild seniors, and rare -- but sudden -- violence.

When \glspl{sunGuard} complain about miscreants and knaves in the tavern, \gls{pigowner} reminds them that the tavern falls under the jurisdiction of the \gls{wheatGuild}, so she will take charge of keeping order in her own `temple'.
The fact that she spends most of her time drunk doesn't detract from her status as \pgls{landlord}, or stop the occasional noble asking her to sneak contraband into the city.

Currently, \gls{pig} hides the \glspl{diggers} in rooms underneath, as they help \gls{pigowner} move things in and out of the city without going through the \glspl{sunGuard} at the gates.%
\footnote{See downstairs, area \vref{farmExit} for the exterior route.}

\begin{boxtext}
  Joyful, out-of-tune song and roasted pig hits you in the face as soon as the door opens.
  With only three tables in the room, people have carved out little seating circles on the ground.
  A fat, black-and-white cat with a brown collar sits in the rafters and eyes you suspiciously as you struggle through the disorganized crowd to get to the bar.
\end{boxtext}
\label{pigCat}

\mapentry[pigHall]{Beerhall}

Here miscreants drink, except for Mog -- the cat -- who spends his time sitting on people while cleaning himself.
The bar has a small step-ladder, so gnomes and dwarves can comfortably walk up to request food and drink.

Roll $2D6$ to find the state of the tavern, and use both results.

\begin{dlist}
  \item
  The kitchen is working!
  And a massive meal costs only 2~\glspl{cp}
  (otherwise, it does not work).
  \item
  Mog has taken a liking to the \gls{pc} with the lowest \roll{Charisma}{Empathy} total, which means they receive free ale as long as they sit there, with Mog on their lap.
  \item
  \Gls{sewerking} drinks quietly in the corner.
  \item
  \Gls{southCook} drinks in the corner with \gls{pigowner}.
  \item
  $1D6$ \glspl{diggers} have arrive to enter room \vref{pigPrivate}, and then move underground.
  \item
  $1D6$ \glspl{diggers} exit room \ref{pigPrivate} with some barrels, and place them in room \vref{pigKitch}.
\end{dlist}

\pigowner

\paragraph{Any trouble here}
receives a vicious response from \gls{pigowner}' most loyal customers.

\humanmaid[\npc{\T[3]\Hu}{Loyal Customers}]

\humanmaid[\npc{\T[3]\Hu}{Loyal Customers}]

\begin{boxtable}[lYYYc]
  \textbf{Name} & \textbf{Att Bonus} & \textbf{Dam Bonus} & \textbf{\Gls{weight}} \\\hline
  \showWeapon{\chair} \\
  \showWeapon{\firepoker} \\
  \showWeapon{\skillet} \\
  \showWeapon{\knife} \\
  \showWeapon{\Log} \\
  \showWeapon{\woodaxe} \\
\end{boxtable}

\mapPic{t}{Dyson_Logos/mincing_pig}{
  \ref{pigHall}/11/46,
  \ref{pigKitch}/10/73,
  \ref{pigPrivate}/25/73,
  \rotatebox{-90}{\large F}/26/785,
  \ref{pigDen}/35/81,
  \ref{pigRoom}/42/89,
  \ref{pig_pantry}/35/96,
  \ref{runoff}/35/60,
  \ref{pigShaft}/51/60,
  \ref{pigTemple}/73/78,
  \rotatebox{-90}{\large S}/73/68,
  \huge\ref{pigDogs}/82/33,
  \Large\ref{pigBank}/75/52,
  \large S/82/43,
  \rotatebox{-90}{\large S}/795/40,
  \ref{pigDown}/85/09,
  {\small\vref{sewerPigWalk}}/85/04,
}

\mapentry[pigKitch]{Kitchen}

\Glspl{server} of the \gls{wheatGuild} work here.
Staff turnover is very high, so the \glspl{pc} will not see the same faces twice.

\begin{boxtext}
  A woman arrives to take your order.
  She looks through you, to the rabble, and shouts  ``\textit{it's no good here nowadays, too crowded!}''.

  The crowded centre table shout back in unison, ``\textit{\gls{pig} was never good!}''.
\end{boxtext}

\southCook

\mapentry[pigPrivate]{Fake Storage}

This room is so stuffed with barrels (some empty, some full) that it's unclear how anyone manages to move more in.
The trick half down to the trapdoor, and half down to good organization.
Every time a barrel moves in, someone below pulls a barrel down the hatch, and comes up to make a little space, and ensure a causeway for people to go between the hidden basement and the rest of \gls{pig}.

If anyone watches closely, they'll notice some people enter here, but don't exit, or the door will remain closed for hours, before someone exits.

\paragraph{Identifying the causeway and trapdoor}
requires an \roll{Intelligence}{Crafts} roll (\tn[10]).

\mapentry[pigDen]{Thieves' Den}
The \glspl{diggers} sit in the stale here, playing card-games, and plotting how to avoid work.
A number of local thieves know of this secret and secluded room, but they will not feel eager to piss of \gls{pigowner}.

\begin{boxtext}
  Three men sit cross-legged on the floor, quietly playing cards.
  The second they see you, an additional layer of silence enters the room.
\end{boxtext}

\humanthief[\npc{\T[3]\Hu}{Three Cutthroats}]

\mapentry[pig_pantry]{Pantry}

\Gls{pigowner} stores additional casks of ale, the good wine, \rations, \rations, and \rations.

Anyone searching hard enough can also find \lootTalisman, recently stolen from \gls{alchemist} (details \vpageref{talismanIndex}).

\mapentry[pigRoom]{\Glsentrytext{pigowner}'s Room}

\Gls{pigowner} lives in a mess of old notes about what she owes to whom, chests of illegal weapons%
\footnote{Weapons are not illegal but stockpiling more weapons than an individual can use \emph{is}.}
hidden under clothes, alcohols, and poisons, all lying about unlabelled.

\textbf{Weapons:} 18 mauls, 16 shortswords, 5 longswords, 20 longbows, 400 arrows, and 20 daggers.

\mapentry[runoff]{Runoff}

\begin{exampletext}
  A gnomish \gls{server} who once worked here put up a wire guardrail in front of the running water, as a safety precaution.
  However, she stood at half the height of a human, so the `guardrail' now functions as a tripwire.
\end{exampletext}

\begin{boxtext}
  A little river gurgles ahead.
  It springs from a crack in a tunnel, to the right, and heads down a greasy slope into darkness.
\end{boxtext}

Little pipes, nooks, and gutters in the city lead underground.
A little drain from above pops out here, and heads steadily downhill, eventually landing in the sewers below (see area \vref{sewerPigWalk}).

The first member of the party to look down the tunnel rolls to spot the tripwire (\roll{Wits}{Vigilance}, \tn[8]), and failure means they immediately go tumbling downwards to the sewers.
Once down the drain, they roll \roll{Speed}{Athletics} to push against the walls, at \tn[9].
Each failed roll increases the \gls{tn} by 1, until they descend into the unforgiving darkness which rests below the world.
Each round they remain down there inflicts \pgls{ep}, so any companions who wish to rescue them had better act quickly.

\mapentry[pigShaft]{Ventilation Shaft}

This little tunnel reaches upwards to allow a modicum of fresh air to circulate down in the nasty little dungeon.
Characters with a Strength of 0 or greater are too large to fit through the narrow hole.
It emerges on a street, just below a rich man's house.

\mapentry[pigTemple]{Temple Passage}

\begin{exampletext}
  The old \gls{templeOfSickness} once took the bodies of the honoured dead through this passage, to the ossuaries below.
  Since the flooding, they've bricked up the entrance, covered it with a tapestry, and no longer think about this out-of-the-way basement.

\end{exampletext}

Loose bricks in the wall let the \glspl{diggers} steal into the \gls{healersGuild}, and take the sick and dying, through tricks or force.
See \vpageref{ghastPlan} for more on their plan to use the dying to make ghasts.

\paragraph{Noticing the sliver of shadow-entrance}
requires a \roll{Wits}{Crafts} roll (\tn[9]).

\mapentry[pigDogs]{Sleeping Dogs}

Some of the more trusted \glspl{diggers} sleep in these little alcove-bedrooms.
Each one has little more than blankets and clothing hooks.
A couple have items, such as daggers, or saved coinage stuffed into obscure locations in the room.

In total, \lootMedium\ exists stuffed into pillows, or ties into the corners of the room where the deepest shadows remain.

\mapentry[pigBank]{Piggy Bank}

\Gls{sewerking} has made a little `piggy-bank' for himself here.
He created a secret little room, between two others.
On the bottom side, a hatch exists, locked tight with bolts, and a key.
The other side remains permanently boarded up, with a hatch, which can only open wide enough for a couple of fingers to get in.

Whenever \gls{sewerking} wants to store some valuables, he tells the other \glspl{diggers} that he wants to place something in his `treasure room', then enters the side with the secret hatch, and stuffs it in.

To stop people stealing from him, he placed a bag of 50~\glsentrylongpl{cp} beside the hatch, so would-be thieves could take that, instead of his actual valuables.
He also placed \pgls{ghast} inside the room, ready to spring out whenever anyone opened the door.

If the \glspl{diggers} ever have serious need of cash, he will stab through the wood, killing the ghast before entering.

\ghast[\npc{\D}{Ghast-in-the-Box}]

In total, the room contains \lootBig, and one \lootTalisman.

\showTalisman

\mapentry[pigDown]{Descent to Catacombs}
This path downwards leads to the thieves' den underground (see room \vref{sewerPigWalk}).

\end{multicols}
