\prisonMap

\section{Station Dungeon}
\label{stationDungeon}
\index{Prison}

\begin{multicols}{2}

\begin{exampletext}
  \noindent
  Last month, \pgls{ogre} escaped past the \glspl{goldenPriests}, and ran through \gls{valley}, eating every auroch, \gls{crawler}, and human he came across.
  And by some miracle, \pgls{guard} managed to capture and bind him.

  \Gls{townmaster} ordered the \gls{sunGuard} to keep it alive so he and \gls{alchemist} could better understand it.
  Since then he's forgotten about it, but the guards have to keep feeding it.

  The \gls{ogre} can't speak the local language, but everyone knows what it wants to say -- `food'.
  Twice a day, they take a cart down the stairs, deal out a small portion to each of the inmates, then place the rest by the ogre's cell as a massive, grabbing hand reaches through and piles the food into its mouth.
  Sometimes it tries to grab the guard feeding it.
  Sometimes it grabs the cart of food and throws it at the guard.
\end{exampletext}

\paragraph{If the \glspl{pc} enter as prisoners,}
they will have to think a lot about how to escape -- this won't be easy!

\paragraph{If anyone tries to pick the locks,}
they will need to craft some make-shift equipment first, and make sure nobody is listening to them.
The roll is \roll{Intelligence}{Larceny}, \tn[12].

Once someone has picked a lock, they can automatically pick every other lock, because the same \gls{natural} applies.

\paragraph{Every day,}
the guards give them two small meals and empty their bucket.

The meals are so small that they gain 1~\gls{ep}, daily.

\paragraph{On day 2,}
a scout form the \gls{guard} gets thrown in a cell for dereliction of duty (he living with villagers and sending back false reports).

\paragraph{On day 4,}
\gls{beardedalemaster} lands in a cell for insulting \gls{townmaster} during a meeting.
She will stay here only one night.

\mapentry[dunStorage]{Storage}

Every day, the guards take the food cart down to the hall, and unload the contents into this room.

A chest, sealed with an intricate knot, contains good quality wine.
The higher ranking guards leave the wine here, and won't tell Cronsink how to open it.

\paragraph{If any prisoners listen carefully,}
they will hear the bottles being deposited while guards talk about their rare vintage.

\mapentry[guardStationRoom]{Shitlist Lodgings}

The \glspl{sunGuard} on \gls{captain}'s shitlist have to sleep down here.
Another guard stays in the \nameref{mainPrisonRoom}, room~\ref{mainPrisonRoom}, below, so that two remain on shift at all times.

Two keys to the cells (one for the top row of cells, and another for the bottom), hang on the wall, and a third key for the chest in room~\ref{thingsRoom}.

\Person{\NPC{\F\Hu}{Hordcut the Guard}{arrogant}{`ha!, yea right\ldots'}{a promotion}}%
  {{1}{2}{0}}% BODY
  {{0}{0}{-1}}% MIND
  {%
    \set{Melee}{1}
    \set{Deceit}{2}
    \set{Crafts}{1}
    \shortsword
    \partialplate
  }% SKILLS
  {\brawler, \berserker}% KNACKS
  {\lootSmall}% EQUIPMENT
  {}% ABILITIES

\mapentry[mainPrisonRoom]{Main Hall}

At least one guard remains here at all times.
\begin{itemize}
  \item
  When Hordcut is on shift, she tells the prisoners to shut up.
  If they don't, she'll open the doors and bash their heads in.
  \item
  When Cronsink comes on shift, he tells prisoners to shut up, or tries to get them to sing with him while he drinks.
  He passes out from drinking too much shortly afterwards.
  \item
  When both are up and awake, they play cards together, and he complains that Hordcut always wins.
\end{itemize}

\humanfarmer[\NPC{\M}{Cronsink the Guard}{hopeful}{swigs bottle}{to be able to sing}]

\mapentry[shroomCell]{Fungi Cell}

This little cell holds an infection of \glspl{bedshroom} -- enough for 3 Air~\glspl{ingredient}.
The growth has begun to weaken the wall -- a sufficient push can dislodge the bricks between cells, and provide an opening big enough for anyone with \pgls{weight}~6 or less.

\mapentry[bardCell]{Bard Cell}

If the \gls{sunGuard} have arrested \gls{warningbard}%
\footnote{See page \pageref{warningbard}.},
he sits here, singing to himself.

\mapentry[ogreCell]{Ogre's Cell}

Here the wretched \gls{ogre} stays, unable to do more than sing, and eat too seldomly.
With a \roll{Intelligence}{Performance} roll (\tn[5]), a character might sing along.
From that point on, Laban will trust them, and not eat them unless he has no other food.

\Person{\npc{\M\N}{Laban the Ogre}}%
  {{6}{0}{3}}% BODY
  {{-3}{-2}{-4}}% MIND
  {%
    \set{Melee}{1}
    \set{Brawl}{2}
    \set{Empathy}{2}
  }% SKILLS
  {}% KNACKS
  {lucky chicken bone}% EQUIPMENT
  {}% ABILITIES

\paragraph{If anyone stages a breakout,}
Laban comes with them, but immediately stops to eat anything (or anyone) he can.
Once satiated, he will continue following anyone leading a prison break.

\mapentry[dunBro]{Oh Brother\ldots}

Spybroth sits here, depressed about his past (he shouted that \gls{townmaster}'s last verdict in the \gls{court} was an outrage) and future (most likely the \gls{guard}).
If anyone speaks hopefully about escape, he tells them everything that will go wrong with the plan.

If the \glspl{pc} prove one of his melancholic predictions wrong, he helps them escape, then goes to hide with his sister, \gls{greyLibrarian} in the \gls{paperGuild}.

\Person{\NPC{\M\Hu}{Spybroth}{doomsayer}{sings `nobody knows the trouble I've seen'}{freedom}}%
  {{1}{0}{1}}% BODY
  {{0}{-1}{0}}% MIND
  {%
    \set{Melee}{1}
    \set{Larceny}{1}
    \set{Stealth}{2}
    \set{Survival}{1}
  }% SKILLS
  {}% KNACKS
  {\lootSmall}% EQUIPMENT
  {}% ABILITIES

\label{spyBroth}

\mapentry[dunGrate]{The Grate}

Here all the filth and debris collected from the prisons gets thrown in the hole.

\paragraph{Breaking the grate open}
requires a \roll{Strength}{Crafts} roll (\tn[10]).
It leads straight downwards to room~\vref{sewerWaterHall} in \nameref{sewers}.

\mapentry[thingsRoom]{Prisoners' Possessions}

The chest contains any valuable items the prisoners carried which might fit inside the chest.
The key rests in room~\ref{guardStationRoom}.

Their other possessions lie scattered across the room, along with some musical instruments.

\mapentry[weaponsRoom]{Weapon Storage}

This storeroom has handheld weapons, siege weapons, and basically every weapon listed anywhere.%
\exRef{core}{Core Rules}{weaponschart}

\end{multicols}
