\section{Cinderfilch \Glsfmttext{broch}}
\index{Cinderfilch|glsentrysymbol{sylf}}
\label{cinderfilch}

\mapNotes[\Large]{
  \huge Cinderfilch's \glsentrytext{broch}/78/96,
  Lower Block/08/46,
  \ref{cinderBase}/09/19,
  \ref{cinderStraw}/09/60,
  \ref{cinderOffice}/50/19,
  \ref{cinderBows}/50/90,
  \ref{cinderFood}/94/19,
  \ref{cinderUpper}/84/24,
  \ref{cinderBeds}/84/77,
  Middle Block/5/00,
  Upper Block/9/47,
}

\widePic{Dyson_Logos/broch_map}

\begin{multicols}{2}

\noindent
You can start any session anywhere, but Cinderfilch \gls{broch}%
\footnote{The \gls{broch} took its name from \pgls{warden}'s daughter, who was eaten by \pgls{woodspy}.}
makes a good default, especially for the first session.
It sits on a semi-popular road, so travellers and traders often come by to stay the night, and complain about the fact they have nowhere to put their horses.
If the troupe happen to be here when that happens, they'll have to stay outside, with lit fires all around the \gls{broch}, to make sure the horses stay safe (people value horses far more than \gls{guard} Fodder).

The current \gls{cycle} is \showCycle, and the wind feels \showTemperature.
\ifcase\value{temperature}%
  \Gls{snow} \glsdesc{snow}.
\or%1
\or%2
\else%3
  \Glspl{heatwave} \glsdesc{heatwave}.
\fi%

\subsubsection{Missions}
come from the \gls{jotter}, in room \ref{cinderThree}.%
\exRef{judgement}{Judgement}{NGmissions}
These might be easy (\textit{accompany these traders}), or more challenging (\textit{guard that \gls{village} for a week}), but once they step onto the road, they should have a little freedom to engage with the various \glspl{sq} before long.

The \gls{broch} contains:

\begin{enumerate}
  \item
  Six \glspl{guard}, chatting.
  \label{cinderBase}
  \item
  Straw and firewood.
  \label{cinderStraw}
  \item
  \Gls{jotter}'s office.
  \label{cinderOffice}
  \item
  \Glspl{soldier}' outpost, with plenty of arrows and hunting bows of every size.
  \label{cinderBows}
  \item
  Food storage (\rations, \rations, \rations, et c.)
  \label{cinderFood}
  \item
  Two \glspl{ranger} currently passed out.
  \label{cinderUpper}
  \item
  Bedding for three people, or a dozen \gls{guard}.
  Archery equipment and firewood for the beacon at the top.
  \label{cinderBeds}
\end{enumerate}

\end{multicols}
