\index{Market!Roads}
\chapter{Guarded Roads}
\epigraph{A rock is a good thing, too, you know. If the Isles of Earthsea were all made of diamond, we'd lead a hard life here.}{Ursula Le Guin}
\label{roadsChapter}

\begin{multicols}{2}
\noindent
Each time the \glspl{pc} go to \gls{town} or the forest, they must pass through this middling \gls{region}.

\Gls{banditking}, the would-be \gls{warden} to \gls{valley}, hides in the \nameref{banditLair}, just past the \gls{edge}, and slowly gathers a small army of malcontents, mostly from the \glspl{guard}.
His messenger will also approach \glspl{pc}, who will have to decide whether or not to join his violent revolution.

Take a look at the thin crust of protective structures surrounding delicate fields on the map \vpageref{Irina/greylands}.

\begin{itemize}
  \item
  The little houses on the inside are scattered hamlets, each controlling large amounts of farmland, full of grazing livestock.
  \item
  The outer structures with multiple rooves are \glspl{village}, with tall walls to defend themselves from the constant probes from \gls{sylf}'s children.
  \item
  The structures with a single tower are \glspl{broch}.
  Each morning and evening, the \glspl{guard} of these tall towers play loud pipes to attract the forest's \glspl{monster} towards them, and away from the inner farmlands.
\end{itemize}

When \pgls{fiend} destroys any \gls{broch} or \gls{village}, you should take a pen, and score out the settlement.

\end{multicols}

\printAllSideQuests{Roads}
\label{sqListRoads}

Fold the page so you can find these summaries later.

\section{Fertile Fields}

\begin{multicols}{2}

\noindent
Most \glspl{village} and hamlets on the map (\autopageref{Irina/greylands}) have no name in this book; keeping track of so many inconsequential locations would just be a pain.
Instead, you should name these locations as they come up, and keep track of any which the players respond to.

Here are a few example names:

\begin{description}
	\item[Liskill]
  where a farmboy killed \pgls{basilisk} with one arrow.
  \index{Liskill}
	\item[Twolisk]
  where a farmboy killed two \glspl{basilisk} with two rocks.
  \index{Twolisk}
	\item[Newarp]
  where people from \gls{archwarp} resettled after it fell, over two centuries ago.
  \index{Newarp}
	\item[Talltail]
  where tall grass grows.
	\item[Fortibane]
  where Fortima Grey killed \pgls{whiteplains} trader for arguing with her about the taxation on the \gls{town} river.
	\histEvent{97}{5}{\Glsfmttext{warden} Fortima Grey argues with a trader from \glsentrytext{whiteplains} over taxation, and kills him with her rapier}
	\item[Artcull]
  named after \pgls{proctor} who stopped the fighting between Liskill and Twolisk.
	\item[Cullend]
  where \Gls{proctor} Artcull tried to make peace between \gls{valley} and \gls{whiteplains}, which resulted in Fortima Grey stabbing him through the neck with her rapier.
  \index{Cullend}
	\item[Fortend]
  where \Gls{warden} Fortima Grey bled to death, after a duel with \pgls{whiteplains} \gls{warden}.
	\histEvent{90}{2}{\Glsfmttext{warden} Fortima Grey falls in a duel with \Glsfmttext{warden} Graupel Whiteheart}
	\item[Sanspipe]
  which was built without a nearby \gls{broch}, and had to survive alone for half a century.
	\item[Songmare]
  known for selling horses that can sing, and lying about their goods (previously called `Tenlisk').
\end{description}

\end{multicols}
