\section{Redfall, Fallen}
\label{redfallFallen}

\mapPic{t}{Dyson_Logos/redfall_keep_fallen}{
  \ref{lobbing_tower}/50/5,
  \ref{keep_ogres}/37/71,
  \ref{keep_patrol}/84/50,
  \ref{food_storage}/81/16,
}%

\begin{multicols}{2}

\noindent
If the citizens of \gls{town} overrun \gls{redfall} (see \autopageref{mastersBounty}), and goblins escape from under the \gls{greentower} (`\nameref{catacombsUnderTower}', \vpageref{catacombsUnderTower}) then the goblins take up permanent residence in \gls{redfall} keep.

The goblins pose a real threat for two reasons:

\begin{enumerate}
  \item
  Traders find them threatening, so they won't pass through.
  \item
  The goblins have no food.
  They found plenty to hunt, but they can't hunt in a civilized area, as it has no aurochs, deer, or other game.
\end{enumerate}

\begin{description}
  \item[On day one,]
  twenty of the goblins leave to hunt game, in two teams of 10.

  \item[On day two,]
  the remaining goblins run out of food, and begin stealing apples, two goats, and a pie (everyone in \gls{redfall} blames Snatchfen for leaving her pie by a window).

  \item[On day three,]
  the goblins kill three cows in the night, but the farmers chase them away before they can return to the keep with the corpses.

  \item[On day four,]
  a raiding party return, and the \gls{redfall} farmers plan to attack the keep.

  \item[On day five,]
  the farmers attack, \pgls{ogre} throws rocks at them, and they flee.

  \item[On the fifth night,]
  the goblins set fire to all the houses, and the farmers flee \gls{redfall}.
\end{description}

\goblin[\npc{\T[6]\N}{Hunting Party}]

\goblin[\npc{\T[6]\N}{Hunting Party}]

\mapentry[keep_ogres]{Philosophical \Glsfmttext{ogre}}

\Pgls{ogre} tells the goblins a tale of goblins being pushed underground by humans coming to \gls{fenestra}, and how they will reclaim their lands once they eat the humans.

\ogre[\npc{\F\N}{Fireside \Glsfmttext{ogre}}]

\goblin

\mapentry[keep_patrol]{Patrolling Goblin}

A single goblin patrols the keep.
She will talk with anyone who speaks the language of the \gls{deep} and looks unthreatening, as she has eaten well already.
Otherwise, she flees and alerts the others.

\goblin[\npc{\N\F}{Wandering Scout}]

\mapentry[food_storage]{Food}

Anything the goblins catch stays in here.
Right now, supplies run low -- half a deer, some stolen milk, and bits of dead otter.

\mapentry[lobbing_tower]{Rock Lobber Tower}

\Pgls{ogre} stays up here, ready to throw down massive rocks.

\ogre[\npc{\M\N}{Roch-Hucking \Glsfmttext{ogre}}] \end{multicols}

