\mapPic{b}{extracted/redfall}{
  \large\glsentrysymbol{paik}/50/90,
}

\section{\Glsfmttext{redfall}}
\label{redfallVillage}

\begin{multicols}{2}

\noindent
\Gls{redfall} is a standard inner settlement --- a hamlet.%
\footnote{Like other words, this one has become slightly twisted in \gls{fenestra}, as these `hamlets' are characterized by being inside the great barrier of outer \glspl{village}, meaning far fewer predators will approach them.}
If trouble arrives, the \gls{sunGuard} archers in the keep typically make an awful lot of noise to draw the creature in, then loose their arrows when it approaches close enough.

\widePic[t]{Dyson_Logos/redfall}

The people in the area create pottery from the rich clay deposits.
They also enjoy a rarity in \gls{fenestra} --- fruit trees.
Large patches of foliage, fern, and trees invite predators to hide in their shadows, but these creatures so rarely approach this close to \glsentrytext{town}, that \gls{redfall} enjoys them safely.
\ldots or they did until \gls{hungrywarden} sent his \glspl{sunGuard} out to take all of their fruit, and demanded seconds.

The recent hike in taxes has driven the now-hungry farmers to desperate measures
(see \vpageref{desperatemeasures} for more on the consequences).

The docks once had a few barges coming down each week, but almost none come down here now, as they receive heavy taxes at the bridge.
If anyone has (or steals) a boat, they will arrive in \gls{town} within \pgls{interval}.

\begin{boxtext}
  \Gls{redfall} seems peaceful, almost idyllic, as children play next to copse of trees without any fear of beasts waiting for them inside.
  Women collect the red earth by the river so they can process it into their famous pottery later.
  Ahead, the keep stands three stories high.
\end{boxtext}

\paragraph{When the \glspl{pc} enter,}
if they look like might be officials or soldiers of any type, the farmers act natural at first, but arrange to surround the troupe at the bridge.

\begin{boxtext}
  As you step onto the bridge, you see a dozen men walking behind you with large bags covering their heads and another sack in their hands.
  In front, another ten with sacks gather as well.
  Ahead and behind, they pull the rocks out.

  ``No more taxes!'', they shout.
\end{boxtext}

\Person{\npc{\T[4]\Hu}{\arabic{noAppearing} Angry Farmers}}%
  {{2}{0}{0}}% BODY
  {{0}{-1}{0}}% MIND
  {%
    \set{Projectiles}{1}
    \set{Crafts}{1}
    \set{Cultivation}{2}
    \Dagger
  }% SKILLS
  {\specialist{husbandry}}% KNACKS
  {\rock $\times 6$}% EQUIPMENT
  {}% ABILITIES

\paragraph{If the \glspl{pc} try to reassure the farmers,}
have them roll \roll{Strength}{Empathy} (\tn[9]) to holler their message to everyone present.
Failure indicates a nasty pelting, although the residents don't intend to kill the anyone --- just drive them off.
A tie gives the \glspl{pc} the option to flee before the pelting.

\paragraph{If the \glspl{pc} ask about the keep,}
the residents complain bitterly, but have no idea that \gls{hungrywarden} has become a monster.

\paragraph{If the troupe attempt to persuade the farmers to assault the keep,}
they can succeed with a \roll{Charisma}{Melee} roll, \tn[10]
(the farmers feel more confident with an experienced tactician leading them).
Of course the farmers also know that the fortress is armed with archers, and will only agree to enter if the troupe have a solid plan concerning the archers.

Roll Morale checks for all involved, as usual.%
\exRef{judgement}{Judgement}{morale}
The battle will likely end before either side loses too many members.

\mapPic{t}{Dyson_Logos/redfall_keep}{
  \huge\ref{redTower}/06/68,
  \huge\ref{redTower}/06/08,
  \Large\rotatebox{0}{\nameref{redTower}}/05/80,
  \huge\rotatebox{-45}{\nameref{redYard}}/34/50,
  \ref{redYard}/28/46,
  \Large\rotatebox{-45}{\nameref{redToilet}}/52/26,
  \huge\ref{redToilet}/545/34,
  \Large\nameref{redKitchen}/31/79,
  \ref{redKitchen}/30/75,
  \Large\rotatebox{-45}{\nameref{redServants}}/43/75,
  \ref{redServants}/41/73,
  \huge\ref{redChild}/85/19,
  \huge\ref{redStable}/65/24,
  \Large\rotatebox{45}{\nameref{redChild}}/84/28,
  \Large\rotatebox{45}{\nameref{redSmolYard}}/75/34,
  \ref{redSmolYard}/65/36,
  \ref{redMechanism}/54/50,
  \ref{redFire}/63/56,
  \ref{redTable}/63/76,
  \large\ref{redCloset}/52/75,
  \huge\nameref{redHall}/63/93,
}

\subsection{\Glsfmttext{redfall} Keep}
\label{redfallKeep}

The keep contains a conspiracy: everyone in there knows that they harbour monsters, but they also know that those monsters can be cured, and that if they tell anyone, they'll lose their employment, and will either have to beg or join the \gls{guard}.

The various staff will only use their \glspl{bow} --- none are dim enough to fight toe-to-toe.

\paragraph{Climbing}
requires a \roll{Speed}{Athletics} roll at \tn[12].
The entire keep sits on raised earth, 2~\glspl{step} high, and the stone walls are 4~\glspl{step} high.

\paragraph{Observing the keep for a day}
involves finding a place to hide, and hearing the sound of chewing, arguments, and Bairnpelt banging, gurgling, and `playing` with the \glspl{sunGuard} (room \vref{redChild}).
They can also find a crumbling wall by the \nameref{redSmolYard} (\gls{area} \vref{redSmolYard}) (\roll{Intelligence}{Athletics} at \tn[8]), which anyone can climb at \tn[8].

\mapentry[redTower]{Towers}

Each of the towers has two \gls{sunGuard} archers (\vpageref{redArchers}), ready to protect their patron, \gls{hungrywarden}, as long as nobody gets too close.
If approached, they surrender.

\boxPair[b]{\label{redArchers}
  \humanarcher[\npc{\T[2]\glsentrysymbol{paik}\Hu}{Archers \composeHumanName\ \& \composeHumanName}]
}{
  \humanarcher[\npc{\T[2]\glsentrysymbol{paik}\Hu}{Archers \composeHumanName\ \& \composeHumanName}]
}

\mapentry[redYard]{Courtyard}

\begin{boxtext}
  You enter the \nameref{redYard}, flanked by two small, square rooms, only double the width of their own doors.
  To the left, a door up  to the archers' tower above, and a door to the windowless room with a red slate roof.
  To the right, a massive room at the base of the second archer's tower.
  And straight ahead, \gls{redfall}'s inner building --- like a small citadel, three stories high.
  The base of its first tall tower has murder-holes, illuminated by candles inside.
  And next to the murder holes in the tower, a door to the small citadel.
\end{boxtext}

\Gls{running} through the courtyard results in three archers taking aim at the \glspl{pc} from the entrance towers (\gls{area}~\ref{redTower}) and the inner tower (\gls{area}~\ref{redMechanism}).

\mapentry[redKitchen]{Kitchen}

The dwindling food supplies are kept here.  They build up to monstrous amounts, then get hurriedly eaten within a day or two.  Barrels of meats, stacks of bread, and multiple bottles of wine -- nothing lasts long.

\mapentry[redServants]{Servants' Quarters}

This place holds sleeping-cots, chests, and washing equipment.
At present only six members of staff remain -- two cooks, two butlers, one \gls{seneschal}, and Tollfen the tax collector.

\mapentry[redSmolYard]{Small Courtyard}

\begin{boxtext}
  On the right, a thin, thatched roof covers a stables.
  On the left, the main entrance to the keep, with a raised portcullis and side-tower.

  \bigLine
  \smallskip

  Stepping forward you see a small door beyond the stable, and another door behind your right shoulder.
\end{boxtext}

\setcounter{enumi}{\value{list}}
\begin{list}{\Alph{enumii}.\space}{\usecounter{enumii}}
  \item\label{redToilet}
  This toilet has a run-off to the \gls{redfall} river.
  Characters with \pgls{weight} of 15 or less can squeeze through.
  \item\label{redStable}
  The stable hosts Janus, who reacts violently to strangers (\roll{Charisma}{Empathy} at \tn[10] to calm him).
  \item\label{redChild}
  \Gls{hungrywarden}'s youngest son Bairnpelt is only a toddler.
  He doesn't understand his condition, and has no self control.
  This makes him dangerous, so the family have decided to lock him in this little room.
\end{list}

\morphhorse[\npc{\R\A}{Janus, the Demonic Horse}]

\Person{\NPC{\R\Hu\M}{Bairnpelt -- ``the Toddler''}{Playful}{Fingers in mouth}{Milk}}%
  {{3}{-1}{2}}% BODY
  {{-4}{-4}{-3}}% MIND
  {%
    \set{Athletics}{1}
    \quarterstaff
  }% SKILLS
  {}% KNACKS
  {(\glsentrytext{hungrywarden} gave him a stick to `play' with the guards), \lootGoblin}% EQUIPMENT
  {}% ABILITIES


\boxPair[t]{
  \smolMapPic{Dyson_Logos/redfall_top}{
    \Large\rotatebox{-90}{\nameref{redArchers}}/07/38,
    \ref{redArchers}/175/20,
    \Large\rotatebox{-45}{\nameref{redGuards}}/67/44,
    \ref{redGuards}/74/20,
    \Large\nameref{redSeneschal}/42/80,
    \ref{redSeneschal}/40/71,
  }
}{
  \smolMapPic{Dyson_Logos/redfall_top}{
    \Large\rotatebox{-90}{\nameref{redFamily}}/07/38,
    \ref{redFamily}/175/20,
    \Large\rotatebox{-45}{\nameref{redStorage}}/67/44,
    \ref{redStorage}/74/20,
  }
}

\null
\mapentry[redMechanism]{Mechanism}

\begin{boxtext}
  A wooden wheel on the wall has chain wrapped around  it, which stretches up to a hole in the ceiling.
  Sunlight rays enter through the murder holes.
\end{boxtext}

A guard remains here on \gls{hungrywarden}'s orders, ready to release the mechanism, which drops the portcullis.

The second \gls{pc} entering should dodge with \roll{Speed}{Vigilance} (\tn[8]) or take \dmg{0}~Damage.

\humansoldier[\npc{\glsentrysymbol{paik}\M\Hu}{\composeHumanName, Loyal \Glsfmttext{sunGuard}}]

\paragraph{Lifting the gate}
needs \roll{Strength}{Athletics} (\tn[10]), and the bars are slim enough that anyone with a \gls{weight} of 15 or less can just about squeeze through.

\mapentry[redHall]{Great Hall}

\begin{boxtext}
  Past the grand wooden, doors, a bonfire sits in a great, bronze dish.
  Eight \glspl{step} beyond it, a massive table with a half-eaten \gls{woodspy} on top of three layers of plates and bones.
  At the head of the table, sits \gls{hungrywarden}, in a meat-stained dressing gown, screaming a maid to work faster as she tries to fit him into his enormous chainmail.
\end{boxtext}

\setcounter{enumi}{\value{list}}
\begin{list}{\Alph{enumii}.\space}{\usecounter{enumii}}
  \item\label{redFire}
  The bronze fire dish.
  \item\label{redTable}
  The feasting table.
  \item\label{redCloset}
  Cupboard with armour and wine.
\end{list}

\hungrywarden

\mapentry[redGuards]{\Glsfmttext{sunGuard} Chambers}

\begin{boxtext}
  This bed chamber has straw, a barrel in one corner, two longswords, five \glspl{bow} and arrows in another, and one spare white uniform.
\end{boxtext}

The barrel contains freshly boiled milk.
The straw beds have two little bags with \lootSmall, and \lootSmall.

\mapentry[redSeneschal]{\Glsfmttext{redseneschal}'s Room}

Debts, expenses, promises to neighbouring \glspl{village}, and late-payments on monies owed to \gls{townmaster} --- this room has it all, and \gls{redfall} has nothing.
\Gls{redseneschal} remains here with his fingers in his ears before rushing off to calm everything down.

\thornSeneschal

\mapentry[redArchers]{More Archers}

Two more archers, stand ready to protect their \glspl{warden}.
The troupe cannot convince them to stop firing while their \glspl{warden} stand nearby (or they risk becoming supper).

\humanarcher[\npc{\T[2]\glsentrysymbol{paik}\Hu}{Archers \composeHumanName\ \& \composeHumanName}]

\mapentry[redStorage]{Old Storage Shelves}

\Gls{hungrywarden} sold most of the arms here to purchase food, so the room now mostly holds pickled fish, wines, salted meats, and vegetables.

A \roll{Wits}{Larceny} roll (\tn[10]) reveals some bags of coinage, cleverly wedged under the stacks of pickled fish.
Removing the coins, without making a sound, requires a \roll{Dexterity}{Larceny} roll (\tn[12]).
Bag 1 has \lootMedium, bag 2 has \lootMedium, and bag 3 has \lootBig.

\mapentry[redFamily]{Family Chambers}

\Gls{hungrywarden} and Carnfin have taken to sleeping in a single room --- a pile of straw and knotted bedding which stinks like sickness.

\ogre[\npc{\R\Hu\F}{Carnfin}]

\end{multicols}
