\segment{Forest}% AREA
{A Field of Geometric Dreams}% NAME
{The troupe find a dozen hibernating \glsfmtplural{crawler} in the snow}% SUMMARY
\label{spiderDreams}

This \gls{segment} only works during \gls{cTwo}, when \gls{snow} covers \gls{fenestra}, and all the \glspl{crawler} hibernate.
During any other \gls{cycle}, you can ignore this \gls{segment} -- it will only play out if nobody has dealt with \gls{spiderqueen} before \gls{sable} curses the land with frost.

\begin{boxtext}
	Eight shiny berries in a bush above you glimmer in the snow.
	They look black, but full of moisture.
\end{boxtext}

If the \gls{pc} picks the `berries', they find out those berries are in fact the eyes of \pgls{crawler}.
It will not try to wake the others, but every noise anyone makes will wake one more \gls{crawler}.

\paragraph{If the \glspl{pc} stay silent,}
this counts as holding their breath.%
\exRef{core}{Core Rules}{holdingBreath}

\paragraph{If they try to kill all the \glspl{crawler}}
then ask them about their plans very carefully.
The \glspl{crawler} hibernate while packed in tight next to each other -- they can move out gently, without waking the others, but if any feel hurt, it will insinctively spread its legs suddenly, and wake up two more.

\chitincrawler[\npc{\T[3]\A\ifnum\value{Strength}>4\F\else\M\fi}{\Glsfmtplural{crawler}}\addtocounter{weight}{2}]

\chitincrawler[\npc{\T[3]\A\ifnum\value{Strength}>4\F\else\M\fi}{\Glsfmtplural{crawler}}\addtocounter{weight}{2}]

If they manage to harvest all the \glspl{crawler}'s parts, this could prove very lucrative indeed.
But then again, if they ask anyone for help, they will want a cut of the profits.

\paragraph{If the \glspl{pc} wait for \gls{spiderqueen},}
then they will have to wait until the \gls{storm} heralds \gls{cThree}, but she will come for her pets, and will not be expecting \pgls{ambush}, so long as they do not look damaged from afar.

\paragraph{The next \gls{segment}}
cannot begin until \gls{cTwo} ends.
