\sidequest[Forest]{Forest Interruptions}
\label{interruptions}

\sqpart{Forest}% AREA
{The Curious Crawler}% NAME
{A hungry \glsentrytext{crawler} digs at a gnomes stump}% SUMMARY
\index{Gnomes!Rescue}

\Pgls{crawler} pulls up the earth beside a tree, as if trying to dig under it.
Shrewd characters might spot that under the tree a little gnome lives.
The side of the tree opens, revealing a narrow staircase.
The \gls{crawler} has smelled the gnome cooking food, and has decided to stay up top and dig until he catches the little creature.

\begin{boxtext}
  A distant shuffling past some trees starts, then stops, then starts then stops.
  In the far distance, you see the dim silhouette of \pgls{crawler} scratching around the base of a tree, as if trying to dig something up.
\end{boxtext}

\roll{Wits}{Survival} (\tn[9]) to understand that the tree leads to an underground home.

\chitincrawler

\keras

\paragraph{If rescued,}
\gls{keras} is delighted, and gifts the characters a scroll which -- once read aloud -- will cast an illusion of \pgls{crawler}.
It was studying \glspl{crawler} for his spells that got him into this mess.

\sqpart{Forest}% AREA
{Random Traders}% NAME
{Three tradesmen are lost in the forest}% SUMMARY

Sunkborn, carrying flowers, and over a hundred eggs, started the day late, and knew that his cargo would be bad before reaching \gls{town}, so he convinced Dogwilt (carrying uncured meats) and Offcuts (carting blood sausage) to go with him via an old road his grandfather told him about.
However, the road is overgrown, so the traders are now stuck in the woods, and lost.

\begin{boxtext}
  In the distance, you see a group of three men trying to get their first wagon out of a muddy ditch.
  Two more wagons sit behind.
\end{boxtext}

\humantrader[\npc{\M\Hu}{Sunkborn}]

\humantrader[\npc{\T[2]\M\Hu}{Dogwilt and Offcuts}]

\sqpart{Forest}% AREA
{The Elven Party}% NAME
{Elves tell the troupe to dance, and dance, and dance}% SUMMARY
\index{Elves!Party}

Elves have better eyesight than most, so many of their feasts take place in the darkness, and involve games of hide and seek, or enchantment.

\begin{boxtext}
  Off-kilter music and half rhyming words, wander out from the forest, then gentle footsteps to the far right, and more in the distant left.

  The scent of fresh fruit, salads and salmon hit you.  There's a low-burning fire in the distance, looking enticing.
\end{boxtext}

The elves hear the characters, and quickly hide as a game.  Those at the farthest reaches of the gathering shout out that the game is on, and everyone between hides quickly.

\begin{boxtext}
  The noise of little feet darts around the silent forest, but nobody responds.
  A feast lies on the blanket.
\end{boxtext}

\paragraph{If a random encounter occurs,}
Erend\"e deals with it, using her spells.

\paragraph{If the characters eat the food, nothing bad happens.}
It tastes great.
The game doesn't end until the characters settle down to eat or they find an elf.

The characters can roll \roll{Wits}{Vigilance} (\tn[8]) to see how quickly they find an elf, but there are two dozen, so it's only a matter of time before they see one.

Once the game is up, all the elves come out of hiding and laugh.
They dance, and sing, and feast.
However, the elves get a little too carried away, and eventually enchant the party to continue dancing all night.

\elf[\NPC{\F\El}{Aiw\"{e}}{massive grin, pixie-hair}{looks upwards}{to help}]

Aiw\"{e} loves a laugh but never learnt when she's gone too far, and will fashion leaf-crowns for dancing characters, adorning them while they dance.

\elvenenchanter[\NPC{\F\El}{Erend\"e}{Curt mannerisms and fierce eyebrows}{raises Eyebrow}{to understand people}]

\showStdSpells

\elf[\NPC{\M\El}{Taurestel}{Long, perfectly black hair}{``For example\ldots''}{To teach people}]

\paragraph{If the \glspl{pc} ever ask about \gls{lostcity},}
the elves say all the legends are lies.

\paragraph{If the \glspl{pc} ever ask about \gls{spiderqueen},}
Taurestel can teach them her favourite song -- a short piece about a flower opening for the first time, half sung, half hummed.
If she ever hears the song, she will stop for \pgls{round}, stunned, and ask how the character ever learnt it.
However, she will ask in Elvish, and will continue attacking if any of her children were harmed.

Learning this song requires a roll of \roll{Intelligence}{Performance} (\tn[10]).

\paragraph{Once the party is in full swing,}
ask for a \roll{Wits}{Academics} roll (\tn[12]).
Each time the party fail, they dance for another \gls{interval} and lose 3~\glspl{ep}.
They dance until they pass out or until someone succeeds in the roll.

\sqpart{Forest}% AREA
{Furry Traders}% NAME
{Three gnolls are here to trade}% SUMMARY
\index{Gnolls!Traders}

The gnolls have caught four deer in a trap, eaten one, and cured the meat from the other three.
They are willing to trade, but don't want coinage.

In total, the gnolls have five days' worth of food, and three spears to spare.

\begin{boxtext}
  In the distance, hunched humanoids carrying spears and heavy loads on their backs stop suddenly.
  They eye you up, then come forward, with ears pricked up high.
  It's a group of gnolls, carrying large sacks.
\end{boxtext}

\gnollhunter[\npc{\T[3]\F\Nl}{Thash, Gozd, and The\'n}]

\gnollhunter[\npc{\T[3]\M\Nl}{Ksho, Gent, and Ga}]
