\thread[town]{Background Noise}
\label{randommeetings}

\segment{town}% AREA
{Pickpocketed}% NAME
{Someone has stolen one of the characters' items}% SUMMARY

\begin{boxtext}
  You feel the side of your leg and suddenly your heart stops.
  You wonder where is\ldots \textit{which item is the last one written on your character sheet?}
\end{boxtext}

The \gls{pc} with the highest Intelligence Bonus makes a \roll{Wits}{Vigilance} roll (\tn[9]).
Failure indicates a thief has stolen the last item on the player's character sheet, and successfully fled.

It might be possible to track the thief down with enough time, but it takes a lot of time.%
\exRef{core}{Core Rules}{verify_rumours}

\null

\humanthief[\NPC{\M\Hu}{Fenslick}{pudgy cheeks}{picks nose}{a stiff drink}]

Fenslick, a local pickpocket, has no excuse except for his young age, and bad luck in life, though he's 25 and was recently kicked out of \pgls{wheatGuild} apprenticeship as \pgls{tender} for drinking too heavily on the job.

If the \glspl{pc} decide to turn him in, he won't struggle.
Once the \glspl{pc} reach \nameref{stationDungeon} (\vpageref{stationDungeon}), the \glspl{sunGuard} put him in a cell, schedule his trial for $1D6$ days ahead, then tell the \glspl{pc} they can watch the trial for free, as a reward for turning him in.

\segment[\gls{night}]{town}% AREA
{Noctivagation}% NAME
{The \glsfmtplural{sunGuard} arrest anyone out at night}% SUMMARY
\index{Nocvivagation}

\begin{exampletext}
  \Gls{townmaster} has decided that `\gls{town} has too many shady folk out at night', so he has made a new law against `Noctivagation', which is the crime of loitering suspiciously at night.
\end{exampletext}

Ten bands of $1D6$ \glspl{sunGuard} roam around \gls{town} from now on, hunting anyone who looks suspicious, especially any \glspl{diggers}.
If a group of \glspl{sunGuard} sees \pgls{torch} wandering the streets at night, they wave their \gls{torch} left-right, then up-down, then left-right.
If the distant \gls{torch} responds with the same signal, they assume that other \glspl{sunGuard} hold it (it's hard to see those details at a distance).

If the \glspl{sunGuard} see anyone up-close, they ask them their business.
\Glspl{pc} can make a \roll{Charisma}{Empathy} roll at \tn[9] to avoid paying a fine of 30~\glspl{cp}.

Every night, from now on, moving around at night requires a \roll{Wits}{Stealth} roll at \tn[9].

\segment{town}% AREA
{The Fat, Black Cat}% NAME
{He simply wants some fish}% SUMMARY

An inhuman scream rings out in the middle of the street.
When the \glspl{pc} look about, they find the source was a fat, black cat looking at them intently.

If they move away, he follows (for at least \pgls{interval}), and if they move towards him, he run away, but looks back to check they're following him.

\paragraph{If the troupe follow,}
they end up at the local fishmongers.
The cat then stands beside the stall and yells at them.
If he gets fish, he simply leaves for the \gls{paperGuild}.

\cat[\npc{\A\M}{Cat}]

\segment{town}% AREA
{Pickpocketed Again!}% NAME
{Someone else picks a character's pocket}% SUMMARY

\begin{boxtext}
  You feel your trouser leg, and suddenly think ``Oh, not again!''.  \textit{What's the last item written on your character sheet?}
\end{boxtext}

The player with the highest Academics \gls{skill} rolls \roll{Wits}{Vigilance}, \tn[8].
This time it's a young woman, down on her luck as her family farm was consumed entirely by \glspl{crawler}.
The rest have died, and she's now alone.

\paragraph{If caught,}
Gabile apologizes profusely, and explains her situation.

\humanthief[\NPC{\F\Hu}{Gabile}{beady eyes}{messes up her hair}{to join a guild}]

