\mapPic{b}{extracted/bandit_camp}{
  \large\Glsfmtname{whiteBandits}/20/82,
  \glssymbol{paik}/27/63,
  \rotatebox{20}{\normalsize White River}/47/51,
}
\section{\Glsfmtname{whiteBandits}}
\label{banditLair}

\renewcommand\csComments{
  \randomize%
  \callout[9]{14,11}{-.3,-2}{Watch Point}{$\dicef{6} + 2$}
  \callout[10]{15.5,7}{-2.5,-1}{Beds,}{beers, and outhouse \dicef{12}}
  \callout[9]{12.8,2.5}{-2,1.3}{Horse Supplies}{70 days worth of meal}
  \callout[8]{10,0.3}{0,0.5}{Stables}{with \dicef{12} horses}
  \callout[8]{6.5,1.6}{.7,1.4}{Large Gate}{$\dicef{6}-2$}
  \callout{3.8,2.5}{1.3,2.5}{Watch Point}{$\dicef{6}-2$}
  \callout[7]{1.5,2}{0.8,4}{Archers}{play cards through the night $\dicef{6} + 2$}
  \callout[7]{0,4.5}{1.3,2.3}{Supplies \& Beds}{$3\times$ shortsword, \arabic{r12}00~\glspl{cp}.  $\dicef{6} + 2$}
  \callout[5]{0,9.5}{0.2,-1.7}{False Welcome}{}
  \callout[8]{5.7,11.3}{0.3,-1.5}{\Glsentrytext{banditking}'s Room}{\arabic{r12}0~\glspl{sp}}
  \callout[7]{2,11}{2,-1.3}{Workshop}{$\dicef{3} -1$ \glspl{ingredient} of each type}
  \callout[10]{9,12}{-0,-5}{Weapons}{shortsword $\times 21$, longbow $\times 31$, round shield $\times 2$, rations $\times 200$}
  \callout{11,10.5}{-0.3,-0.6}{Gate}{murder holes $\dicef{6}-2$}
}

\begin{multicols}{2}
\histEvent{5}{4}{\Glsfmttext{banditking} begins building a secret \glsfmttext{village}}

\begin{exampletext}
  \noindent
  \Gls{banditking} heard about these interesting hills from \gls{sewerthief} last \gls{cycle}, and immediately began making connections with the nearby \glspl{village}.
  The area lets out almost no light throughout the night, even with a raging fire in the middle.
  The surrounding mountains provides an early dusk, which helps keeps the covert \gls{village} cool, and keep supplies fresh.
\end{exampletext}

When the weather clears, neighbouring \glspl{village} can see the light plumes of smoke from the \nameref{banditLair}.
They gossip about it on occasion, but won't mention it to outsiders -- they suspect the money's coming from some `tax-dodging new \gls{village}', and don't mind so long as they keep buying all the food for a good price.

As \gls{banditking} returns, he stores the wagons a mile from the outpost, then takes the horses the last bit of the journey, after covering the wagons in forest leaves.

Each area in the outpost has varying numbers of bandits -- roll the dice stated next to the area to see how many.

The \glspl{whiteBandits} have a week's worth of food.
Interfering with the supply line will result in vicious raids on \glspl{village} within walking distance (20~miles), which will push \gls{townmaster} to send his \gls{sunGuard} out to find and destroy the area within a month.

\widePic[t]{Dyson_Logos/bandit_camp}

Determine the current state of the outpost by rolling two dice, and using both results:

\begin{dlist}
  \item
  \Gls{banditking} returns from \gls{town} with $2D6$ bandits.
  He has money from \gls{sewerking}.
  \item
  Bandits drink -- each has a -1~Penalty.
  \item
  Bandits have begun to fight.
  If \gls{banditking} is present, he breaks it up; otherwise one of them inflicts $1D6$ Damage, and the other limps away to drink.
  \item
  The bandits entice \pgls{monster} to enter at the Western entrance (`False Welcome'), then release their arrows.
  Once dead, they pull the \gls{monster} apart, and eat it.
  \item
  Training time!
  All bandits must get their \glspl{bow}.
  \item
  \Gls{banditking} sneaks out with $1D3$ bags of 10~\glspl{gp}, to bury them in the forest (he doesn't trust the others).
\end{dlist}

\end{multicols}

\Needspace{12\baselineskip}
\begin{multicols}{2}

\vspace{2em}
\humansoldier[\npc{\M\T[2]\Hu}{Supplies Thief}]

\humanarcher[\npc{\F\T[2]\Hu}{Practising Archer}]

\end{multicols}

\needspace{14\baselineskip}
\begin{multicols}{2}

\humanfarmer[\npc{\F\T[2]\Hu}{Singing Drunk}]

\humanfarmer[\npc{\M\T[2]\Hu}{Pro Gambler}]

\end{multicols}

\needspace{14\baselineskip}
\begin{multicols}{2}

\humanthief[\npc{\M\T[2]\Hu}{Card Player}]

\humanthief[\npc{\F\T[2]\Hu}{Sword Sharpener}]

\end{multicols}

\Needspace{12\baselineskip}
\begin{multicols}{2}

\humanthief[\npc{\M\T[2]\Hu}{Paranoid Nutcase}]

\humanfarmer[\npc{\M\T[2]\Hu}{Horse Minder}]

\end{multicols}
