\subsection[the Old Alchemy Basement]{\glssymbol{yonder}~The Old Alchemy Basement~\glssymbol{yonder}}
\label{old_alchemy_basement}

\histEvent{270}{2}{%
  The alchemist, Inkparch, attacks those in \glsentrytext{archwarp}'s alchemical gate, passes into undeath, then seals the alchemical library's basement door, and remains sealed and alone to the present%
}

\begin{exampletext}
  \noindent
  Like all advanced alchemists, Inkparch felt he was better than normal people, which was true in regard to alchemy, and false in regard to social skills.
  One particularly heated argument with the Dean of Forces escalated into a tantrum, then a fight, and eventually a battle.%
  \footnote{The Dean of Forces felt there was one magical gateway between \glsentrytext{archwarp} and \glsentrytext{sixshadow}, while Inkparch counted two gateways -- one in \glsentrytext{archwarp}, and the other in \glsentrytext{sixshadow}.}

  As his argument with the Dean became continuously more bitter, the two began an alchemical `jostling', which prompted the guards to come and break the situation apart.
  This escalated the situation even further, until Inkparch found himself engaged in a battle with the entire alchemical basement.

  At this point, Inkparch began a classic necromantic trick -- he cast \textit{Soul Specks}, so he could hold his breath, then twisted the air into a foetid smog, making everyone in the area choke.
  Finally, a Force \gls{spell} sealed the mundane exit.

  This plan went excellently, until one of the guards stabbed Inkparch in the tonsils before his permanent death.
  Inkparch also died, but his necromantic \gls{spell} ensured his soul remained fixed in place, and he could continue moving as \pgls{ghast}, or perhaps `lich' (the only difference being alchemical knowledge).

  The first escape plan was to approach the alchemical gateway, and speak the words to open it -- `open to trade!'; this didn't work, due to his shattered larynx.
  The second plan was to cast \textit{Soul Specks} on the Dean of Forces, ensuring his survival, and have him speak the words to open the gateway; but of course the Dean said he would rather pass into undeath and sit there for a century than help Inkparch with anything.
  The third plan was to raise the corpses in the basement as \glspl{ghoul}, and try to tell the \glspl{ghoul} (in the silent language of the undead) how to speak the words `open to trade'.

  In a fuming (and inexpressible) rage, Inkparch decided to trap the gateway, so he could kill anyone coming to end him.
  With chains pulled from the laboratory, he bound the undead to the pillars in front of the alchemical gateway, so that once someone entered, the \glspl{ghoul} would pull against the chains, which would pull apart the pillars, and the ceiling would come crashing down.

  This plan has yet to fail, but the gateway has not opened in the centuries since the incident, and he has no idea why.
  And over those centuries, after someone barred the door from the \emph{outside}, flood-water slowly filled the basement.

  The \glspl{ghoul} here still make noises with what remains of their larynx, but not a single one has managed to properly utter the required sentence.
  As a result, the undead within the basement still chant the opening words of the gateway, but they can never get it right.
  Still they chant\ldots

  `\textbf{Opena trei\ldots opena trei\ldots}'
\end{exampletext}

The entire basement of the old alchemical laboratory is sodden with water, resting knee-height to a human.

\begin{boxtext}
  Looking down stairs, you see a hallway built for gnomes, lined with pillars, and with a black floor, then you correct yourself.
  Black water sits along the entire hallway, which looks like a floor.

  In the far darkness, you can just about see great double doors along the hall, to the right, before the rest of the hall goes black.
\end{boxtext}

\mapPic{b}{Dyson_Logos/under_lost_city}{
  \Large \ref{deanRoom}/18/37,
  \Large \ref{deadIllusionist}/42/37,
  \Large \ref{officeEntrance}/30/18,
  \huge S/36/18,
  \huge\rotatebox{90}{S}/75/71,
  \huge S/66/86,
  \ref{alchemyHall}/18/84,
  \nameref{alchemyHall}/18/93,
  \rotatebox{45}{\nameref{alchemyEquipment}}/14/61,
  \ref{alchemyEquipment}/20/59,
  \rotatebox{25}{\nameref{alchemyLibrary}}/46/76,
  \ref{alchemyLibrary}/52/72,
  \rotatebox{45}{\nameref{alchemyRooms}}/29/41,
  \ref{alchemyRooms}/31/37,
  \rotatebox{-45}{\nameref{alchemyGift}}/76/88,
  \ref{alchemyGift}/71/83,
  \rotatebox{45}{\nameref{alchemySecret}}/66/31,
  \ref{alchemySecret}/60/39,
  \rotatebox{-90}{\nameref{summoningRoom}}/93/58,
  \ref{summoningRoom}/83/58,
}

\paragraph{Wading through the water}
is difficult.
All movement rates are halved.

\paragraph{Darkness}
means someone must carry \pgls{torch} for the group to see, and any \glspl{torch} dropped in the water instantly extinguish.

\paragraph{The cold water and foetid air}
each inflict \pgls{ep} each \gls{interval}.
Allowing the barrow to air out for \pgls{interval} means it only inflicts 1 \gls{ep} per \gls{interval}.

\paragraph{All doors}
have swollen due to the many \glspl{cycle} of water-logging.
Opening them requires a \roll{Strength}{Crafts} roll (\tn[10]).
As usual, each roll remains as-is, so if someone fails to open a door they will need to find a way to gather more strength, or better tools, or simply give up opening that door.

\paragraph{Narrow hallways}
make wielding long weapons challenging.%
\exRef{core}{Core Rules}{enclosedcombat}

\paragraph{The Dead Chant} when not in combat.
If they stand at the other end of a hallway, they chant.
If the characters lock them in a room, the dead stand outside and chant while clawing at the door.

\paragraph{Cave-ins} present a real danger here.  If the ceiling ever collapses while the characters are inside, the falling rocks from above at first deals $1D6-2$ Damage to everyone in the room, then $1D6-1$, and so on, increasing by 1 each \gls{round}, until everyone exits or dies.

\subsubsection*{Cold Seasons}

If the \glspl{pc} arrive during \gls{cTwo}, you might expect freezing waters.
However, when the initial \glspl{guard} entered, Inkparch killed them with \gls{spell} of foetid-air and confusion, and used the energy from their souls to unfreeze the water in the area (he doesn't like everyone being confined).
This left him with less energy, which he did not want to spend on raising them.
Therefore, you should remove those undead.

\mapentry[alchemyHall]{Dead in the Water}

The dozen \glspl{ghoul} in the hallway had nothing better to do than fall over and lie in the water.
The high peat concentrations have preserved their bodies very well, though it does make them very stiff.

This creates an unplanned (but deadly) ambush, as anyone moving inside simply feels an `uneven' floor as they trample over the \glspl{ghoul}.
This wakes them up, and then the dead will stand up \emph{between} the characters.

Six \glspl{ghoul} rest at the start of the hallway, and another nine soon after.
A further five at the other end of the hallway begin walking towards them immediately.

\paragraph{If the party attempt to fell any pillars,}
have them roll \roll{Strength}{Crafts} (\tn[13], +2 Bonus for using ropes).
Once the pillars fall, the entire area collapses within two rounds.

\paragraph{If anyone searches the bodies,}
they find eight of the \glspl{ghoul} which were once \glspl{guard}.

\bookInvestigationChart[b]

\ghoul[\npc{\T[6]\D}{\arabic{noAppearing} \gls{guard} \Glsfmtplural{ghoul}}]

\ghoul[\npc{\T[9]\D}{\arabic{noAppearing} Ancient \Glsfmtplural{ghoul}}]

\mapentry[alchemyEquipment]{Study Supplies}

\begin{boxtext}
  The shelves in this wide room are full of smashed and broken equipment, but it looks generally alchemical.
  Brass beakers, glass beakers, jars with rotten \gls{digger} infants suspended in unknown fluids, pots with mould leaching out, and alcohol-burners, litter the shelves.
\end{boxtext}

\index[mana]{Fate!Rubies}
Almost all of the \glspl{ingredient} which alchemists rely on have gone rotten over the centuries.
However, two pouches of red ruby dust remain, which function as Fire \glspl{boon}.
\index[mana]{Fire!Ruby dust}

\paragraph{Characters who scour the room delicately,}
can find valuable remains with a \roll{Dexterity}{Academics} roll.
They gain all items below the \gls{tn}.
On a draw, something slips from their hand, and into the much, so the player will know they can find the item if they somehow raise their result (perhaps with \pgls{restingaction}, over the course of \pgls{interval}).

{\small
  \begin{boxtable}
    \textbf{Roll} & \textbf{Result} \\
    \hline
        9         &   \lootMedium\ in a rotten, leather bag. \\
        10        &   \lootBig\ worth of green topaz lying in the water. \\
        11        &   Ruby-dust leather pouch (Fire \gls{boon}). \\
        12        &   Ruby-dust leather pouch (Fire \gls{boon}). \\
        13        &   \lootJewellery, stashed in a waterlogged book. \\
  \end{boxtable}
}

\boxPair{
  \inkparch
}{
  \deanOfForces
}

\mapentry[alchemyLibrary]{Library}
\index{Library!Ancient}

The books here have mostly become water-logged, and fallen to mould.
However, some highly-valuable books remain with ink still on the page.
If handled roughly, the books will degrade to mulch.

Characters can roll \roll{Dexterity}{Academics} to rescue books.
Compare the results to the table \vpageref{libraryTable} -- they obtain \emph{one} book below the \glsentrylong{tn}, while a tie indicates that they have identified the book before accidentally manhandling it to destruction.

Looking over these books requires \pgls{interval}, and each of the players should decide if they want to roll a check themselves (so the group can recover more valuables faster) or if they want their character to search with another \gls{pc}, to perform \pgls{bandAct}.

In addition to the other books, a book lying open details the Doom Study spell.

\doomStudySpell

\mapentry[alchemyRooms]{Dark Pit}

\begin{boxtext}
  These doors swing open effortlessly, showing a new room with three more doors; right, left and centre.
  Before you can take another step, the narrow double-doors to the right burst open, and a dead man, with black cavities for eyes, and a beard falling to dust, steps out\ldots%
  \footnote{While Inkparch rampaged, the Dean of Forces locked himself in his room, but this did not save him from joining Inkparch in undeath.}
  he points emphatically at the water.
\end{boxtext}

Inkparch remains where he began -- at the bottom of the stairs, now wholly covered in water.%
\footnote{Neither wants to move, as all movement drains the \gls{undead} of a little of their remaining energy, so they have spent the last couple of centuries communicating bitterly in the ethereal language of untethered souls, and occasionally playing chess against each other by memorizing a theoretical board.}
The \glspl{pc} will almost certainly fail to notice the drop, and so Inkparch intends to wait for them, and drag down the first foot he perceives.
\emph{However}, the Dean of Forces has a hate-fuelled plan he's held onto for some time.

\paragraph{The second any character enters,}
the undead Dean exits room~\ref{deanRoom} to warn them of the danger in the water.%
\footnote{The Dean can see the characters' lights through cracks in his bedroom's door.}

\paragraph{If anyone steps into the water,}
they can roll \roll{Dexterity}{Caving} (\tn[12]), or slip down the sudden-stairs, which allows Inkparch a \gls{vitalShot} against the character, which he uses to grab.%
\exRef{core}{Core Rules}{grab}
After that, if the character falls below 0~\glspl{ap}, they reflexively breathe in the foetid water, gaining 3~\glspl{ep}.

%!
\null
\setcounter{enumi}{\value{list}}
\begin{list}{Room\space\Alph{enumii}.\space}{\usecounter{enumii}}
  \item
  still houses the undead Dean of Force.
  \label{deanRoom}
  \item
  houses nothing but broken furniture, sludge, and the remains of the Dean of Illusion who drank poison to avoid Inkparch's wrath.
  The bottle still rests in his left hand, and in his right, a bribe for \gls{abderian} -- \lootBig.
  Characters passing an \roll{Intelligence}{Academics} roll (\tn[13]) will understand his position from the insignia on his tattered gown.
  \label{deadIllusionist}
  \item
  once provided a miniature lobby before the \nameref{alchemySecret} in room \ref{alchemySecret}.
  The Dean of Illusion's disgusting eating habits made the place so rotten and mouldy that others complained, so he covered the mess with an illusion \gls{spell}.
  \label{officeEntrance}
  \begin{boxtext}
    The heavy door creaks open to a well-kept room, like an expensive upstairs booth in a tavern, complete with a couch, a desk, and a freshly cooked breakfast on the table.
  \end{boxtext}
\end{list}

\paragraph{If Inkparch receives Damage,}
he beats \pgls{retreat} to the bottom of his dank pool.

\paragraph{If nobody in the troupe attack the Dean,}
he remains motionless, then finally lowers his head, in a silent request to finally die.

\paragraph{If \pgls{pc} brushes the illusion \gls{spell} out of room \ref{officeEntrance},}
they will see the door upstairs immediately.

\mapentry[alchemySecret]{Little Study}

\begin{boxtext}
  The stairs reach up, and finally you step your muddy boots out of the water and along a cold, but dry corridor.
  The room contains tables with super-annuated scrolls, dust, and a series of very out-of-date books on alchemical theory.
  Another passage leads out.
\end{boxtext}

\paragraph{Searching the paperwork}
uncovers a note complaining that the alchemical gateway's `open to trade password' seems too simple, and should be some word in ancient Dwarvish, without any vowels.
The \glspl{pc} may read this as `the password which allows the gate to open for trade', rather than the actual meaning -- that the password is literally `open to trade'.

The shelves also contain a strange and well preserverd book called \emph{An Account of the Fingers} (see \autoref{bookOfFingers}).
\index{Books!Fingers}
\label{fingers:basement}

\paragraph{Resting here}
inflicts no \glspl{ep}, as the place is not full of cold water or foetid air (tell the players they can breathe better -- they may guess that some passage outside is here).

A \roll{Wits}{Crafts} check, \tn[10], reveals a loose wooden board in the ceiling.
It used to be an exit to the ground floor of the town above, \vpageref{basementTrapdoor}, but now the upper floor is just the ground outside\ldots after a lot of digging upwards.

\boxPair[t]{
  \ghoul[\npc{\T[8]\D}{\arabic{noAppearing} Ancient \Glsfmtplural{ghoul}}]
}{
  \ghoul[\npc{\T[8]\D}{\arabic{noAppearing} Ancient \Glsfmtplural{ghoul}}]
}

\mapentry[alchemyGift]{Giftschrank}

\begin{boxtext}
  The bricks fall away easily, revealing a full new room.
  Two skeletons rest on a table, each clutching a book.%
  \footnote{The skeletons on the table have aged worse than the other corpses, as they were never preserved in the peat-water.
  They died of hunger rather than facing the dead they knew to be outside.}
\end{boxtext}

One holds a book of poetry, and the other holds a book of Mind \gls{spell}, which she never managed to understand before dying.
The book on Mind \glspl{spell} has plentiful, practical material.
It is worth 6~\glspl{gp}, while the book of poems is worth~4~\glspl{sp}.

\paragraph{Spotting the hidden door from the outside}
requires a \roll{Wits}{Crafts} (\tn[12]).

\medbreak

\mapentry[summoningRoom]{Gateway}

\begin{boxtext}
  The massive double doors slowly swing inwards, and the torchlight reveals a flooded hallway of six stone pillars, two enclaves (on the left and right), and a stairway ahead leading up to a stage.
  The stage shows a grand stone arch, like a doorway, leading nowhere but the darkness behind it.
\end{boxtext}

The magical gateway can sense any living soul, and can cast a Force spell to detect that one phrase -- `\textit{open to trade}'.

\paragraph{If any of the players say the opening words out loud,}
then so do their characters; the \glspl{ghoul} in the room begin chanting along with them in unison,%
\footnote{As usual, speech costs 1~\gls{ap}, so the \glspl{pc} should enjoy the unexpected and rare advantage they receive from \glspl{ghoul} spending \pgls{ap} on attempting to talk.}
and gateway opens.
Two things can happen here:

\paragraph{During \gls{cTwo}}
the other side has a flat wall of ice.
\paragraph{At all other times}
the gateway opens to a room of water, which floods in, along with a massive acidic ooze-creature.%
\footnote{This massive ooze was minding its own business \vpageref{shadowJelly}, room \ref{shadowJelly}.}
Everyone rolls \roll{Speed}{Athletics} to avoid being slammed by the water (and receiving $1D6$ Damage).

\paragraph{Once the ooze enters,}
it begins to devour whatever flesh is closest to it (probably the \glspl{ghoul}, and any \glspl{pc} the \glspl{ghoul} were grappling).

\uncommonlyLargeJelly

\begin{boxtext}
  You look behind, and rusted chains rise from the water --- one side tied to the pillars, and the other to a dozen of the dead.

  The dead begin to chant\ldots

  `\textbf{Opena trei\ldots opena trei\ldots}'
\end{boxtext}

\vspace{-1em}
\begin{list}{\bfseries On round~\arabic{enumi}. }{\usecounter{enumi}}
  \item
  the room remains silent.
  \item
  the \glspl{ghoul} stand up.
  \item
  Inkparch approaches the troupe from behind (assuming nobody killed him).
  \item
  the pillars visibly strain as long as six or more \glspl{ghoul} pull against them.
  \item
  the first pillar collapses if the \glspl{ghoul} have not been felled.
\end{list}

\paragraph{If two pillars collapse}
then the entire room collapses.
Everyone inside receives $1D6-2$ Damage, which increases by 1 each round until everyone has left, or died.

\paragraph{If a group of \glspl{ghoul} grab a character,}
they stop pulling at their chains and focus on feeding, until they have fed (they consume souls instantly, once a target dies).

\paragraph{If anyone enters the gateway,}
they find themselves in a pitch-black room at \gls{shadowGate}, room \vref{shadowGate}.

\end{multicols}

