\section{\Glsfmttext{archwarp}}
\label{lostcity}

\mapPic{b}{extracted/basement}{
  \glsentrysymbol{yonder}/53/70,
}

\begin{multicols}{2}

\mapPic{t}{Dyson_Logos/forgotten_city}{
  \ref{fallen_tower}/32/72,
  \ref{campfire}/29/61,
  \ref{basementTrapdoor}/18/58,
  \ref{lostGriffins}/73/76,
  \ref{shiningLoch}/72/38,
  \ref{lostDoor}/58/24,
}

\histEvent{299}{4}{\Glsfmttext{shadowGate} drives traders between \glsfmttext{sixshadow} and \glsfmttext{archwarp}}
\begin{exampletext}
  \noindent
  Some centuries ago, a town known as \gls{archwarp} rose to prominence and wealth due to the magical gateway created by alchemists.

  Since then, the gateway has closed, the population left, and most of the stone requisitioned for other structures and sent downstream.

  Patches of stone walls, or artistic structures remain to this day, causing all sorts of rumours among the rare rangers who pass through the area.
\end{exampletext}

\begin{boxtext}
  The trees and vines here cling to blocks of stone, as if trying to crush the last remnants of civilization.
  You sometimes wander for so long without seeing a single brick that you forget you're anywhere but a normal forest, but then another errant stone, or the marble hand of a statue juts up not far from the riverbank, to remind you of the ghosts resting in this place.
\end{boxtext}

\begin{exampletext}
  \noindent
  \Pgls{southSeeker} of the \gls{wolfhead} came here in search of the old alchemy library, and found it.
  However, he didn't dare enter the old door to the alchemy basement's library he found, so he hired \glspl{guard} to enter, and check the barrow for safety.
  He planned to have them `split the loot', and then help them sell whatever valuables remained inside, and hoped they didn't see (or didn't understand) the alchemical gateway.
\end{exampletext}

\subsection{Journeying to \Glsfmttext{archwarp}}
If the troupe manage to procure a boat, they might arrive by journeying upriver; otherwise they must walk.

\paragraph{Anyone ferrying them by boat}
will demand at least 5~\glspl{sp} per day, and will not hang around to be attacked (so if a wandering monster happens by, they will leave or die).

\paragraph{During the journey towards \gls{archwarp},}
the troupe will spot \gls{southSeeker} leaving.
He will give them an awkward stare, as he sits in a sail-boat big enough for half a dozen men at least.
He knows that they must be going to investigate something, and he knows that they know he was there.

If the \glspl{pc} don't know him, he will say nothing, wave frostily, and continue to let the currents guide him.
However, if he considers them reasonable acquaintances, he will stop and arrange to get what he wants while giving away as little information as possible.

\southSeeker

\subsection{Campfire Embers}

\boxPair{
  \mouthdigger[\npc{\T[3]\A}{\arabic{noAppearing} \Glsfmtplural{digger}}]
}{
  \jelly
}

\begin{enumerate}
  \item
  This old, fallen tower supports the last roof (made of stone) in all of \gls{archwarp}.
  \Gls{southSeeker}'s bedding remains here.
  \label{fallen_tower}
  \item
  This hidden doorway has so much topsoil grown over it that nobody could imagine it was there.
  However, anyone in the basement below, in room \vref{alchemySecret}, may notice the underside, and dig their way up.
  \label{basementTrapdoor}
  \item
  The campfire shows evidence of a dozen people.
  The \glspl{pc} can roll \roll{Intelligence}{Vigilance} to understand what the debris around the campfire means.
  \begin{nametable}{Campfire Investigation}
  \textbf{Roll} & \textbf{Result} \\
  \hline
    7 & A dozen men were here. \\
    8 & They ate a griffin. \\
    9 & \glspl{guard}. \\
    10 & Only one person left the area. \\
    11 & Someone prepared \gls{griffin} wings to make \pgls{boon} over the camp fire. \\
  \end{nametable}
  \label{campfire}
  \item
  These blossoming fruit trees hold a trap: \glspl{digger}.
  The amount of fruit depends upon the \gls{cycle}.
  \begin{description}
    \item[\Gls{cTwo}]
    means nothing but snow on the trees.
    \item[\Gls{cFive}]
    sees the canopy nearly collapse with food.
    The trees hold six days' worth of fruits (which goes rotten within two days)
    and the \glspl{digger} here have two litters of six sprogs each.%
    \footnote{\Glspl{digger} children can be used as \glspl{ingredient}.}
    \item[Other \glspl{cycle}]
    mean the trees contain four days' worth of food.

  \end{description}
  \label{lostGriffins}
  \item
  This glistening loch holds an acidic ooze.%
  \exRef{judgement}{Judgement}{ooze}
  However, during \gls{cTwo}, the rivers and lochs freeze over, leaving the ooze in silent and pure contemplation.
  \label{shiningLoch}

  \item
  This old basement door lay under the mud for some centuries, but it became a good deal more obvious once \gls{southSeeker} opened it.
  The \glspl{pc} can roll \roll{Wits}{Vigilance} (\tn[8]) to locate it.
  \label{lostDoor}
\end{enumerate}

\subsection{Before the Journey Back}

\begin{exampletext}
  The \glspl{guard} who came with \gls{southSeeker} to investigate the old wooden door already had a mission from their \gls{jotter}, and \gls{investigator} noticed their disappearance instantly.
  He ferreted out a dozen drunken \glspl{fodder} from \gls{town} and told them he'd send them all to \gls{paik}%
  \footnote{\ldots meaning `they would hang'.}
  personally if they failed to come with him and hunt down the deserters.

\end{exampletext}

\investigator

\humanthief[\npc{\T[3]\Hu}{\arabic{noAppearing} \Glspl{fodder}}]

\humansoldier[\npc{\T[3]\Hu}{\arabic{noAppearing} \Glspl{fodder}}]

\Gls{investigator} will arrive \pgls{interval} after the \glspl{pc} arrive, so he may wait at the camp site while they investigate the alchemical basement, or he may wander up behind them, and decide that \emph{the \glspl{pc} are the \gls{guard} deserters}.

\paragraph{If \gls{southSeeker} passed the \glspl{pc} silently on the river,}
he became wary that they might double-back and come after him, so he pulled his boat to the bank, and stayed hidden at the side.
This means that \gls{investigator} did not see \gls{southSeeker}, and if the \glspl{pc} mention him going downriver, he will decide they are all liars, and then inform them of his decision.

