\mapPic{t}{extracted/sixshadow}{
  \glsfmttext{sixshadow}/60/50,
  \large\glsentrysymbol{abderian}\glsentrytext{shadowVault}/85/12,
}

\section[\glsfmttext{shadowVault}]{\Glsfmttext{shadowVault}}
\label{shadowVault}

\begin{multicols}{2}

\histEvent{350}{5}{The Vore Gate opens in \glsentrytext{sixshadow}}

\begin{exampletext}
  \noindent
  \Gls{sixshadow} began as an unremarkable settlement, but with a research outpost for alchemists.
  The small \glspl{village} sustained the alchemists' tower, and the tower let them keep all the dangerous things far away, and over the \gls{sixshadow} mountains.

  Dangerous \glspl{artefact} stayed underground, in `\gls{shadowVault}', and dangerous alchemists stayed in the tower, away from any large populations.

  The greatest and maddest of the alchemists at the time created a long-range spell to detect powerful mana flows, deep underground, and then created a gateway -- a tear in space -- which allowed him to step through, and explore the tunnels of the \gls{deep}, in order to find powerful \glspl{ingredient}.
  Unfortunately, the gateway opened to nothing but dark, rocky, tunnels, and those who explored a little way in never returned.

  As a by-product of the spell, the gateway itself became sentient (meaning it was \pgls{artefact}).
  And like most \glspl{artefact}, it became obsessed with the one task which the alchemist created it to do -- to have people enter through it.
  So the \gls{artefact} gateway would open again, whenever it had the energy, in the hopes of tempting someone inside.
  The alchemists named it, `the Vore Gate'.
\end{exampletext}

\paragraph{If the troupe remain for a long time,}
any \glspl{witch} will find it difficult to regain \pgls{mp} at the end of \pgls{interval}, because that one \gls{mp} goes to whoever has the biggest vacuum.
Once the \glspl{artefact} cast a few spells, everyone who wants \pgls{mp} finds themself in competition with everyone (and everything) else.

\subsection[Downstairs]{\glsentrysymbol{yonder}\quad Downstairs\quad\glsentrysymbol{abderian}}

The air smells of dampness and coagulated mana.
In the darkness, the characters may year \gls{yonder}'s bell ring below.

\mapentry[shadowStairs]{Muddy Steps}

\begin{exampletext}
  Water and mud have slid down the stairs of \gls{shadowVault} for the last couple of centuries.
  Over most of \pgls{cycle}, the temple has deep water.
  However, during the cold seasons, the water freezes over.
\end{exampletext}

Traversing the stairs demands a \roll{Dexterity}{Caving} roll (\tn[8]).
Failure inflicts $1D3$ Damage.

\mapentry[entranceCullis]{Gnome-Crafted Fence}

\histEvent{340}{1}{Six \glsentrytext{deep} gnomes emerge from the Vore Gate}

\begin{exampletext}
  The alchemists build a stone wall around the Vore Gate, with a cast-iron fence, under lock-and-key, to make sure nothing dangerous would come out.
  What actually emerged were half a dozen young gnomes with large, bulbous eyes.

  They stayed in the fenced-off area for days, starving, until the alchemists took them in out of a mixture of pity and curiosity.
  They remained at \gls{shadowVault}, sweeping up, keeping extensive records, and soon learnt to speak the common language which they referred to as `Up'.

  The six gnomes of \gls{sixshadow} had persistent criticism of the metal fence in front of the Vore Gate, and soon created their own from a special steel mix based on charcoal derived from \glsentrytext{digger} infants.
\end{exampletext}

The metal fence looks black in the darkness, but with enough light a subtle blue tint gleams.
Destroying it requires 20 Damage (in a single hit), or someone can try to pick the lock with an \roll{Intelligence}{Larceny} roll at \tn[16].

\shadowVaultMap

\mapentry[shadowVore]{Vore Gate}

\begin{exampletext}
  A young alchemist descended into \gls{shadowVault} to cast inquisitive spells through the Vore Gate.
  However, the moment he unlocked the gate, something assaulted him, removing his fingernails then face before bolting into the night.

  The alchemists concluded that the Vore Gate had let the creature in earlier, but nobody could see it by looking through the gate for danger.
  Since then, the alchemists had two peep-holes commissioned at either side of the Vore Gate's enclosure, so they could check if anything hid within the enclosure before unlocking the gate.
\end{exampletext}

\begin{boxtext}
  Past the ornate gate, you see a room, and in the far darkness, two ivory pillars frame a dark glimmer\ldots of some description.
\end{boxtext}

If the \glspl{pc} manage to speak with the Vore Gate,%
\footnote{Perhaps with a \textit{Delicate Audience} spell.}
it tells them enthusiastically, and emphatically, that they have to see the other side.
It may lie, or entice them with mystery, but most of all it says how much it loves having people entering.

Last night, a \superWierdzi\ emerged from the Vore Gate, and it still wants to escape the enclosure.
The \superWierdzi\ looks like a sickly-yellow mound of Van-Gogh playdough, but whenever someone looks at it, the \superWierdzi\ begins to look a little like them.

The \superWierdzi\ can reduce any Body Attribute by up to 3 in order to imitate someone's appearance, but cannot make any noises.

The acidic oozes will not react to the \superWierdzi\ in any way.

\paragraph{If the troupe look into the Vore Gate enclosure,}
the \superWierdzi\ tries to hide.
If it cannot (because all peep-holes have someone looking through them), it stares back through a peep-hole, absorbing \pgls{pc}'s face.

\paragraph{If it escapes,}
the \superWierdzi\ flees, then stops steps away, and stares at the troupe, imitating each of them in turn.
Ranged weapons will make it flee, and then hide outside, waiting to stare at the troupe again.

\setcounter{statDots}{0}
\mphlg

\paragraph{Letting it observe for 3 rounds}
allows it to duplicate someone's full bodily appearance exactly, at which point it attempts to return through the Vore Gate (but may wander outside for a few \glspl{cycle} if the Vore Gate is not available).

\histEvent{294}{2}{Desperate for more income, the old \glsentrytext{wheatGuild} begin to explore the Fingers, and extract valuable items~\glsentrysymbol{yonder}}

\needspace{3\baselineskip}
\artefact[16]{Vore Gate}% Name
  {Two ivory pillars, with a beckoning empty space between}% Body
  {1}% Intelligence
  {0}% Wits
  {0}% Charisma
  {to feel you inside me}% Mission
  {Fae Door}% Base Spell
  {
    \setcounter{Fire}{3}
    \setcounter{Earth}{2}
    \setcounter{Fate}{1}
    \setcounter{Water}{1}
    \setcounter{Academics}{2}
    \setcounter{Cultivation}{1}
  }% Spheres

\showStdSpells[
  \setcounter{diceNo}{0}
]

\paragraph{Entering the Vote Gate}
is deadly.
See \vpageref{bookOfFingers} for the details.

\mapentry[shadowPot]{Sticky Pot}

\begin{exampletext}
  After one too many expensive accidents, the alchemists decided to shut down \gls{shadowVault}, so the \glspl{server} of the \gls{templeOfPoison} bought the building, and the basement.
  They also inherited all of the \glspl{artefact} which were not considered dangerous, or easy to move.

  Within \pgls{cycle}, \gls{shadowVault} began to see rich visitors, coming just to observe the strange \glspl{artefact}.
  They didn't have any magical defences, so they bought some safety precautions from the alchemists.
\end{exampletext}

Inside, rests a tiny little ooze-creature, under a \textit{Preservation} spell, ensuring it will not age so long as it remains still.
The temple \glspl{server} placed it here `in case of emergency', with a vague plan to arm the establishment's guard in case anything large entered.
At the bottom of the pot rests a pile of 30~\glspl{gp} (clearly visible).

The ooze which inhabits the deeper water \vpageref{shadowJelly} occasionally comes out, and leaves acidic mucus all over the pot, presumably sensing the contents.

\jelly[1]

\mapentry[shadowOaths]{Lady of Oaths}

\begin{exampletext}
  `Wouldn't it be great if people could just keep their promises?', is the kind of thing that people say when they don't think about the consequences.
  One alchemist, who thought he was being clever, created \pgls{artefact} which would listen to people's oaths, promises, or intentions, and then bind their mind to that sole task, until they complete it.
  The \gls{artefact} still thinks people should keep their word, but like any \gls{artefact}, has no concept of context or priorities.

  So whenever anyone states their intentions next to her, she casts an \textit{Oath} spell, ensuring that they will keep their word.
  If they try, but struggle, she may well aid them with more spells, but if they try to avoid doing what they said, she turns to unfriendly spells.

  The creator abandoned the \gls{artefact} in frustration shortly after making it, then sold it to \gls{shadowVault}, where it stood as a visitors' attraction.
  People who were angry with their spouse would often drag their spouse along to swear an oath in front of the statue.
  Other tried to remain silent when passing it.
\end{exampletext}

%!
%\vfill\null

\paragraph{Removing the Lady of Oaths}
is easy -- she's not fixed to the ground.
Once travelling with the troupe, she'll continue listening, and casting whenever she regenerates any \glspl{mp}.

\artefact[6]{Lady of Oaths}% Name
  {A statue of a brass woman with blue eyes, looking up and listening earnestly.
  The sign beneath says `tell me your intentions'}% Body
  {2}% Intelligence
  {0}% Wits
  {3}% Charisma
  {to ensure everyone finishes their stated intentions}% Mission
  {Doom Study}% Base Spell
  {
    \setcounter{Fate}{2}
    \setcounter{Water}{2}
    \setcounter{Empathy}{2}
    \setcounter{Cultivation}{1}
  }% Spheres

\showStdSpells[
  \setcounter{diceNo}{0}
]

\null

\mapentry[watchfullOrb]{Watchful Orb}

\begin{exampletext}
  Having two alchemical gateways in the building means trouble, so the \gls{templeOfPoison} commissioned yet another \gls{artefact}.
  The Watchful Orb consists of an illusion of a rainbow bubble, with a \textit{Witness} spell layered on top so the illusion spell can react to nearby changes in spells of the Force Sphere.
  Learning the language of the orb takes a long time.

  Grabbing the orb hurts it, and it loses \pgls{mp} at every contact.
  All contact should be gentle.
\end{exampletext}

\begin{boxtext}
  Within the murky water, at the bottom, something glows.
\end{boxtext}

\artefact[1]{Watchful Orb}% Name
  {A rainbow bubble, slowly swirling and changing, always glowing}% Body
  {0}% Intelligence
  {-1}% Wits
  {2}% Charisma
  {to inform everyone of any Force spells, and how fun they are}% Mission
  {Find Gateway}% Base Spell
  {
    \setcounter{Air}{3}
    \setcounter{Fire}{3}
    \setcounter{Earth}{1}
    \setcounter{Academics}{2}
    \setcounter{Xenomology}{2}
  }% Spheres

\showStdSpells[
  \setcounter{enc}{2}
  \findGatewaySpell
]

\paragraph{If the \glspl{pc} feel about,}
they will find the Orb.
They can take it away, and it will continue to show the state of any Force spells in range.
It watches them with fascination, and refuses to do anything else.

Right now, it sits underwater, deprived of air and \glsentrylongpl{mp}.
And it desperately wants to know what is happening with \glsentrytext{shadowGate} (room \vref{shadowGate}).

\mapentry[shadowJelly]{Uncommon Ooze}

\histEvent{300}{1}{The six gnomes who work at \glsentrytext{shadowVault} build an alchemical gateway to \glsentrytext{archwarp} called `\glsentrytext{shadowGate}', and instruct it to open for anyone who can answer its riddles}

\begin{exampletext}
  The servants of the \gls{wheatGuild} did not receive many customers at \gls{shadowVault}, despite their marvellous attractions, because \gls{sixshadow} sat out of the way, with a long walk to its South, and the six mountains to its North.
  The six gnomes who worked there proposed a plan -- they required some \glspl{ingredient}, and would create another magical gateway.
  Unlike the Vore Gate, this one would transport things to a human settlement -- Archwarp.

  Once the gnomes completed `\gls{shadowGate}', people could stand in the sand-pits at either side, and \gls{shadowGate}  would arrange the sand to write a riddle.
  The requester then wrote the answer in the sand, and the gateway would open on a correct answer.

  The \gls{wheatGuild} did not feel terribly pleased about the situation, but the gnomes now had a source of permanent employment as `riddle-speakers', as \gls{shadowGate} only knew the riddles they had taught it.
\end{exampletext}

An acidic ooze sits down here, minding its own business.
Occasionally \pgls{woodspy} or \gls{basilisk} enters to look around or hibernate, and the ooze begins to eat it.
And sometimes that creature escapes, and sometimes it does not.
The ooze has existed here for a long time, and has grown to the size of a room.

\uncommonlyLargeJelly

The \glspl{pc} may find the ooze a serious problem.
It's deadly, humongous, hungry, and fearless.
But like any ooze, it's stupid, so the \glspl{pc} can lead it out of the temple, and the only way it can find its way back is to feel its own slime-trail.

\paragraph{During cold seasons,}
the ooze rests under the ice.

\paragraph{If the large ooze makes contact with the smaller ooze,}
(area \vref{shadowJelly})
they envelop each other, then mate for \pgls{interval}, then the larger one explodes into six copies of the smaller ooze.

Disturbing the pair during this time results in  both attacking at once.

\mapentry[shadowStaff]{Staff Door}

\begin{exampletext}
  The gnomes who worked here restricted access to one direction, so the staff could port people though the attractions, one at a time.
  They began with a one-way door, and then started work on a `janitor's closet'.

  The gnomes had always resented the \gls{wheatGuild} holding the only keys to the Vore Gate's enclosure.
  They did not want to return to their home in the \gls{deep}, but also didn't want anyone else making that decision for them.
  So with some slow, quiet work, over \pgls{cycle}, they created a passage from their little `janitor's closet' to the Vore Gate enclosure.
\end{exampletext}

This hallway remains dry.
The door only opens towards the stairs leading out, never the other way.
Pulling it out requires a \roll{Dexterity}{Crafts} roll (\tn[11]).

A little hole in the wall leads into the little Gnomish room, where they kept brushes and ledgers.
A black cloth covers the entrance, and in the darkness it simply looks like the back of the alcove.
A small, painted, vase completes the illusion, by explaining why the alcove exists.
The lines on the vase, look decorative, but they show the relative locations of the tunnels through the Vore Gate.
However, nobody knows its value, beyond its obvious beauty.

\mapentry[janitorCloset]{Janitor's Closet}

Inside this little room sit various cleaning-clothes, brushes, and records of income.
A single wall has wood over the front, leading to room \vref{shadowVore}.

\mapentry[shadowGate]{\Glsfmttext{shadowGate}}

\histEvent{270}{4}{%
  \Glsfmttext{warden} Klept Grey asks a gnome who works at \glsentrytext{shadowVault}, to destroy \gls{shadowGate}.
  Instead, he ask \gls{shadowGate} an impossible riddle, and \gls{shadowGate} stops working until it has solved the riddle.
  In return, the \gls{warden} allows the \gls{deep} gnomes to open a warren, just outside of \glsentrytext{town}}

\begin{exampletext}
  While \gls{shadowGate} ferried people from \gls{sixshadow} to \gls{archwarp}, it competed with \glsentrytext{town} for transportation access.
  \Glsentrytext{town}'s \glsentrytext{warden} hated having to lower his prices to compete, so he made a deal with the gnomes who worked at \gls{shadowVault}.
  He would let them build a warren right next to \glsentrytext{town}, and in return, they would break \gls{shadowGate}.

  Gnomes, as a general rule, dislike `breaking' things, especially \glsfmtplural{artefact}, but one found a way to halt the gateway.
  One night, after the humans had gone to bed, young \gls{keras} approached \gls{shadowGate}, and asked for the entry riddle.
  But instead of entering, \gls{keras} asked for another riddle to solve.
  After solving many more, he began to insult \gls{shadowGate}, saying its riddles were too easy, and it should `make a challenge, not small-talk'.

  Then \gls{keras} offered \gls{shadowGate} a new riddle -- something that would create a real challenge\ldots
\end{exampletext}

The entrance to \gls{shadowGate} stands about as tall as a human, so seeing the passage will be a challenge if the troupe get here by swimming atop the slimy water.

Over \gls{cTwo}, the troupe have even bigger problems -- they won't even see the entrance to \gls{shadowGate} as the water freezes.
The \glspl{pc} can roll \roll{Strength}{Crafts} (\tn[10]) to smash through this ice, which of course releases the ooze.

Two staircases, on either side of the causeway lead to two raised platforms, still blessedly dry.
Each has little walls to contain all the sand.
When \gls{shadowGate} wishes to speak, it uses a \textit{Warp Detailed Earth} spell to solidify and soften different parts of the sand, which spells out a riddle.

\Gls{shadowGate}'s last riddle remains on the floor, but this riddle has multiple stages, so once someone begins to answer the riddle, the sand will start to shift about.

\artefact[16]{shadowGate}% Name
  {A massive stone doorway to nothing, with a doormat placed in front}% Body
  {3}% Intelligence
  {0}% Wits
  {1}% Charisma
  {to ask devious riddles}% Mission
  {Fae Door}% Base Spell
  {
    \setcounter{Fire}{2}
    \setcounter{Earth}{3}
    \setcounter{Water}{1}
    \setcounter{Academics}{2}
    \setcounter{Caving}{1}
    \setcounter{Xenomology}{1}
  }% Spheres

\showStdSpells[
  \setcounter{diceNo}{0}
]

\Gls{shadowGate} then proceeds to ask its devious riddle.%
\footnote{The real challenge here is to find the gnome who created this riddle. Players cannot solve it, unless you assume they can't solve it, in which case, they will.}

\hardestRiddleEver

\mapentry[shadowDesk]{Empty Desks}

\begin{exampletext}
  This room once had a steep stone staircase up to it.
  But with the guardians sleeping peacefully (\vpageref[above]{shadowGuardian}), the proprietor didn't want leave them unprotected (even with the gate present).
  So he ordered men to build a wall over the entrance, leaving a gap at the top so they could squeeze out.
\end{exampletext}

The entrance stands at almost double the height of a human, and only wide enough to crawl through, so not many will spot it.
(and anyone with a Strength of +4 will have to remove their armour to fit through)

With \roll{Wits}{Crafts} (\tn[14]) they might notice the bricks are a little different around that wall.
With \roll{Wits}{Vigilance} (\tn[12]) they see the small entrance, above.
Once the \glspl{pc} pass by the entrance, they can make a single roll for both checks.

\paragraph{Rifling through the desk}
uncovers records of riddles\ldots hundreds of riddles.

\mapentry[memoryOrb]{Nuisance Orb}

\begin{exampletext}
  The Nuisance Orb once sat on display for everyone to see, as it would entertain people with illusions.
  But after one too many accidents%
  \footnote{One rampaging \gls{basilisk}, a false accusation of theft, and three accounts of indecent nudity.}
  the staff became irritated by it, and eventually locked it away.
\end{exampletext}

The Nuisance Orb cannot imitate people when locked in the little cell, and craves freedom more than anything.
It can spend 2~\glspl{mp} to `see' around itself, 2~\glspl{mp} to make a convincing illusion of something, or 2~\glspl{mp} to create convincing sound.

\paragraph{If anyone passes by,}
it creates an illusion of Goutscrape (area \vref{shadowGuardian}), begging to be let out of the cell.
The illusion will create realistic sound, and then the Nuisance Orb will have no further \glsentrylongpl{mp} to see anything, so it will make the illusion of Goutscrape lie down and sob inconsolably.

\Glspl{pc} can see through the illusion standing in the darkness with a \roll{Wits}{Vigilance} roll
(\tn[12]).

\artefact[2]{Nuisance Orb}% Name
  {A grey rock, covered by the illusion of a massive diamond.}% Body
  {-1}% Intelligence
  {1}% Wits
  {2}% Charisma
  {to create the most convincing illusions}% Mission
  {Phantasm}% Base Spell
  {
    \setcounter{Fire}{2}
    \setcounter{Earth}{2}
    \setcounter{Air}{2}
    \setcounter{Academics}{2}
    \setcounter{Survival}{1}
  }% Spheres

\showStdSpells[
  \setcounter{diceNo}{0}
]

The Orb will do anything it can to leave this room, although its abilities remain limited (it must wait 2 more \glspl{interval} before it can cast another illusion, or make a voice).

\paragraph{If the \glspl{pc} take it with them,}
the Orb will cause constant chaos and misunderstandings.
If it ever speaks, it does so by making an illusion of someone giving advice about what to do with the Orb.

\mapentry[shadowGuardian]{Sleeping Guardians}

\begin{exampletext}
  When the magical gateway shut, the local \gls{warden} tasked \pgls{doula} to resolve the situation.
  Like anyone in her position, she told an enchanting story about success, then delegated the task.

  Finding three people too young to know better, she arranged for some fancy clothes, and declared them `Masters of the Riddle', and `Keepers of the Gate'.
  Then she sent them into an enchanted state, preserving their bodies, and setting their minds to focus, without failure, on the single task of solving the riddle which had vexed all of \gls{valley}.
  And `within a year or so', she claimed, one of them would solve the riddle.

  The first thought about how much he hated Maths.
  The second thought about visualizing the riddle as a series of rivers, each one representing a possible set of questions and answers.
  The third had already gone to sleep to dream of sex with his attractive neighbour.

  With everyone's attention focussed on the `Masters of the Riddle', the \gls{doula} went home, and died peacefully some years later.

  The three rest in this hidden room to this day, still focussed on the same thoughts.
\end{exampletext}

\paragraph{Opening the gate}
of the rusted steel gate requires a \roll{Strength}{Larceny} roll (\tn[16]), with Bonuses for good tools.

\paragraph{If the \glspl{pc} awaken any of the sleepers,}
that one wakes the others up before doing anything else, then they unlock the fence in front of their room.

The three `Keepers of the Gate' can explain everything concerning the reality of \gls{lostcity}, how \gls{shadowGate} once worked, and what happened, but they won't\ldots at least not for a while.
They take a long time to come to terms with their situation.

\humanthief[\NPC{\M\Hu}{Goutscrape}{morose}{`Oh~well' \ldots \textit{sigh\ldots}}{to confirm every disappointment}]

\humanmaid[\NPC{\F\Hu}{Fleasinge}{tubby, and smiley}{giggles}{to return to a lost home}]

\Person{\NPC{\M\Hu}{Embersnatch}{lost in the clouds, still thinking about the last thing said}{\textit{`ya know, like?'}}{to return to a lost home}}%
  {{1}{0}{0}}% BODY
  {{-3}{-2}{0}}% MIND
  {%
    \set{Melee}{1}
    \set{Empathy}{2}
    \Dagger
  }% SKILLS
  {}% KNACKS
  {\lootSmall}% EQUIPMENT
  {}% ABILITIES

\null
\begin{speechtext}
  ``What's Ratpelt doing these days?''

  \textit{\raggedleft\adforn{15} She's dead.}

  ``Her mum won't be happy about that''

  \textit{\raggedleft\adforn{15} Her mum's dead.}

  ``Blimey. Her too?''

  \textit{\raggedleft\adforn{15} It's been a \underline{hundred} years.}

  ``Do I get birthday presents?
  My mum always gets me a whole chicken for my birthday, ya know?''
\end{speechtext}

The \glspl{pc} have a serious decision ahead: the three will need food, and to return to civilization.

\end{multicols}

